### 2014-05-02 ProjectNotes.tex
Added notes for modified perceptron algorithm.

\documentclass{article}

\usepackage{amsmath}
\newcommand{\V}[1]{\boldsymbol{#1}}
\newcommand{\E}[0]{\mathbb{E}}
\title{Machine Learning Project Notes}

\author{Joseph McDonald and Steven Delong}

\begin{document}

\maketitle

\section*{Perceptron with Positive Corrections.}

We would like to modify the perceptron algorithm to only make updates when $\hat{y} = 1$ in order for the user to not have to see every article, but this will leave the number of mistakes made with $\hat{y} = 0$ unbounded.  as a compromise, let us generate iid variables $k_i$ for each observation which are equal to 1 with probability $p$ and equal to $0$ with probability $1-p$.  If $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=1$, the algorithm does not ask for the correct label, and makes no update.  It seems that in this way, we should still be able to bound the number of mistakes, perhaps in expectation or probabilistically.\\

Let us let $I_1$ be the set of $t$ where a mistake was made and,
$\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
$\hat{y} = 0, k = 1$, and let $I_3$ be the set where a mistake was
made, $\hat{y} = 0$ and $k = 0$. Finally, let $M_i = |I_i|$ for $i =
1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
$M$ in the usual perceptron case.  We assume that there exits a $\rho$
and $R$ satisfying the assumptions of theorem 7.8. Let $M' = M_1 + M_2$, then
\begin{align*}
M' =& \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2}
y_t\V{x}_t \\
 \leq & \  \|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t \|\\
= & \ \|\sum_{t \in I_1 \cup I_2} \V{w}_{t+1} - \V{w}_t) \| \\
= & \ \|\V{w}_{T+1} \| \\
= & \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 -
  \|\V{w}_t\|^2 }\\
= & \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
  \|\V{w}_t\|^2 }\\
= & \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
  \|\V{x}_t\|^2} \\
\leq & \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
\sqrt{M'r^2} \\
\Rightarrow M' \leq &\frac{r^2}{\rho^2} \\
\end{align}
We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
Here we revert to a weaker bound, considering the expectation of
$M_3$.  
\begin{align*}
M_3 = & \sum_{I_2} 1_{k = 0} \\
\E[M_3] = & \sum_{I_2} \E[1_{k = 0}] = (1 - p) (M_3 + M_2) \\
M_2 = & \sum_{I_2} 1_{k = 1} \\
\E[M_2] = & p (M_3 + M_2) \\
\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]\\
\end{align}
We may then apply the crude bound $\E[M_3] \leq & \frac{1-p}{p}
M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
\begin{align*}
\E[M]  =  & \E[M'] + \E[M_3] \\
\leq & \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
\leq = \frac{1}{p}\frac{r^2}{\rho^2} \\
\end{align}
Note that this is a weak bound.  Not only is it greater than the
original perceptron bound by a factor of $1/p$, it is also only a
bound in expectation.

\end{document}

### 2014-05-02 ProjectNotes.tex
fixed typos in tex file

@@
 \documentclass{article}
-
+\usepackage{amssymb}
 \usepackage{amsmath}
@@
 \Rightarrow M' \leq &\frac{r^2}{\rho^2} \\
-\end{align}
+\end{align*}
 We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
@@
 \E[M_2] = & p (M_3 + M_2) \\
-\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]\\
-\end{align}
-We may then apply the crude bound $\E[M_3] \leq & \frac{1-p}{p}
+\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
+\end{align*}
+We may then apply the crude bound $\E[M_3] \leq  \frac{1-p}{p}
 M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
@@
 \leq = \frac{1}{p}\frac{r^2}{\rho^2} \\
-\end{align}
+\end{align*}
 Note that this is a weak bound.  Not only is it greater than the

### 2014-05-03 ArxivData.py
changed gettodayspapers(): gets data through OAIPMH, update subject list

@@ -7,6 +7,7 @@ import sys
 from xml.etree import ElementTree as ET
 from sklearn.feature_extraction.text import TfidfVectorizer
 import time
+from datetime import date
 
 class Paper:
     """ Class to hold paper information.
@@ -146,7 +147,7 @@ def IDFromLink(link):
     return paper_id
     
 
-def GetTodaysPapers():
+def GetTodaysPapers(subject=''):
     """ 
     GetTodaysPapers()
     
@@ -158,17 +159,31 @@ def GetTodaysPapers():
     return value:
            This function returns a list of Paper objects, populated from the papers on Arxiv
     """
+    
 
-    #list of all subjects to grab papers from
-    subject_list = ["cs","math","physics","cond-mat","math-ph","stat"]
+    #list of all subjects to grab papers from, check if optional argument set is in list
+    subject_list = ['physics:astro-ph','physics:cond-mat','physics:gr-qc',
+        'physics:hep-ex','physics:hep-lat','physics:hep-ph','physics:hep-th',
+        'physics:math-ph','physics:nlin','physics:nucl-ex','physics:nucl-th',
+        'physics','physics:quant-ph','math','cs','q-bio','q-fin','stat']
+    if subject in subject_list:
+        subject_string = '&set='+subject
+    elif subject:
+    #RAISE ERROR since subject doesn't match a set name TODO
+        return
+    else:
+        subject_string = ''
+
+    # get today's date as a string 'YYYY-MM-DD'
+    today = str(date.today())
 
     #initialize paper list
     id_list = []
     paper_list = []
     
-    #TODO, loop through subjects
-    url = "http://export.arxiv.org/rss/math"
-
+    #set the URL using OAI-PMH standard,  TODO, loop through subjects
+    url = 'http://export.arxiv.org/oai2?verb=ListRecords&from='+today+subject_string+'&metadataPrefix=oai_dc'
+    #url = "http://export.arxiv.org/rss/math"
 
     #extract info here.
     data = urllib.urlopen(url).read()

### 2014-05-07 ArxivData.py
hard coded getdata.py for now.

@@ -397,7 +397,7 @@ def GetPapersOAI(day='', until='', subject='',subcategories=None):
                    'cs' : computer_science, 'q-bio' : quant_bio} 
 
     #Hard code testing subcategories for now.
-    testing_subcategories = ["Mathematics - Numerical Analysis","Mathematics - Functional Analysis", "Mathematics - Probability", "Mathematics - Probability", "Computer Science - Data Structures and Algorithms", "Computer Science - Information Theory", "Mathematics - Analysis of PDEs",'Computer Science - Computational Engineering, Finance, and Science', 'Computer Science - Learning']
+    testing_subcategories = ["Mathematics - Numerical Analysis","Mathematics - Functional Analysis", "Mathematics - Probability", "Mathematics - Probability", "Computer Science - Data Structures and Algorithms", "Computer Science - Information Theory", "Mathematics - Analysis of PDEs",'Computer Science - Computational Engineering, Finance, and Science', 'Computer Science - Learning','Mathematics - Combinatorics','Mathematical Physics']
                    
 
     # if day not specified, get today's date as a string 'YYYY-MM-DD'; if until specified, create string

### 2014-05-07 getTestData.py

@@ -19,19 +19,22 @@ if __name__ == '__main__':
         #+ad.GetPapersOAI('2014-04-30','2014-05-02','cs'))
 
     #remove duplicates, do this the dumb way for now
-    remove_list = []
+    unique_paper_list = []
     for j in range(len(paper_list)):
-        for k in range(j,len(paper_list)):
+        unique_flag = True
+        for k in range(j+1,len(paper_list)):
             if paper_list[j].id == paper_list[k].id:
-                remove_list.append(paper_list[k])
+                unique_flag = False
+                print paper_list[j].title
                 
-    for r in remove_list:
-        paper_list.remove(r)
-
-    print "total articles: " , len(paper_list)
+        if unique_flag:
+            unique_paper_list.append(paper_list[j])
+                
+                
+    print "total articles: " , len(unique_paper_list)
 
     with open('TestData.pkl','wb') as file:
-        dump(paper_list,file)
+        dump(unique_paper_list,file)
 
 
 

### 2014-05-07 ArxivData.py
small changes to ArxivData

@@ -314,16 +314,17 @@ def GetTodaysPapers(subject=''):
     return paper_list
 
 
-def GetPapersOAI(day='', until='', subject='',subcategories=None):
+def GetPapersOAI(day='', until='', subject='', subcategories=None):
     """ 
-    GetPapersOAI()
-    
     Function to get all arxiv papers updated on the specific day within subject using OAI-PMH protocol,
         for harvesting large batches of papers.
     
     inputs:
-            day (optional), subject (optional)
-
+            day
+            until
+            subject
+            subcategories
+            
     return value:
             This function returns a list of Paper objects, populated from Arxiv papers updated on given
             range of days within given subject set
@@ -355,19 +356,19 @@ def GetPapersOAI(day='', until='', subject='',subcategories=None):
         'Instrumentation and Detectors','Medical Physics','Optics','Physics Education',
         'Physics and Society','Plasma Physics','Popular Physics','Space Physics']
 
-    astrophysics = ['Astrophysics of Galaxies','Cosmology and Nongalactic Astrophysics',
+    astroph = ['Astrophysics of Galaxies','Cosmology and Nongalactic Astrophysics',
         'Earth and Planetary Astrophysics','High Energy Astrophysical Phenomena',
         'Instrumentation and Methods for Astrophysics','Solar and Stellar Astrophysics']
 
-    cond_matter = ['Disordered Systems and Neural Networks','Materials Science',
+    cond-mat = ['Disordered Systems and Neural Networks','Materials Science',
         'Mesoscale and Nanoscale Physics','Other Condensed Matter','Quantum Gases',
         'Soft Condensed Matter','Statistical Mechanics','Strongly Correlated Electrons',
         'Superconductivity']
 
-    nonlin_sciences = ['Adaptation and Self-Organizing Systems','Cellular Automata and Lattice Gases',
+    nlin-sci = ['Adaptation and Self-Organizing Systems','Cellular Automata and Lattice Gases',
         'Chaotic Dynamics','Exactly Solvable and Integrable Systems','Pattern Formation and Solitons']
 
-    computer_science = ['Artificial Intelligence','Computation and Language',
+    cs = ['Artificial Intelligence','Computation and Language',
         'Computational Complexity','Computational Engineering, Finance, and Science',
         'Computational Geometry','Computer Science and Game Theory',
[…]

### 2014-05-08 ArxivData.py
added shuffle to getTestData, includes OfficialTestData

@@ -360,12 +360,12 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
         'Earth and Planetary Astrophysics','High Energy Astrophysical Phenomena',
         'Instrumentation and Methods for Astrophysics','Solar and Stellar Astrophysics']
 
-    cond-mat = ['Disordered Systems and Neural Networks','Materials Science',
+    cond_mat = ['Disordered Systems and Neural Networks','Materials Science',
         'Mesoscale and Nanoscale Physics','Other Condensed Matter','Quantum Gases',
         'Soft Condensed Matter','Statistical Mechanics','Strongly Correlated Electrons',
         'Superconductivity']
 
-    nlin-sci = ['Adaptation and Self-Organizing Systems','Cellular Automata and Lattice Gases',
+    nlin_sci = ['Adaptation and Self-Organizing Systems','Cellular Automata and Lattice Gases',
         'Chaotic Dynamics','Exactly Solvable and Integrable Systems','Pattern Formation and Solitons']
 
     cs = ['Artificial Intelligence','Computation and Language',
@@ -383,34 +383,34 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
         'Social and Information Networks','Software Engineering','Sound','Symbolic Computation',
         'Systems and Control']
 
-    q-bio = ['Biomolecules','Cell Behavior','Genomics','Molecular Networks',
+    q_bio = ['Biomolecules','Cell Behavior','Genomics','Molecular Networks',
         'Neurons and Cognition','Other Quantitative Biology','Populations and Evolution',
         'Quantitative Methods','Subcellular Processes','Tissues and Organs']
 
-    q-fin = ['Computational Finance','Economics','General Finance','Mathematical Finance',
+    q_fin = ['Computational Finance','Economics','General Finance','Mathematical Finance',
         'Portfolio Management','Pricing of Securities','Risk Management','Statistical Finance',
         'Trading and Market Microstructure']
 
     stat = ['Applications','Computation','Machine Learning','Methodology',
         'Other Statistics','Statistics Theory']
 
-    subject_dict = {'physics:astro-ph':astroph, 'physics:cond-mat':cond-mat,
-        'physics:gr-qc':[], 'physics:hep-ex':[],'physics:hep-lat':[],'physics:hep-ph':[],
[…]

### 2014-05-08 getTestData.py

@@ -1,6 +1,7 @@
 import ArxivData as ad
 from cPickle import dump
 import time
+from random import shuffle
 
 paper_list = []
 
@@ -32,6 +33,8 @@ if __name__ == '__main__':
                 
                 
     print "total articles: " , len(unique_paper_list)
+
+    shuffle(unique_paper_list)
 
     with open('TestData.pkl','wb') as file:
         dump(unique_paper_list,file)

### 2014-05-08 LabelData.py
changed LabelData.py to pull from OfficialTestData.pkl

@@ -10,7 +10,7 @@ from ArxivData import Paper
 from ArxivData import PromptUser
 
 #filename where data is stored
-data_filename = "./TestData.pkl"
+data_filename = "./OfficialTestData.pkl"
 
 data_file = open(data_filename,"rb")
 

### 2014-05-08 ArxivData.py
changed labeldata to use OfficialTetsData.pkl

@@ -5,7 +5,7 @@ import urllib
 import re #for removing namespaces, featurizing abstracts
 import sys
 from xml.etree import ElementTree as ET
-from sklearn.feature_extraction.text import TfidfVectorizer
+#from sklearn.feature_extraction.text import TfidfVectorizer
 #import time
 from datetime import datetime
 import cPickle

### 2014-05-08 ArxivData.py
Added OnlineSVm.py

@@ -75,6 +75,19 @@ class TextFeatureVector:
                 
         return weights
 
+    def UpdateWeightsSVM(self,weights,y,eta,C):
+        """ update weights according to the rule 
+        weights = weights - eta(w_t - C*x*y) 
+        for online SVM"""
+        
+        for word in iter(self.words):
+            if word in weights:
+                weights[word] = weights[word] - eta*(weights[word] - C*y*self.words[word]/self.total_words)
+            else:
+                weights[word] = C*eta*y*self.words[word]/self.total_words
+                
+        return weights
+
 
     def __str__(self):
         

### 2014-05-08 OnlineSVM.py

@@ -1,0 +1,72 @@
+import numpy as np
+from ArxivData import TextFeatureVector
+from ArxivData import FeaturizeAbstracts # for testing.
+
+def sign(x):
+    """ compute sign of x, with convention that 0 is positive """
+    if x >= 0:
+        return 1
+    else:
+        return -1
+
+class OnlineSVMClassifier:
+    """ Online SVM classifier for binary classification."""
+
+    def __init__(self,C,eta):
+        """ Constructor, takes parameter C used in the SVM algorithm. 
+
+        Arguments:
+                C - penalty parameter for SVM algorithm
+                eta - learning rate
+                
+        """
+
+        self.weights = dict()
+        self.eta = eta
+        self.C = C
+
+        
+    def Update(self,x,y_hat,y):
+        """ given that the SVM has guessed y_hat for data x, update it 
+        using the correct value y.
+
+        Note: must be used after prediction to obtain a correct accuracy estimate, 
+        Note: We may only update on some of the predictions where y_hat = -1 (undesireable paper).
+        
+        Note: y_hat is not directly used in this function, but is included for consistency with PerceptronClassifier Update function.
+        """
+
+        if(y*x.Dot(self.weights) < 1):
+            x.UpdateWeightsSVM(self.weights,y,self.eta,self.C)
+        else:
+            x.UpdateWeightsSVM(self.weights,y,self.eta,0.0)
+            
+        return
+
+
+    def Predict(self,x):
+        """ predict y by using sign of w dot x """
+
+        return sign(x.Dot(self.weights))
+
+
+
+if __name__ == "__main__":
+    
+    x = ["This is a Test Abstract"]
+    x = FeaturizeAbstracts(x)[0]
+    
+    svmclassifier = OnlineSVMClassifier(0.3,0.2)
+    
+    y_hat = svmclassifier.Predict(x)
+    
+    assert y_hat == 1, "SVM should predict y_hat = 1 at initialization.  It does not."
+    
+    #update
+    svmclassifier.Update(x,y_hat,-1)
+    
+    y_hat2 = svmclassifier.Predict(x)
+    
+    assert y_hat2 == -1, "SVM should predict y_hat = -1 after update"
+
+    print "Completed some basic tests."

### 2014-05-08 Perceptron.py

@@ -1,5 +1,6 @@
 import numpy as np
 from ArxivData import TextFeatureVector
+from ArxivData import FeaturizeAbstracts #for testing.
 
 def sign(x):
     """ compute sign of x, with convention that 0 is positive """
@@ -171,24 +172,26 @@ class WinnowClassifier():
 if __name__ == "__main__":
     
 
-    x = np.ones(10)
-    pclassifier = PerceptronClassifier(10,0.3)
+    x = ["This is a test abstract"]
+    x = FeaturizeAbstracts(x)
+    pclassifier = PerceptronClassifier(0.3)
     
-    y_hat = pclassifier.Predict(x)
+    y_hat = pclassifier.Predict(x[0])
     
     assert y_hat == 1, "y_hat for perceptron should be 1 at initialization, it is not"
     
-    pclassifier.Update(x,y_hat,-1)
-    y_hat_2 = pclassifier.Predict(x)
+    pclassifier.Update(x[0],y_hat,-1)
+    y_hat_2 = pclassifier.Predict(x[0])
     
     assert y_hat_2 == -1, "y_hat should be -1 after update, it is not"
 
-
+    
+    #NOTE: Winnow currently unused
     wclassifier = WinnowClassifier(8,0.3)
     
     x = np.array([1.0, 1.0, 1.0, 1.0, -1.0, -1.0, -1.0, -1.0])
     y_hat = wclassifier.Predict(x)
-    
+
     assert y_hat == 1, "y_hat for winnow should be 1 at initialization for this x, it is not"
     
     wclassifier.Update(x,y_hat,-1)

### 2014-05-08 Perceptron.py
started setting up testing.

@@ -50,6 +50,12 @@ class PerceptronClassifier:
         
         return float(self.n_correct)/float(self.n_wrong + self.n_correct)
 
+#wrapper functions to set up classifiers for testing
+def makePerceptronClassifier(parameters):
+    """ parameters are just eta """
+    
+    classifier = PerceptronClassifier(parameters[0])
+
 
 class KernelPerceptronClassifier():
 

### 2014-05-08 TestClassifiers.py

@@ -1,0 +1,48 @@
+from ArxivData import FeaturizeVector
+import cPickle
+from ArxivData import Paper
+from ArxivData import PromptUser
+from OnlineSVM import OnlineSVMClassifier
+from Perceptron import PerceptronClassifier
+
+
+#helper functions to set up classifiers
+def makePerceptronClassifier(parameters):
+    """ parameters are just eta """
+    
+    classifier = PerceptronClassifier(parameters[0])
+
+
+
+#names of people who contributed labels
+names = ["steven","sid","iantobasco","joey","manas","travis"]
+
+#get data
+data_filename = "./OfficialTestData.pkl"
+data_file = open(data_filename,"rb")
+paper_list = cPickel.load(data_file)
+abstracts = GetAbstracts(paper_list)
+abtract_vectors = FeaturizeAbstracts(abstracts)
+
+classifer_list = [MakePerceptronClassifier, MakeOnlineSVMClassifier, MakeOnlineSVMClassifier]
+parameters_list = [[0.3], [0.3, 0.2],[0.3,0.4]]
+
+#go through all classifiers to test
+for cln in range(len(classifier_list)):
+    
+    classifier = classifier_list[cln](parameters_list[cln])
+
+    #go through labeled data.
+    for name in names:
+        #get labels
+        label_filename = name + "labels.pkl"
+        label_file = open(label_filename,"rb")
+    
+        
+    
+    
+
+
+
+
+    

### 2014-05-08 OnlineSVM.py
progress on testing script.  Travis labels added.

@@ -48,7 +48,24 @@ class OnlineSVMClassifier:
         """ predict y by using sign of w dot x """
 
         return sign(x.Dot(self.weights))
+    
+    def __repr__(self):
+        
+        repstring = 'Online SVM Classifier, eta = %1.3f, C = %1.3f'.format(self.eta, self.C)
+        
+        return repstring
+    
+    __str__ = __repr__
+        
 
+
+#wrapper functions to set up classifiers for testing
+def MakeOnlineSVMClassifier(parameters):
+    """ parameters are just eta """
+    
+    classifier = OnlineSVMClassifier(parameters[0],parameters[1])
+    
+    return classifier
 
 
 if __name__ == "__main__":

### 2014-05-08 Perceptron.py

@@ -50,11 +50,22 @@ class PerceptronClassifier:
         
         return float(self.n_correct)/float(self.n_wrong + self.n_correct)
 
+    def __repr__(self):
+        
+        repstring = 'Perceptron Classifier, eta = %1.3f'.format(self.eta)
+        
+        return repstring
+    
+    __str__ = __repr__
+
+
 #wrapper functions to set up classifiers for testing
-def makePerceptronClassifier(parameters):
+def MakePerceptronClassifier(parameters):
     """ parameters are just eta """
     
     classifier = PerceptronClassifier(parameters[0])
+    
+    return classifier
 
 
 class KernelPerceptronClassifier():

### 2014-05-08 TestClassifiers.py

@@ -1,16 +1,13 @@
-from ArxivData import FeaturizeVector
+from ArxivData import FeaturizeAbstracts
+from ArxivData import GetAbstracts
+import numpy as np
 import cPickle
 from ArxivData import Paper
 from ArxivData import PromptUser
 from OnlineSVM import OnlineSVMClassifier
+from OnlineSVM import MakeOnlineSVMClassifier
 from Perceptron import PerceptronClassifier
-
-
-#helper functions to set up classifiers
-def makePerceptronClassifier(parameters):
-    """ parameters are just eta """
-    
-    classifier = PerceptronClassifier(parameters[0])
+from Perceptron import MakePerceptronClassifier
 
 
 
@@ -20,23 +17,61 @@ names = ["steven","sid","iantobasco","joey","manas","travis"]
 #get data
 data_filename = "./OfficialTestData.pkl"
 data_file = open(data_filename,"rb")
-paper_list = cPickel.load(data_file)
+paper_list = cPickle.load(data_file)
 abstracts = GetAbstracts(paper_list)
-abtract_vectors = FeaturizeAbstracts(abstracts)
+abstract_vectors = FeaturizeAbstracts(abstracts)
 
-classifer_list = [MakePerceptronClassifier, MakeOnlineSVMClassifier, MakeOnlineSVMClassifier]
+classifier_list = [MakePerceptronClassifier, MakeOnlineSVMClassifier, MakeOnlineSVMClassifier]
 parameters_list = [[0.3], [0.3, 0.2],[0.3,0.4]]
 
 #go through all classifiers to test
 for cln in range(len(classifier_list)):
     
-    classifier = classifier_list[cln](parameters_list[cln])
+    for p in [1.0, 0.1]:
 
-    #go through labeled data.
-    for name in names:
-        #get labels
-        label_filename = name + "labels.pkl"
-        label_file = open(label_filename,"rb")
+        #create classifier
+        classifier = classifier_list[cln](parameters_list[cln])
+        
+        print classifier
+        print "P value is: ", p
+        
+        #go through labeled data a few times, 
+        for name in names:
+            #get labels
+            label_filename = name + "labels.pkl"
+            label_file = open(label_filename,"rb")
+            labels = cPickle.load(label_file)
+
+            n_wrong = 0
+            n_right = 0
+            for i in range(len(abstract_vectors)):
+            
+                x = abstract_vectors[i]
+                y_hat = classifier.Predict(x)
+                y = labels[i]
[…]

### 2014-05-09 ArxivData.py
changed testdata stuff, set up testing, started fixing proof in ProjectNotes.tex

@@ -419,7 +419,9 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
                    'cs' : cs, 'q-bio' : q_bio} 
 
     #Hard code testing subcategories for now.
-    testing_subcategories = ["Mathematics - Numerical Analysis","Mathematics - Functional Analysis", "Mathematics - Probability", "Mathematics - Probability", "Computer Science - Data Structures and Algorithms", "Computer Science - Information Theory", "Mathematics - Analysis of PDEs",'Computer Science - Computational Engineering, Finance, and Science', 'Computer Science - Learning','Mathematics - Combinatorics','Mathematical Physics']
+#    testing_subcategories = ["Mathematics - Numerical Analysis","Mathematics - Functional Analysis", "Mathematics - Probability", "Computer Science - Data Structures and Algorithms", "Computer Science - Information Theory", "Mathematics - Analysis of PDEs",'Computer Science - Computational Engineering, Finance, and Science', 'Computer Science - Learning','Mathematics - Combinatorics','Mathematical Physics']
+
+    testing_subcategories = ["Mathematics - Numerical Analysis", "Computer Science - Learning","Mathematical Phyics", "Physics - Computational Physics"]
                    
 
     # if day not specified, get today's date as a string 'YYYY-MM-DD'; if until specified, create string
@@ -454,11 +456,13 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
 
     #extract info here.
     data = urllib.urlopen(url).read()
-
+    
     # declare namespaces
     ns = {'ns':'http://www.openarchives.org/OAI/2.0/',
         'dc':'http://purl.org/dc/elements/1.1/'}
     root = ET.fromstring(data)
+
+
     
     #initialize paper list
     paper_list = []    
@@ -471,17 +475,18 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
 #        print "today's date", str(datetime.today())
        
         if IsPaperInSubcategories(entry, testing_subcategories, ns):
-            print this_paper.title
             # check that the paper was published today, not just updated.
-#MAKE SUBCATEGORY DICTIONARY FOR CHECKING
+            #TODO: MAKE SUBCATEGORY DICTIONARY FOR CHECKING
             if day and until:
                 if (datetime.strptime(day, '%Y-%m-%d')
                     <= datetime.strptime(this_paper.published, '%Y-%m-%d')
                     <= datetime.strptime(until, '%Y-%m-%d')):
+                    print "appending paper"
[…]

### 2014-05-09 OnlineSVM.py

@@ -51,7 +51,7 @@ class OnlineSVMClassifier:
     
     def __repr__(self):
         
-        repstring = 'Online SVM Classifier, eta = %1.3f, C = %1.3f'.format(self.eta, self.C)
+        repstring = 'Online SVM Classifier, eta = %1.3f, C = %1.3f' % (self.eta, self.C)
         
         return repstring
     

### 2014-05-09 Perceptron.py

@@ -52,7 +52,7 @@ class PerceptronClassifier:
 
     def __repr__(self):
         
-        repstring = 'Perceptron Classifier, eta = %1.3f'.format(self.eta)
+        repstring = 'Perceptron Classifier, eta = %1.3f' % self.eta
         
         return repstring
     

### 2014-05-09 TestClassifiers.py

@@ -42,29 +42,40 @@ for cln in range(len(classifier_list)):
             label_file = open(label_filename,"rb")
             labels = cPickle.load(label_file)
 
-            n_wrong = 0
-            n_right = 0
+            #initialize counts for accuracy
+            n_pos_right = 0
+            n_precision_wrong = 0
+            n_recall_wrong = 0
             for i in range(len(abstract_vectors)):
             
                 x = abstract_vectors[i]
                 y_hat = classifier.Predict(x)
                 y = labels[i]
-                if y == y_hat:
-                    n_right += 1
+                if y == 1 and y_hat == 1:
+                    n_pos_right += 1
+                elif y == -1 and y_hat == -1:
+                    #do nothing, doesn't count as positive correct
+                    pass
                 elif y_hat == 1:
                     #update on false positive, add one to n_wrong
-                    n_wrong += 1
+                    n_precision_wrong += 1
                     classifier.Update(x,y_hat,y)
                 else:
                     #maybe update on false negative, depends on p.
-                    k = np.random.binomial(p,1)
-                    n_wrong += 1
+                    n_recall_wrong += 1
+                    k = np.random.binomial(1,p)
                     if k == 1:
                         classifier.Update(x,y_hat,y)
                         
 
             print "User: ", name
-            print "Accuracy: ", float(n_right)/float(n_wrong + n_right)
+            print "Total preferred papers: ", n_pos_right + n_recall_wrong
+            if n_pos_right != 0:
+                print "Recall: ", float(n_pos_right)/float(n_pos_right + n_recall_wrong)
+                print "Precision: ", float(n_pos_right)/float(n_pos_right + n_precision_wrong)
+            else:
+                print "Recall: ", 0.0
+                print "Precision: ", 0.0
 
         print "-"*80
             

### 2014-05-09 getTestData.py

@@ -6,17 +6,29 @@ from random import shuffle
 paper_list = []
 
 if __name__ == '__main__':
-    
-    math_list = ad.GetPapersOAI('2014-04-29', '2014-05-02', 'math')
+
+    # Note: Modified to be more relevant and increase total number of 
+    #       articles for OfficialTestData2.pkl
+
+    #originally was 5-30 - 04-02
+    math_list = ad.GetPapersOAI('2014-02-20', '2014-03-08', 'math')
+
+    print "math: ", len(math_list)
 
     #sleep for 21 , have to do this in order to use OAI MP again
     time.sleep(21)
 
-    cs_list = ad.GetPapersOAI('2014-04-29', '2014-05-02', 'cs')
+    cs_list = ad.GetPapersOAI('2014-02-20', '2014-03-08', 'cs')
 
-    print 'math:', len(math_list), ', cs: ', len(cs_list)
+    print "cs: ", len(cs_list)
 
-    paper_list = math_list + cs_list #(ad.GetPapersOAI('2014-04-30','2014-05-02','math')
+    time.sleep(21)
+
+    phys_list = ad.GetPapersOAI('2014-01-20', '2014-03-10', 'physics')
+
+    print 'math:', len(math_list), ', cs: ', len(cs_list), ', physics: ', len(phys_list)
+
+    paper_list = math_list + cs_list  + phys_list#(ad.GetPapersOAI('2014-04-30','2014-05-02','math')
         #+ad.GetPapersOAI('2014-04-30','2014-05-02','cs'))
 
     #remove duplicates, do this the dumb way for now
@@ -26,7 +38,6 @@ if __name__ == '__main__':
         for k in range(j+1,len(paper_list)):
             if paper_list[j].id == paper_list[k].id:
                 unique_flag = False
-                print paper_list[j].title
                 
         if unique_flag:
             unique_paper_list.append(paper_list[j])

### 2014-05-09 Perceptron.py
Added margin perceptron.

@@ -133,6 +133,55 @@ def DotKernel(x,y):
     #multiplication of TextFeatureVectors gives a dot product.
     return x*y
 
+class MarginPerceptronClassifier():
+    "Margin perceptron for online learning """
+    
+    def __init__(self,eta,rho):
+        """ Constructor for margin perceptron, sets learning rate eta and
+        margin rho """
+        
+        self.eta = eta
+        self.rho = rho
+        self.weights = dict()
+
+    def Update(self,x,y_hat,y):
+        """ Update classifier based on incorrect decision """
+        
+        #if weights  == 0
+        
+        w_norm = self.GetWNorm()
+        
+        if (w_norm == 0) or (y*x.Dot(self.weights)/w_norm < self.rho/2.):
+            x.UpdateWeights(self.weights,y,self.eta)
+            
+        return
+
+    def GetWNorm(self):
+        """ Calculate 2-norm of the weight vector """
+        value = 0.
+        for word in self.weights:
+            value += weights[word]**2
+            
+        value = np.sqrt(value)
+
+        return value
+
+    def Predict(self,x):
+        """ predict y by using the sign of a dot product of x with weights """
+
+        return sign(x.Dot(self.weights))        
+
+
+    def __repr__(self):
+        
+        repstring = 'Perceptron Classifier, eta = %1.3f, rho = ' % (self.eta, self.rho)
+        
+        return repstring
+
+
+    __str__ = __repr__
+
+
 class WinnowClassifier():
     
     """ Simple Winnow algorithm for online learning. 
@@ -202,7 +251,19 @@ if __name__ == "__main__":
     
     assert y_hat_2 == -1, "y_hat should be -1 after update, it is not"
 
+
+
+    margin_pclassifier = MarginPerceptronClassifier(0.3,0.02)
     
+    y_hat = margin_pclassifier.Predict(x[0])
+    
+    assert y_hat == 1, "y_hat for margin perceptron should be 1 at initialization, it is not"
+    
+    margin_pclassifier.Update(x[0],y_hat,-1)
+    y_hat_2 = margin_pclassifier.Predict(x[0])
+    
+    assert y_hat_2 == -1, "margin perceptron y_hat should be -1 after update, it is not"
+
     #NOTE: Winnow currently unused
     wclassifier = WinnowClassifier(8,0.3)
     

### 2014-05-09 ArxivData.py
in ArxivData added OAIWrapper and more to GetPapersOAI

@@ -326,6 +326,37 @@ def GetTodaysPapers(subject=''):
             
     return paper_list
 
+def OAIWrapper():
+    print 'Please enter an arXiv category from the following list:'
+    print subject_list
+
+    while True:
+        subject = raw_input()
+        
+        if subject in subject_list:
+            break
+        else:
+            print 'Invalid subject, please choose from list.'
+
+    day = raw_input('Enter a start date in form YYYY-MM-DD:')
+    until = raw_input('Enter an end date in form YYYY-MM-DD:')
+    
+    subcategories = []
+    if subject_dict[subject]:
+        print ('Enter all preferred subcategories from subject as listed below (capitalization). 
+            Enter "done" when finished.')
+        print subject_dict[subject]
+        
+        while True:
+            subcategory = raw_input()
+            if subcategory in subject_dict[subject]:
+                subcategories.append(subcategory)
+            elif subcategory == 'done':
+                break
+            else:
+                print 'Must choose valid subcategory or enter "done" and continue.'
+
+    GetPapersOAI(day=day, until=until, subject=subject, *subcategories)
 
 def GetPapersOAI(day='', until='', subject='', subcategories=None):
     """ 
@@ -350,7 +381,7 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
         'physics:math-ph','physics:nlin','physics:nucl-ex','physics:nucl-th',
         'physics','physics:quant-ph','math','cs','q-bio','q-fin','stat']
     
-    subcategory_list = ['Mathematics - Differential Geometry','Mathematics - Functional Analysis','Mathematics - Numerical Analysis','Mathematics - Probability']
+    #subcategory_list = ['Mathematics - Differential Geometry','Mathematics - Functional Analysis','Mathematics - Numerical Analysis','Mathematics - Probability']
 
     math = ['Algebraic Geometry','Algebraic Topology','Analysis of PDEs','Category Theory',
         'Classical Analysis and ODEs','Combinatorics','Commutative Algebra',
@@ -413,16 +444,29 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
         'physics:nucl-th':[],'physics':physics,'physics:quant-ph':[],'math':math,'cs':cs,
         'q-bio':q_bio,'q-fin':q_fin,'stat':stat}
 
+    subject_name = {'physics:astro-ph':'Astrophysics','physics:cond-mat':'Condensed Matter',
[…]

### 2014-05-09 ArxivData.py
Added ArxivSubjects to maek code a bit cleaner.  Changes to gettestdata and OAI wrapper.  Need to probably remove the commented out subjects.

@@ -9,6 +9,8 @@ from xml.etree import ElementTree as ET
 #import time
 from datetime import datetime
 import cPickle
+import ArxivSubjects as arxs
+import time
 
 class TextFeatureVector:
     """ feature vector, just a dictionary of words present in an abstract, and for each word
@@ -328,35 +330,39 @@ def GetTodaysPapers(subject=''):
 
 def OAIWrapper():
     print 'Please enter an arXiv category from the following list:'
-    print subject_list
+    print arxs.subject_list
 
     while True:
         subject = raw_input()
         
-        if subject in subject_list:
+        if subject in arxs.subject_list:
             break
         else:
             print 'Invalid subject, please choose from list.'
 
     day = raw_input('Enter a start date in form YYYY-MM-DD:')
+    print day
     until = raw_input('Enter an end date in form YYYY-MM-DD:')
+    print until
     
     subcategories = []
-    if subject_dict[subject]:
-        print ('Enter all preferred subcategories from subject as listed below (capitalization). 
-            Enter "done" when finished.')
-        print subject_dict[subject]
+    if arxs.subject_dict[subject]:
+        print ('Enter all preferred subcategories from subject as listed below (capitalization). Enter "done" when finished.')
+        print arxs.subject_dict[subject]
         
         while True:
             subcategory = raw_input()
-            if subcategory in subject_dict[subject]:
+            if subcategory in arxs.subject_dict[subject]:
                 subcategories.append(subcategory)
+                print "Please pick another subcategory or enter 'done'"
             elif subcategory == 'done':
                 break
             else:
                 print 'Must choose valid subcategory or enter "done" and continue.'
 
-    GetPapersOAI(day=day, until=until, subject=subject, *subcategories)
+    paper_list = GetPapersOAI(day=day, until=until, subject=subject, subcategories=subcategories)
+
+    return paper_list
 
 def GetPapersOAI(day='', until='', subject='', subcategories=None):
     """ 
@@ -376,97 +382,97 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
     
 
     #list of all subjects to grab papers from, check if optional argument set is in list
-    subject_list = ['physics:astro-ph','physics:cond-mat','physics:gr-qc',
[…]

### 2014-05-09 ArxivSubjects.py

@@ -1,0 +1,78 @@
+""" This file is just for convenience.  Holds all the hardcoded subjects and subcategories from arxiv. """
+
+subject_list = ['physics:astro-ph','physics:cond-mat','physics:gr-qc',
+                'physics:hep-ex','physics:hep-lat','physics:hep-ph','physics:hep-th',
+                'physics:math-ph','physics:nlin','physics:nucl-ex','physics:nucl-th',
+                'physics','physics:quant-ph','math','cs','q-bio','q-fin','stat']
+
+math = ['Algebraic Geometry','Algebraic Topology','Analysis of PDEs','Category Theory',
+        'Classical Analysis and ODEs','Combinatorics','Commutative Algebra',
+        'Complex Variables','Differential Geometry','Dynamical Systems','Functional Analysis',
+        'General Mathematics','General Topology','Geometric Topology','Group Theory',
+        'History and Overview','Information Theory','K-Theory and Homology','Logic',
+        'Mathematical Physics','Metric Geometry','Number Theory','Numerical Analysis',
+        'Operator Algebras','Optimization and Control','Probability','Quantum Algebra',
+        'Representation Theory','Rings and Algebras','Spectral Theory','Statistics Theory',
+        'Symplectic Geometry']
+
+physics = ['Accelerator Physics','Atmospheric and Oceanic Physics','Atomic Physics',
+        'Atomic and Molecular Clusters','Biological Physics','Chemical Physics','Classical Physics',
+        'Computational Physics','Data Analysis, Statistics and Probability','Fluid Dynamics',
+        'General Physics','Geophysics','History and Philosophy of Physics',
+        'Instrumentation and Detectors','Medical Physics','Optics','Physics Education',
+        'Physics and Society','Plasma Physics','Popular Physics','Space Physics']
+
+astroph = ['Astrophysics of Galaxies','Cosmology and Nongalactic Astrophysics',
+        'Earth and Planetary Astrophysics','High Energy Astrophysical Phenomena',
+        'Instrumentation and Methods for Astrophysics','Solar and Stellar Astrophysics']
+
+cond_mat = ['Disordered Systems and Neural Networks','Materials Science',
+            'Mesoscale and Nanoscale Physics','Other Condensed Matter','Quantum Gases',
+            'Soft Condensed Matter','Statistical Mechanics','Strongly Correlated Electrons',
+            'Superconductivity']
+
[…]

### 2014-05-09 getTestData.py

@@ -6,30 +6,22 @@ from random import shuffle
 paper_list = []
 
 if __name__ == '__main__':
+    
+    # Fetch articles from different subjects.
+    go_again = True
+    while go_again:
+        time.sleep(20)
+        this_paper_list = ad.OAIWrapper()
+        print "Number of Articles found: ", len(this_paper_list)
+        paper_list.extend(this_paper_list)
+        in_str = raw_input("Would you like to look at another subject as well? yes/no.")
 
-    # Note: Modified to be more relevant and increase total number of 
-    #       articles for OfficialTestData2.pkl
+        if in_str in ["yes","Yes","y","Y","1"]:
+            go_again = True
+            print "Waiting for 20 seconds before retrieving data again from arxiv."
+        elif in_str in ["no","No","n","N","0"]:
+            go_again = False
 
-    #originally was 5-30 - 04-02
-    math_list = ad.GetPapersOAI('2014-02-20', '2014-03-08', 'math')
-
-    print "math: ", len(math_list)
-
-    #sleep for 21 , have to do this in order to use OAI MP again
-    time.sleep(21)
-
-    cs_list = ad.GetPapersOAI('2014-02-20', '2014-03-08', 'cs')
-
-    print "cs: ", len(cs_list)
-
-    time.sleep(21)
-
-    phys_list = ad.GetPapersOAI('2014-01-20', '2014-03-10', 'physics')
-
-    print 'math:', len(math_list), ', cs: ', len(cs_list), ', physics: ', len(phys_list)
-
-    paper_list = math_list + cs_list  + phys_list#(ad.GetPapersOAI('2014-04-30','2014-05-02','math')
-        #+ad.GetPapersOAI('2014-04-30','2014-05-02','cs'))
 
     #remove duplicates, do this the dumb way for now
     unique_paper_list = []
@@ -43,7 +35,7 @@ if __name__ == '__main__':
             unique_paper_list.append(paper_list[j])
                 
                 
-    print "total articles: " , len(unique_paper_list)
+    print "total articles after removing duplicates: " , len(unique_paper_list)
 
     shuffle(unique_paper_list)
 

### 2014-05-09 getTestData.py
moved sleep to after getting papers.:

@@ -10,7 +10,6 @@ if __name__ == '__main__':
     # Fetch articles from different subjects.
     go_again = True
     while go_again:
-        time.sleep(20)
         this_paper_list = ad.OAIWrapper()
         print "Number of Articles found: ", len(this_paper_list)
         paper_list.extend(this_paper_list)
@@ -19,6 +18,7 @@ if __name__ == '__main__':
         if in_str in ["yes","Yes","y","Y","1"]:
             go_again = True
             print "Waiting for 20 seconds before retrieving data again from arxiv."
+            time.sleep(20)
         elif in_str in ["no","No","n","N","0"]:
             go_again = False
 

### 2014-05-09 ArxivData.py
Changed files for custom labeling and data.

@@ -380,95 +380,6 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
             range of days within given subject set
     """
     
-
-    #list of all subjects to grab papers from, check if optional argument set is in list
-#    subject_list = ['physics:astro-ph','physics:cond-mat','physics:gr-qc',
-#        'physics:hep-ex','physics:hep-lat','physics:hep-ph','physics:hep-th',
-#        'physics:math-ph','physics:nlin','physics:nucl-ex','physics:nucl-th',
-#        'physics','physics:quant-ph','math','cs','q-bio','q-fin','stat']
-#    
-#    #subcategory_list = ['Mathematics - Differential Geometry','Mathematics - Functional Analysis','Mathematics - Numerical Analysis','Mathematics - Probability']
-#
-#    math = ['Algebraic Geometry','Algebraic Topology','Analysis of PDEs','Category Theory',
-#        'Classical Analysis and ODEs','Combinatorics','Commutative Algebra',
-#        'Complex Variables','Differential Geometry','Dynamical Systems','Functional Analysis',
-#        'General Mathematics','General Topology','Geometric Topology','Group Theory',
-#        'History and Overview','Information Theory','K-Theory and Homology','Logic',
-#        'Mathematical Physics','Metric Geometry','Number Theory','Numerical Analysis',
-#        'Operator Algebras','Optimization and Control','Probability','Quantum Algebra',
-#        'Representation Theory','Rings and Algebras','Spectral Theory','Statistics Theory',
-#        'Symplectic Geometry']
-#
-#    physics = ['Accelerator Physics','Atmospheric and Oceanic Physics','Atomic Physics',
-#        'Atomic and Molecular Clusters','Biological Physics','Chemical Physics','Classical Physics',
-#        'Computational Physics','Data Analysis, Statistics and Probability','Fluid Dynamics',
-#        'General Physics','Geophysics','History and Philosophy of Physics',
-#        'Instrumentation and Detectors','Medical Physics','Optics','Physics Education',
-#        'Physics and Society','Plasma Physics','Popular Physics','Space Physics']
-#
-#    astroph = ['Astrophysics of Galaxies','Cosmology and Nongalactic Astrophysics',
-#        'Earth and Planetary Astrophysics','High Energy Astrophysical Phenomena',
-#        'Instrumentation and Methods for Astrophysics','Solar and Stellar Astrophysics']
-#
[…]

### 2014-05-09 getTestData.py

@@ -7,20 +7,33 @@ paper_list = []
 
 if __name__ == '__main__':
     
+    #get name
+    name = raw_input("Please enter your name (no spaces.)")
+
     # Fetch articles from different subjects.
     go_again = True
     while go_again:
         this_paper_list = ad.OAIWrapper()
         print "Number of Articles found: ", len(this_paper_list)
         paper_list.extend(this_paper_list)
-        in_str = raw_input("Would you like to look at another subject as well? yes/no.")
 
-        if in_str in ["yes","Yes","y","Y","1"]:
-            go_again = True
-            print "Waiting for 20 seconds before retrieving data again from arxiv."
-            time.sleep(20)
-        elif in_str in ["no","No","n","N","0"]:
-            go_again = False
+
+        answered = False
+        while answered == False:
+            in_str = raw_input("Would you like to look at another subject as well? yes/no.")
+
+            if in_str in ["yes","Yes","y","Y","1"]:
+                go_again = True
+                answered = True
+                print "Waiting for 20 seconds before retrieving data again from arxiv."
+                time.sleep(20)
+            elif in_str in ["no","No","n","N","0"]:
+                go_again = False
+                answered = True
+            else:
+                print "Please input yes or no."
+                answered = False
+            
 
 
     #remove duplicates, do this the dumb way for now
@@ -39,7 +52,7 @@ if __name__ == '__main__':
 
     shuffle(unique_paper_list)
 
-    with open('TestData.pkl','wb') as file:
+    with open(name + 'CustomTestData.pkl','wb') as file:
         dump(unique_paper_list,file)
 
 

### 2014-05-09 getTestData.py
small edits.

@@ -56,4 +56,3 @@ if __name__ == '__main__':
         dump(unique_paper_list,file)
 
 
-

### 2014-05-09 ArxivData.py
GetPapersOAI lists papers harvested

@@ -523,6 +523,10 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
 
     # create list of papers
 
+    print len(root.findall('.//{http://www.openarchives.org/OAI/2.0/}record')), 'papers harvested.'
+    if len(root.findall('.//{http://www.openarchives.org/OAI/2.0/}record')) == 1000:
+        print 'Choose smaller date range to receive newer papers.'
+
     start = time.clock()
     for entry in root.findall('.//{http://www.openarchives.org/OAI/2.0/}record'): #, namespaces=ns):
         this_paper = Paper(entry, 'OAI')

### 2014-05-09 ArxivData.py
altered checking date range in IsPaperInSubcategories

@@ -429,7 +429,7 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
         if IsPaperInSubcategories(entry, subcategory_list, ns):
             # check that the paper was published today, not just updated.
             if day and until:
-                if (datetime.strptime(day, '%Y-%m-%d')
+                if (datetime.fromordinal(datetime.strptime(day, '%Y-%m-%d').toordinal()-5)
                     <= datetime.strptime(this_paper.published, '%Y-%m-%d')
                     <= datetime.strptime(until, '%Y-%m-%d')):
                     paper_list.append(this_paper)

### 2014-05-10 getTestData.py
added steven custom labels and data.

@@ -55,4 +55,3 @@ if __name__ == '__main__':
     with open(name + 'CustomTestData.pkl','wb') as file:
         dump(unique_paper_list,file)
 
-

### 2014-05-10 TestClassifiers.py
Added custom data functionality to TestClassifiers.py

@@ -1,5 +1,6 @@
 from ArxivData import FeaturizeAbstracts
 from ArxivData import GetAbstracts
+import random
 import numpy as np
 import cPickle
 from ArxivData import Paper
@@ -13,6 +14,8 @@ from Perceptron import MakePerceptronClassifier
 
 #names of people who contributed labels
 names = ["steven","sid","iantobasco","joey","manas","travis"]
+custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl'}
+custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl'}
 
 #get data
 data_filename = "./OfficialTestData.pkl"
@@ -42,15 +45,43 @@ for cln in range(len(classifier_list)):
             label_file = open(label_filename,"rb")
             labels = cPickle.load(label_file)
 
+            #get extra data and labels
+            if name in custom_data_dict:
+                custom_data_file_name = custom_data_dict[name]
+                custom_label_file_name = custom_label_dict[name]
+            
+                with open(custom_data_file_name,"rb") as custom_data_file:
+                    custom_paper_list = cPickle.load(custom_data_file)
+                    custom_abstracts = GetAbstracts(custom_paper_list)
+                    custom_abstract_vectors = FeaturizeAbstracts(custom_abstracts)
+                    current_data = abstract_vectors + custom_abstract_vectors
+
+                with open(custom_label_file_name,"rb") as custom_label_file:
+                    custom_labels = cPickle.load(custom_label_file)
+                    current_labels = labels + custom_labels
+
+            else:
+                current_data = abstract_vectors
+                current_labels = labels
+
+            #shuffle custom and regular data together
+            packaged_data = [(current_data[i],current_labels[i]) for i in range(len(current_data))]
+            random.seed(1)
+            random.shuffle(packaged_data)
+                
+            for i in range(len(packaged_data)):
+                current_data[i] = packaged_data[i][0]
+                current_labels[i] = packaged_data[i][1]
+
             #initialize counts for accuracy
             n_pos_right = 0
             n_precision_wrong = 0
             n_recall_wrong = 0
-            for i in range(len(abstract_vectors)):
+            for i in range(len(current_data)):
             
-                x = abstract_vectors[i]
+                x = current_data[i]
                 y_hat = classifier.Predict(x)
-                y = labels[i]
[…]

### 2014-05-11 ArxivData.py
Added Classifier Tester, and added creation wrapper for Kernel perceptron.

@@ -68,7 +68,6 @@ class TextFeatureVector:
 
     def UpdateWeights(self,weights,y,eta):
         """ update weights according to the rule weigts = weights + eta*x*y """
-        
         for word in iter(self.words):
             if word in weights:
                 weights[word] = weights[word] + eta*y*self.words[word]/self.total_words
@@ -89,8 +88,39 @@ class TextFeatureVector:
                 weights[word] = C*eta*y*self.words[word]/self.total_words
                 
         return weights
+    
 
+    def __sub__(self,other):
+        """ Subtraction operator """
+        
+        new = TextFeatureVector()x
+        for word in self.words:
+            if word in other.words:
+                new.words[word] = self.words[word] - 
+                
+        
+    def Norm(self):
+        """ calculate norm of a data TextData object """
+        value = 0
+        for word in self.words:
+            value += 
 
+    def Distance2(self,y):
+        """ Calculate distance squared from self to y. 
+            Used for Gaussian Kernel """
+        distance = 0.
+        for word in self.words:
+            if word in y.words:
+                distance += (self.words[word]/self.total_words - y.words[word]/y.total_words)**2
+            else:
+                distance += (self.words[word]/self.total_words)**2
+
+        for word in y.words:
+            if word not in self.words:
+                distance += (y.words/y.total_words)**2
+
+        return distance
+                
     def __str__(self):
         
         string_rep = "{ "

### 2014-05-11 ClassifierTester.py

@@ -1,0 +1,153 @@
+import random
+import numpy as np
+
+
+class ClassifierTester:
+    """ Used to test any of the classifiers we use for abstract classification. """
+    
+    def __init__(self,classifier_creator,gridsearch_parameters,n_params,p):
+        
+        self.n_params = n_params
+        if self.n_params not in [1, 2]:
+            print "number of parameters must be 1 or 2"
+            raise NotImplementedError
+        self.classifier_creator = classifier_creator
+        self.p = p
+
+        self.gridsearch_parameters = gridsearch_parameters
+
+        self.recall_grid = dict()
+        self.precision_grid = dict()
+
+        
+    def Test(self,data,labels):
+        
+        #setup parameters for gridsearch
+        if self.n_params == 1:
+            parameters_list = [[p] for p in self.gridsearch_parameters]
+        elif self.n_params == 2:
+            parameters_list = [[x,y] for x in self.gridsearch_parameters[0] for y in self.gridsearch_parameters[1]]
+
+        for params in parameters_list:
+            
+            #create classifier
+            classifier = self.classifier_creator(params)
+            
+            #initialize counts for accuracy
+            n_pos_right = 0
+            n_precision_wrong = 0
+            n_recall_wrong = 0
+            for i in range(len(data)):
+            
+                x = data[i]
+                y_hat = classifier.Predict(x)
+                y = labels[i]
+                if y == 1 and y_hat == 1:
+                    n_pos_right += 1
+                elif y == -1 and y_hat == -1:
+                    #do nothing, doesn't count as positive correct
+                    pass
+                elif y_hat == 1:
+                    #update on false positive, add one to n_wrong
+                    n_precision_wrong += 1
+                    classifier.Update(x,y_hat,y)
+                else:
+                    #maybe update on false negative, depends on p.
+                    n_recall_wrong += 1
+                    k = np.random.binomial(1,self.p)
+                    if k == 1:
+                        classifier.Update(x,y_hat,y)
+                    
+#            print "Total preferred papers: ", n_pos_right + n_recall_wrong
+            if n_pos_right != 0:
+                self.recall_grid[self._ParamsToString(params)] = float(n_pos_right)/float(n_pos_right + n_recall_wrong)
+                self.precision_grid[self._ParamsToString(params)] = float(n_pos_right)/float(n_pos_right + n_precision_wrong)
+            else:
+                self.recall_grid[self._ParamsToString(params)] = 0.0
+                self.precision_grid[self._ParamsToString(params)] = 0.0
+
[…]

### 2014-05-11 Perceptron.py

@@ -24,6 +24,7 @@ class PerceptronClassifier:
         self.weights = dict()
         self.n_correct = 0
         self.n_wrong = 0
+        self.name = "Perceptron Classifier"
         
     def Update(self,x,y_hat,y):
         """ given that the Perceptron has guessed y_hat for data x, update it 
@@ -89,6 +90,7 @@ class KernelPerceptronClassifier():
         self.kernel = kernel
         self.n_correct = 0
         self.n_wrong = 0
+        self.name = "Kernel Perceptron Clasifier"
         
         
     def Update(self,x,y_hat,y):
@@ -133,6 +135,35 @@ def DotKernel(x,y):
     #multiplication of TextFeatureVectors gives a dot product.
     return x*y
 
+
+def MakeGaussianKernel(sigma):
+    """ create a function which is a 
+    Gaussian Kernel exp(-||x - x'||^2/(2 sigma^2))
+    """
+    
+    def GaussianKernel(x,y):
+        
+        return np.exp(x.Distance2(y)/(2.*sigma))
+    
+    return GaussianKernel
+                      
+
+def MakeGaussianKernelPerceptronClassifier(parameters):
+    """ wrapper to make Gaussian Kernel Perceptron from a list of 
+    parameters:
+        parameters[0] = learning rate
+        parameters[1] = sigma, variance of kernel
+    """
+
+    g_kernel = MakeGaussianKernel(parameters[1])
+    
+    kclassifier = KernelPerceptronClassifier(parameters[0],g_kernel)
+
+    return klassifier
+    
+    
+    
+
 class MarginPerceptronClassifier():
     "Margin perceptron for online learning """
     
@@ -143,6 +174,7 @@ class MarginPerceptronClassifier():
         self.eta = eta
         self.rho = rho
         self.weights = dict()
+        self.name = "Margin Perceptron Classifer"
 
     def Update(self,x,y_hat,y):
         """ Update classifier based on incorrect decision """
@@ -209,6 +241,7 @@ class WinnowClassifier():
         self.weights = np.ones(n)/n
         self.n_correct = 0
         self.n_wrong = 0
+        self.name = "Winnow Classifer"
         
         
     def Update(self,x,y_hat,y):

### 2014-05-11 TestClassifiers.py

@@ -11,154 +11,9 @@ from Perceptron import PerceptronClassifier
 from Perceptron import MakePerceptronClassifier
 from Perceptron import MarginPerceptronClassifier
 from Perceptron import MakeMarginPerceptronClassifier
+from ClassifierTester import ClassifierTester
 
 
-
-class ClassifierTester:
-    """ Used to test any of the classifiers we use for abstract classification. """
-    
-    def __init__(self,classifier_creator,gridsearch_parameters,n_params,p):
-        
-        self.n_params = n_params
-        if self.n_params not in [1, 2]:
-            print "number of parameters must be 1 or 2"
-            raise NotImplementedError
-        self.classifier_creator = classifier_creator
-        self.p = p
-
-        self.gridsearch_parameters = gridsearch_parameters
-
-        self.recall_grid = dict()
-        self.precision_grid = dict()
-
-        
-    def Test(self,data,labels):
-        
-        #setup parameters for gridsearch
-        if self.n_params == 1:
-            parameters_list = [[p] for p in self.gridsearch_parameters]
-        elif self.n_params == 2:
-            parameters_list = [[x,y] for x in self.gridsearch_parameters[0] for y in self.gridsearch_parameters[1]]
-
-        for params in parameters_list:
-            
-            #create classifier
-            classifier = self.classifier_creator(params)
-            
-            #initialize counts for accuracy
-            n_pos_right = 0
-            n_precision_wrong = 0
-            n_recall_wrong = 0
-            for i in range(len(data)):
-            
-                x = data[i]
-                y_hat = classifier.Predict(x)
-                y = labels[i]
-                if y == 1 and y_hat == 1:
-                    n_pos_right += 1
-                elif y == -1 and y_hat == -1:
-                    #do nothing, doesn't count as positive correct
-                    pass
-                elif y_hat == 1:
-                    #update on false positive, add one to n_wrong
-                    n_precision_wrong += 1
-                    classifier.Update(x,y_hat,y)
-                else:
-                    #maybe update on false negative, depends on p.
-                    n_recall_wrong += 1
-                    k = np.random.binomial(1,self.p)
-                    if k == 1:
-                        classifier.Update(x,y_hat,y)
-                    
-#            print "Total preferred papers: ", n_pos_right + n_recall_wrong
-            if n_pos_right != 0:
[…]

### 2014-05-11 ArxivData.py
Fixed some issues with kernel perceptron

@@ -88,22 +88,6 @@ class TextFeatureVector:
                 weights[word] = C*eta*y*self.words[word]/self.total_words
                 
         return weights
-    
-
-    def __sub__(self,other):
-        """ Subtraction operator """
-        
-        new = TextFeatureVector()x
-        for word in self.words:
-            if word in other.words:
-                new.words[word] = self.words[word] - 
-                
-        
-    def Norm(self):
-        """ calculate norm of a data TextData object """
-        value = 0
-        for word in self.words:
-            value += 
 
     def Distance2(self,y):
         """ Calculate distance squared from self to y. 
@@ -117,7 +101,7 @@ class TextFeatureVector:
 
         for word in y.words:
             if word not in self.words:
-                distance += (y.words/y.total_words)**2
+                distance += (y.words[word]/y.total_words)**2
 
         return distance
                 

### 2014-05-11 ClassifierTester.py

@@ -68,7 +68,6 @@ class ClassifierTester:
 
     def ReportGrid(self):
         
-
         if self.n_params == 1:
             classifier = self.classifier_creator([0.0])
             print classifier.name
@@ -137,6 +136,12 @@ class ClassifierTester:
 
                 
             return
+
+
+    def ReportBest(self):
+        """ Report best classifier """
+    
+    
 
     def _ParamsToString(self,params):
         """ helper function to turn params into a 

### 2014-05-11 Perceptron.py

@@ -159,7 +159,7 @@ def MakeGaussianKernelPerceptronClassifier(parameters):
     
     kclassifier = KernelPerceptronClassifier(parameters[0],g_kernel)
 
-    return klassifier
+    return kclassifier
     
     
     

### 2014-05-11 TestClassifiers.py

@@ -11,6 +11,8 @@ from Perceptron import PerceptronClassifier
 from Perceptron import MakePerceptronClassifier
 from Perceptron import MarginPerceptronClassifier
 from Perceptron import MakeMarginPerceptronClassifier
+from Perceptron import MakeGaussianKernelPerceptronClassifier
+from Perceptron import KernelPerceptronClassifier
 from ClassifierTester import ClassifierTester
 
 
@@ -32,15 +34,16 @@ if __name__ == "__main__":
     etas = [1.0]
     rhos = [2**(-7),2**(-6),2**(-5),2**(-4),2**(-3),2**(-2)]
     Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0, 4.0, 8.0, 16.0, 32.0]
-    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier]
-    parameters_list = [etas, [etas,rhos], [etas,Cs]]
+    sigmas = [0.005, 0.01, 0.02, 0.04, 0.1, 0.5, 1.0]
+    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier]
+    parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas]]
     nparams_list = [1, 2, 2, 2]
                       
     
 #go through all classifiers to test
     for cln in range(len(classifier_list)):
         
-        for p in [1.0, 0.1, 'adaptive']:
+        for p in [1.0, 0.1]:
             print "P value is: ", p
         #go through labeled data a few times, 
             for name in names:

### 2014-05-12 ClassifierTester.py
Fixed some kernel perceptron stuff.

@@ -141,7 +141,6 @@ class ClassifierTester:
     def ReportBest(self):
         """ Report best classifier """
     
-    
 
     def _ParamsToString(self,params):
         """ helper function to turn params into a 

### 2014-05-12 ArxivData.py
added polynomial kernel and adaptive p testing.

@@ -2,11 +2,9 @@
     document preferences.  """
 
 import urllib
-import re #for removing namespaces, featurizing abstracts
+import re
 import sys
 from xml.etree import ElementTree as ET
-#from sklearn.feature_extraction.text import TfidfVectorizer
-#import time
 from datetime import datetime
 import cPickle
 import ArxivSubjects as arxs

### 2014-05-12 ClassifierTester.py

@@ -13,6 +13,8 @@ class ClassifierTester:
             raise NotImplementedError
         self.classifier_creator = classifier_creator
         self.p = p
+        if self.p == 'adaptive':
+            self.current_p = 1.0
 
         self.gridsearch_parameters = gridsearch_parameters
 
@@ -37,6 +39,7 @@ class ClassifierTester:
             n_pos_right = 0
             n_precision_wrong = 0
             n_recall_wrong = 0
+            total_negative_checks = 0
             for i in range(len(data)):
             
                 x = data[i]
@@ -45,8 +48,17 @@ class ClassifierTester:
                 if y == 1 and y_hat == 1:
                     n_pos_right += 1
                 elif y == -1 and y_hat == -1:
-                    #do nothing, doesn't count as positive correct
-                    pass
+                    #update total_negative_checks count if we had to check, 
+                    # and for adaptive p, update value of current_p
+                    if self.p == 'adaptive':
+                        #got it correct, reduce p towards 0.01, our minimum
+                        if np.random.binomial(1,self.current_p) == 1:
+                            self.current_p = 0.9*self.current_p + 0.001
+                            total_negative_checks += 1
+                    else:
+                        if np.random.binomial(1,self.p) == 1:
+                            total_negative_checks += 1
+
                 elif y_hat == 1:
                     #update on false positive, add one to n_wrong
                     n_precision_wrong += 1
@@ -54,11 +66,22 @@ class ClassifierTester:
                 else:
                     #maybe update on false negative, depends on p.
                     n_recall_wrong += 1
-                    k = np.random.binomial(1,self.p)
-                    if k == 1:
-                        classifier.Update(x,y_hat,y)
+                    if self.p == 'adaptive':
+                        # got it wrong, move current_p toward 1.0
+                        # to check more frequently
+                        k = np.random.binomial(1,self.current_p)
+                        if k == 1:
+                            total_negative_checks += 1
+                            classifier.Update(x,y_hat,y)
+                            self.current_p = 0.4*self.current_p + 0.6
+                    else:
+                        k = np.random.binomial(1,self.p)
+                        if k == 1:
+                            total_negative_checks += 1
+                            classifier.Update(x,y_hat,y)
+
                     
-#            print "Total preferred papers: ", n_pos_right + n_recall_wrong
+            print "Total Negative Checks: ", total_negative_checks
             if n_pos_right != 0:
[…]

### 2014-05-12 Perceptron.py

@@ -160,9 +160,35 @@ def MakeGaussianKernelPerceptronClassifier(parameters):
     kclassifier = KernelPerceptronClassifier(parameters[0],g_kernel)
 
     return kclassifier
+
+
+def MakePolynomialKernel(c,d):
+    """ create a function which is a 
+    Polynomial Kernel 
+    """
     
+    def PolynomialKernel(x,y):
+        
+        return (x*y + c)**d
     
+    return PolynomialKernel
+                      
+
+def MakePolynomialKernelPerceptronClassifier(parameters):
+    """ wrapper to make Polynomial Kernel Perceptron from a list of 
+    parameters:
+        parameters[0] = c, constant offset
+        parameters[1] = d, degree of polynomial kernel
+        
+        learning rate, eta, is set to a constant 1.0
+    """
+
+    p_kernel = MakePolynomialKernel(parameters[0],parameters[1])
     
+    kclassifier = KernelPerceptronClassifier(1.0,p_kernel)
+
+    return kclassifier
+
 
 class MarginPerceptronClassifier():
     "Margin perceptron for online learning """

### 2014-05-12 TestClassifiers.py

@@ -12,6 +12,7 @@ from Perceptron import MakePerceptronClassifier
 from Perceptron import MarginPerceptronClassifier
 from Perceptron import MakeMarginPerceptronClassifier
 from Perceptron import MakeGaussianKernelPerceptronClassifier
+from Perceptron import MakePolynomialKernelPerceptronClassifier
 from Perceptron import KernelPerceptronClassifier
 from ClassifierTester import ClassifierTester
 
@@ -35,15 +36,16 @@ if __name__ == "__main__":
     rhos = [2**(-7),2**(-6),2**(-5),2**(-4),2**(-3),2**(-2)]
     Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0, 4.0, 8.0, 16.0, 32.0]
     sigmas = [0.005, 0.01, 0.02, 0.04, 0.1, 0.5, 1.0]
-    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier]
-    parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas]]
-    nparams_list = [1, 2, 2, 2]
+    cs = [-0.5, -0.25, -0.125, -0.0625, 0.0, 0.0625, 0.125, 0.25]
+    ds = [1, 2, 3, 4]
+    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier]
+    parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas], [cs, ds]]
+    nparams_list = [1, 2, 2, 2, 2]
                       
-    
 #go through all classifiers to test
     for cln in range(len(classifier_list)):
-        
-        for p in [1.0, 0.1]:
+
+        for p in [1.0, 0.1, 'adaptive']:
             print "P value is: ", p
         #go through labeled data a few times, 
             for name in names:
@@ -84,57 +86,7 @@ if __name__ == "__main__":
                     current_data[i] = packaged_data[i][0]
                     current_labels[i] = packaged_data[i][1]
 
-
                 classifier_tester.Test(current_data,current_labels)
                 classifier_tester.ReportGrid()
                         
-                #initialize counts for accuracy
-#                n_pos_right = 0
-#                n_precision_wrong = 0
[…]

### 2014-05-12 Paper.tex
added Paper.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb}
\pagestyle{myheadings}
\markright{Joseph McDonald}

\textwidth=7in
\textheight= 9in

\topmargin=-0.5in
\oddsidemargin=-0.25in

\newcommand{\xbar}{\bar{x}}
\newcommand{\V}[1]{\boldsymbol{#1}}
\newcommand{\E}[0]{\mathbb{E}}

\begin{document}
\title{Online Learning Your arXiv Preferences}
\author{Steve Delong and Joey McDonald}
\maketitle
\begin{abstract}
Our goal was to construct a tool that feeds a user a selection of abstracts of papers from the online database, arXiv.org, recieves a label indicating whether the user is interested in that article or not, and progressively learns the users preferences through an online learning algorithm. It uses this information to present articles that it believes the user will like. We created and tested this using a few sample users' preferences including each of ours. Beyond constructing the tool we found some theoretical justification for bounding the number of updates in expectation while only presenting a fraction of samples that are predicted to be uninteresting.
\end{abstract}

\section{Introduction}

The online database arXiv receives several thousand new submissions a month, and sifting through those articles even in just a single subfield to find one of particular interest can be a daunting task. Since arXiv conveniently stores metadata of its submissions in a fairly accessible XML format, a program that compiles and uses this metadata to find papers matching particular research interests could be a great tool for the scientists intending to peruse new research. Essentially this would serve as a ``Pandora," the music recommendation engine, for math, physics, and computer science papers, and it would work by learning the preferences of the user.

The metadata for each article includes an abstract, which should contain enough information to determine the relevance of the article. We decided that performing text classification using the words in the abstracts would give us the feature data needed to create a learning algorithm that would present interesting papers to the user and filter out those that fall outside the user's research interest. Furthermore it seemed most useful that the tool employ online learning, receiving a paper, extracting feature data and obtaining labels from the user, and updating the hypothesis one article at a time, so that the tool can present abstracts while getting progressively more accurate.

One of the important aspects of the algorithm is that it present some articles predicted to be uninteresting. Otherwise there is risk in mislabeling and potentially discarding many articles that are interesting to the user. Nevertheless the goal is to have an active filter on the articles lest the whole purpose of the program be defeated. Since there must be a balance between presenting only interesting articles and having a full understanding of the user's interests, we must choose what fraction of uninteresting articles are presented. In the following section we present a bound on the number of updates made by the Perceptron algorithm we employ, justifying why the algorithm may work towards an accurate hypothesis while receiving labels for only a fraction of the samples labeled uninteresting.

In Section 3, we describe the main components of the program in the python modules we created, and give a description on how to use the tool. We present our results in Section 4, followed by other observations and concluding remarks.

%it is important that not all papers that are predicted uninteresting be discarded by the engine. Without the true there is risk in

\section{Some Theory: Bounding Updates}

The main engine behind the tool is a modified Perceptron algorithm which employs an accept-reject method among the papers it labels uninteresting. The following pseudocode details the algorithm, where $x_t$ denotes feature data, $y_t$ denotes labels, $\widehat{y}_t$ are predictions, $w_t$ are hypotheses, and $k_t$ are i.i.d. random variables used for the accept-reject method. $k_t = 1$ with probability $p$ and $k_t = 0$ with probability $1-p$.\\

\noindent Modified Perceptron algorithm:
\begin{quotation}
%\noindent Modified Perceptron:\\
\noindent $w_1=0$\\
{\tt for $t=1$ to $T$}:\\
\indent receive($x_t$)\\
\indent $\widehat{y}_t=\mbox{sign}(w_t\cdot x_t)$\\
\indent {\tt if} $\widehat{y}_t =1$ {\tt or} ($\widehat{y}_t =0$ {\tt and} $k_t = 1$):\\
\indent\indent receive($y_t$)\\
\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
\indent\indent {\tt else $w_{t+1} = w_t$}\\
\indent {\tt else if $\widehat{y}_t = 0$ and $k_t=0$}:\\
\indent\indent $w_{t+1} = w_t$\\
{\tt return $w_{T+1}$}

\end{quotation}

As mentioned, if the algorithm only made updates when $\widehat{y}=1$ (i.e. interesting) then this would leave the number of mistakes made when $\widehat{y} = 0$ unchecked (and, hence, several lost interesting articles). As a compromise, we generate the i.i.d. variables $k_i$ for each observation when $\widehat{y} = 0$. Note that if $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=0$, the algorithm does not ask for the correct label, and makes no update.

Let $I_1$ be the set of $t$ where a mistake was made and
$\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
$\hat{y} = 0, k = 1$, and let $I_3$ be the set where a mistake was
made, $\hat{y} = 0$ and $k = 0$. Finally, let $M_i = |I_i|$ for $i =
1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
$M$ in the usual perceptron case.  We assume that there exits a $\rho$
and $R$ satisfying the assumptions of Theorem 7.8 from our text, and a separating hyperplane determined by the vector $v$. Let $M' = M_1 + M_2$, then
\begin{align*}
M' =&\ \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2} y_t\V{x}_t \
 \leq   \left\|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t\right\| \\
=& \ \left\|\sum_{t \in I_1 \cup I_2} (\V{w}_{t+1} - \V{w}_t) \right\| 
= \ \|\V{w}_{T+1} \| \\
=&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 - \|\V{w}_t\|^2 }\\
= &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
  \|\V{w}_t\|^2 }\\
= &\ \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
  \|\V{x}_t\|^2} \\
\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
\sqrt{M'r^2} \end{align*}
This implies that $M' \leq \frac{r^2}{\rho^2}$.
We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
Here we revert to a weaker bound, considering the expectation of
$M_3$. Since 
\[M_3 = \sum_{i=1}^m 1_{\left\{\hat{y}_i = 0 \cap y_i = 1\right\}}1_{k_i = 0}, \]
we get that
\begin{align*}
\E[M_3] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 0}] \\
 = &\ (1 - p)\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}],
\end{align*}
where the last equality used the fact that $k_i$ is independent of the data.  Now we want to control the sum of expectations in this expression, and to do this we consider the expectation of $M_2$.
\begin{align*}
M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}1_{k_i = 1} \\
\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\\
\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
\end{align*}
We may then apply the crude bound $\E[M_3] \leq  \frac{1-p}{p}
M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
\begin{align*}
\E[M]  =  &\ \E[M'] + \E[M_3] \\
\leq & \ \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
\leq  & \ \frac{1}{p}\frac{r^2}{\rho^2} \\
\end{align*}
Note that this is a weak bound.  Not only is it greater than the
original perceptron bound by a factor of $\frac{1}{p}$, it is also only a
bound in expectation.

\end{document}

%GIVE THE ALGORITHM THEN PRESENT THE BOUND

%Recommendation engines have become an important feature of many services on the internet, and

% We envisioned that eventually after receiving enough data the tool can tailor the articles it presents to the preferences of the user and offer mostly articles that are ``interesting." The tool would sometimes offer articles it predicts that are uninteresting in order to get a full

\end{document}

### 2014-05-12 Paper.tex
added basic bar raphs for Precision and Recall.

@@
 \indent $\widehat{y}_t=\mbox{sign}(w_t\cdot x_t)$\\
-\indent {\tt if} $\widehat{y}_t =1$ {\tt or} ($\widehat{y}_t =0$ {\tt and} $k_t = 1$):\\
+\indent {\tt if} $\widehat{y}_t =1$ {\tt or} ($\widehat{y}_t =-1$ {\tt and} $k_t = 1$):\\
 \indent\indent receive($y_t$)\\
@@
 \indent\indent {\tt else $w_{t+1} = w_t$}\\
-\indent {\tt else if $\widehat{y}_t = 0$ and $k_t=0$}:\\
+\indent {\tt else if $\widehat{y}_t = -1$ and $k_t=0$}:\\
 \indent\indent $w_{t+1} = w_t$\\
@@
 As mentioned, if the algorithm only made updates when $\widehat{y}=1$ (i.e.
-interesting) then this would leave the number of mistakes made when $\widehat{y} = 0$ unchecked (and, hence, several lost interesting articles).
+interesting) then this would leave the number of mistakes made when $\widehat{y} = -1$ unchecked (and, hence, several lost interesting articles).
 As a compromise, we generate the i.i.d.
@@
 Let $I_1$ be the set of $t$ where a mistake was made and
-$\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
-$\hat{y} = 0, k = 1$, and let $I_3$ be the set where a mistake was
-made, $\hat{y} = 0$ and $k = 0$. Finally, let $M_i = |I_i|$ for $i =
+$\hat{y}=1$ (false positives).  Let $I_2$ be the set where a mistake was made and
+$\hat{y} = -1, k = 1$ (false negatives where the algorithm updates), and let $I_3$ be the set where a mistake was
+made, $\hat{y} = -1$ and $k = 0$ (false negatives where the algorithm does \bold{not} make an update). Finally, let $M_i = |I_i|$ for $i =
 1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
@@
 \begin{align*}
-M' =&\ \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2} y_t\V{x}_t \
+M' \rho =&\ \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2} y_t\V{x}_t \
  \leq   \left\|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t\right\| \\
@@
 This implies that $M' \leq \frac{r^2}{\rho^2}$.
-We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
+We then have that $M = M' + M_3$, so we would like a bound on $M_3$, the number of mistakes made that the algorithm does not update on.
 Here we revert to a weaker bound, considering the expectation of
@@
 \begin{align*}
-M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}1_{k_i = 1} \\
-\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
-= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\\
+M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}1_{k_i = 1} \\
+\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
+= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}]\\
 \Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]

### 2014-05-12 ArxivData.py

@@ -539,17 +539,27 @@ def FeaturizeAbstracts(abstracts):
         abstract_vectors  -  list of TextFeatureVectors, one for each abstract.
 
     """
-    stop_words = ["is","it","that","the","a","an","of","in","this","and"]
+    stop_words = ["is","it","that","the","a","an","of","in","this","and","if","by","are","when","not","with","at","on","also","to"]
 
     feature_list = []
     #initialize feature vector
     for abstract in abstracts:
         text_features = TextFeatureVector()
-    
-        bag_of_words = re.findall(r"[\w']+",abstract)
-        for word in bag_of_words:
-            word = word.lower()
+        abstract_cleaned = re.sub(r'\$\$[^$]*\$\$','',abstract)
+        abstract_cleaned = re.sub(r'\$[^$]*\$','',abstract_cleaned)
+        
+#        abstract_cleaned = re.sub(r'\\begin{align[^\(\end\)]*\\end{align\*?}','',abstract_cleaned)
+        abstract_cleaned = re.sub(r'\$[^$]*\$','',abstract_cleaned)
+        
+        bag_of_words = re.findall(r"[\w']+",abstract_cleaned)
+        for k in range(len(bag_of_words)):
+            word = bag_of_words[k].lower()
             if word not in stop_words:
+ #               if word == "t":
+ #                   print "T CAME FROM"
+ #                   print abstract_cleaned
+                    
+
                 text_features.AddWord(word)
 
         feature_list.append(text_features)

### 2014-05-12 ClassifierTester.py

@@ -5,8 +5,9 @@ import numpy as np
 class ClassifierTester:
     """ Used to test any of the classifiers we use for abstract classification. """
     
-    def __init__(self,classifier_creator,gridsearch_parameters,n_params,p):
+    def __init__(self,classifier_creator,gridsearch_parameters,n_params,p,classifier_name):
         
+        self.classifier_name = classifier_name
         self.n_params = n_params
         if self.n_params not in [1, 2]:
             print "number of parameters must be 1 or 2"
@@ -81,13 +82,16 @@ class ClassifierTester:
                             classifier.Update(x,y_hat,y)
 
                     
-            print "Total Negative Checks: ", total_negative_checks
+#            print "Total Negative Checks: ", total_negative_checks
             if n_pos_right != 0:
                 self.recall_grid[self._ParamsToString(params)] = float(n_pos_right)/float(n_pos_right + n_recall_wrong)
                 self.precision_grid[self._ParamsToString(params)] = float(n_pos_right)/float(n_pos_right + n_precision_wrong)
             else:
                 self.recall_grid[self._ParamsToString(params)] = 0.0
                 self.precision_grid[self._ParamsToString(params)] = 0.0
+                
+#            if self.classifier_name == "Perceptron":
+#                classifier.ReportHighestWeights()
 
     def ReportGrid(self):
         
@@ -161,9 +165,66 @@ class ClassifierTester:
             return
 
 
-    def ReportBest(self):
-        """ Report best classifier """
-    
+    def ReportBestRecall(self):
+        """ Report best classifier by recall
+        
+        inputs:
+              none
+
+        outputs:
+              best_param - the parameter set that gave the best recall
+              max_recall - the value of the recall of this classifier with
+                           the best parameters
+        """
+
+        #setup parameters for gridsearch
+        if self.n_params == 1:
+            parameters_list = [[p] for p in self.gridsearch_parameters]
+        elif self.n_params == 2:
+            parameters_list = [[x,y] for x in self.gridsearch_parameters[0] for y in self.gridsearch_parameters[1]]
+
+        
+        max_recall = 0.
+        best_param = None
+        #go through all parameters tested by this object, and return
+        # the parameters that gave the best recall
+        for param in parameters_list:
+            if self.recall_grid[self._ParamsToString(param)] > max_recall:
+                max_recall = self.recall_grid[self._ParamsToString(param)]
+                best_param = param
+
+        return best_param, max_recall
+
+
+    def ReportBestPrecision(self):
+        """ Report best classifier by precision
+        
[…]

### 2014-05-12 Perceptron.py

@@ -59,6 +59,21 @@ class PerceptronClassifier:
     
     __str__ = __repr__
 
+    def ReportHighestWeights(self):
+        #HACK: report the words with the largest absolute weights
+        
+        words_and_weights = [(self.weights[word],word) for word in self.weights]
+            
+        sort_wandw = sorted(words_and_weights, reverse=True)
+        print "10 Most Positive words:"
+        for k in range(10):
+            print sort_wandw[k][1], sort_wandw[k][0]
+        print "10 Most Negative words:"
+        for k in range(10):
+            print sort_wandw[-k][1], sort_wandw[-k][0]
+            
+            
+
 
 #wrapper functions to set up classifiers for testing
 def MakePerceptronClassifier(parameters):

### 2014-05-12 TestClassifiers.py

@@ -1,8 +1,9 @@
-from ArxivData import FeaturizeAbstracts
-from ArxivData import GetAbstracts
 import random
 import numpy as np
 import cPickle
+from matplotlib import pyplot
+from ArxivData import FeaturizeAbstracts
+from ArxivData import GetAbstracts
 from ArxivData import Paper
 from ArxivData import PromptUser
 from OnlineSVM import OnlineSVMClassifier
@@ -32,6 +33,7 @@ if __name__ == "__main__":
     abstracts = GetAbstracts(paper_list)
     abstract_vectors = FeaturizeAbstracts(abstracts)
     
+    #set up lists of parameters and classifiers for grid searches
     etas = [1.0]
     rhos = [2**(-7),2**(-6),2**(-5),2**(-4),2**(-3),2**(-2)]
     Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0, 4.0, 8.0, 16.0, 32.0]
@@ -39,19 +41,22 @@ if __name__ == "__main__":
     cs = [-0.5, -0.25, -0.125, -0.0625, 0.0, 0.0625, 0.125, 0.25]
     ds = [1, 2, 3, 4]
     classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier]
+    classifier_names = ["Perceptron","Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron"]
     parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas], [cs, ds]]
     nparams_list = [1, 2, 2, 2, 2]
+    
                       
 #go through all classifiers to test
     for cln in range(len(classifier_list)):
 
         for p in [1.0, 0.1, 'adaptive']:
             print "P value is: ", p
-        #go through labeled data a few times, 
-            for name in names:
+            for k in range(len(names)):
+                #use k to determine plots
+                name = names[k]
                 print "User: ", name
                 #create classifier tester
-                classifier_tester = ClassifierTester(classifier_list[cln],parameters_list[cln],nparams_list[cln],p)
+                classifier_tester = ClassifierTester(classifier_list[cln],parameters_list[cln],nparams_list[cln],p,classifier_names[cln])
 
             #get labels
[…]

### 2014-05-12 ClassifierTester.py
added travis custom labels.  Added more to plots.

@@ -21,6 +21,7 @@ class ClassifierTester:
 
         self.recall_grid = dict()
         self.precision_grid = dict()
+        self.neg_update_grid = dict()
 
         
     def Test(self,data,labels):
@@ -42,7 +43,6 @@ class ClassifierTester:
             n_recall_wrong = 0
             total_negative_checks = 0
             for i in range(len(data)):
-            
                 x = data[i]
                 y_hat = classifier.Predict(x)
                 y = labels[i]
@@ -81,8 +81,11 @@ class ClassifierTester:
                             total_negative_checks += 1
                             classifier.Update(x,y_hat,y)
 
-                    
-#            print "Total Negative Checks: ", total_negative_checks
+
+
+                            
+            self.neg_update_grid[self._ParamsToString(params)] = total_negative_checks
+            
             if n_pos_right != 0:
                 self.recall_grid[self._ParamsToString(params)] = float(n_pos_right)/float(n_pos_right + n_recall_wrong)
                 self.precision_grid[self._ParamsToString(params)] = float(n_pos_right)/float(n_pos_right + n_precision_wrong)
@@ -90,9 +93,6 @@ class ClassifierTester:
                 self.recall_grid[self._ParamsToString(params)] = 0.0
                 self.precision_grid[self._ParamsToString(params)] = 0.0
                 
-#            if self.classifier_name == "Perceptron":
-#                classifier.ReportHighestWeights()
-
     def ReportGrid(self):
         
         if self.n_params == 1:
@@ -175,6 +175,8 @@ class ClassifierTester:
               best_param - the parameter set that gave the best recall
               max_recall - the value of the recall of this classifier with
                            the best parameters
+             best_neg_updates - number of times algorithm asked for a label on
+                                a negative prediction.
         """
 
         #setup parameters for gridsearch
@@ -186,14 +188,16 @@ class ClassifierTester:
         
         max_recall = 0.
         best_param = None
+        best_neg_updates = 0
         #go through all parameters tested by this object, and return
         # the parameters that gave the best recall
         for param in parameters_list:
             if self.recall_grid[self._ParamsToString(param)] > max_recall:
                 max_recall = self.recall_grid[self._ParamsToString(param)]
                 best_param = param
+                best_neg_updates = self.neg_update_grid[self._ParamsToString(param)]
 
-        return best_param, max_recall
+        return best_param, max_recall, best_neg_updates
 
 
     def ReportBestPrecision(self):
[…]

### 2014-05-12 TestClassifiers.py

@@ -23,8 +23,8 @@ from ClassifierTester import ClassifierTester
 if __name__ == "__main__":
 #names of people who contributed labels
     names = ["steven","sid","iantobasco","joey","manas","travis"]
-    custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl'}
-    custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl'}
+    custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
+    custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
     
 #get data
     data_filename = "./OfficialTestData.pkl"
@@ -35,14 +35,17 @@ if __name__ == "__main__":
     
     #set up lists of parameters and classifiers for grid searches
     etas = [1.0]
-    rhos = [2**(-7),2**(-6),2**(-5),2**(-4),2**(-3),2**(-2)]
-    Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0, 4.0, 8.0, 16.0, 32.0]
-    sigmas = [0.005, 0.01, 0.02, 0.04, 0.1, 0.5, 1.0]
-    cs = [-0.5, -0.25, -0.125, -0.0625, 0.0, 0.0625, 0.125, 0.25]
+    rhos = [2**(-8), 2**(-7),2**(-6),2**(-5)]
+    Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0]
+    sigmas = [0.01, 0.02, 0.04,0.2, 1.0]
+    cs = [-0.25, -0.125, -0.0625, -0.03125, 0.0, 0.03125, 0.0625, 0.125]
     ds = [1, 2, 3, 4]
     classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier]
     classifier_names = ["Perceptron","Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron"]
[…]

### 2014-05-13 ClassifierTester.py
added more to visualization.  Removed some un-useful parameters from gridsearch.

@@ -185,7 +185,6 @@ class ClassifierTester:
         elif self.n_params == 2:
             parameters_list = [[x,y] for x in self.gridsearch_parameters[0] for y in self.gridsearch_parameters[1]]
 
-        
         max_recall = 0.
         best_param = None
         best_neg_updates = 0

### 2014-05-13 TestClassifiers.py

@@ -40,10 +40,22 @@ if __name__ == "__main__":
     sigmas = [0.01, 0.02, 0.04,0.2, 1.0]
     cs = [-0.25, -0.125, -0.0625, -0.03125, 0.0, 0.03125, 0.0625, 0.125]
     ds = [1, 2, 3, 4]
+    
+    #liss of classifiers and their names
     classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier]
     classifier_names = ["Perceptron","Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron"]
-    classifier_r_labels = range(len(classifier_names))
-    classifier_p_labels = range(len(classifier_names))
+
+
+    #set up empty lists for labels on bar graphs
+    classifier_r_labels = dict()
+    for name in names:
+        classifier_r_labels[name] = range(len(classifier_names))
+    classifier_p_labels = dict()
+    for name in names:
+        classifier_p_labels[name] = range(len(classifier_names))
+
+
+    #set up parameters and their names                                      
     parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas], [cs, ds]]
     parameter_names = [["eta"],["eta","rho"],["eta","C"],["eta","sigma"],["c","d"]]
     nparams_list = [1, 2, 2, 2, 2]
@@ -52,8 +64,10 @@ if __name__ == "__main__":
 #go through all classifiers to test
     for cln in range(len(classifier_list)):
 
+        #go through values for p
         for p in [1.0, 0.1, 'adaptive']:
             print "P value is: ", p
+            #go through users
             for k in range(len(names)):
                 #use k to determine plots
                 name = names[k]
@@ -62,7 +76,7 @@ if __name__ == "__main__":
                 #create classifier tester
                 classifier_tester = ClassifierTester(classifier_list[cln],parameters_list[cln],nparams_list[cln],p,classifier_names[cln])
 
-            #get labels
+               #get labels
                 label_filename = name + "labels.pkl"
                 label_file = open(label_filename,"rb")
                 labels = cPickle.load(label_file)
@@ -107,36 +121,59 @@ if __name__ == "__main__":
 
                 if p == 1.0:
                     pyplot.figure(2*k)
-                    pyplot.bar(cln,max_recall,label="p = 1.0",width=0.2, color="blue")
[…]

### 2014-05-13 ClassifierTester.py
Added more labeling stuff.  Fixed an issue where number of negative updates was reported wrong.

@@ -41,7 +41,10 @@ class ClassifierTester:
             n_pos_right = 0
             n_precision_wrong = 0
             n_recall_wrong = 0
-            total_negative_checks = 0
+            total_negative_checks = 0    #how many negative predictions the user must verify
+            total_end_negative_checks = 0 #how many checks we do in the last 100 papers
+
+            #loop through data and run the algorithm
             for i in range(len(data)):
                 x = data[i]
                 y_hat = classifier.Predict(x)
@@ -56,9 +59,13 @@ class ClassifierTester:
                         if np.random.binomial(1,self.current_p) == 1:
                             self.current_p = 0.9*self.current_p + 0.001
                             total_negative_checks += 1
+                            if len(data) - i < 100 :
+                                total_end_negative_checks += 1
                     else:
                         if np.random.binomial(1,self.p) == 1:
                             total_negative_checks += 1
+                            if len(data) - i < 100 :
+                                total_end_negative_checks += 1
 
                 elif y_hat == 1:
                     #update on false positive, add one to n_wrong
@@ -73,17 +80,19 @@ class ClassifierTester:
                         k = np.random.binomial(1,self.current_p)
                         if k == 1:
                             total_negative_checks += 1
+                            if len(data) - i < 100 :
+                                total_end_negative_checks += 1
                             classifier.Update(x,y_hat,y)
                             self.current_p = 0.4*self.current_p + 0.6
                     else:
                         k = np.random.binomial(1,self.p)
                         if k == 1:
                             total_negative_checks += 1
+                            if len(data) - i < 100 :
+                                total_end_negative_checks += 1
                             classifier.Update(x,y_hat,y)
 
 
-
-                            
             self.neg_update_grid[self._ParamsToString(params)] = total_negative_checks
             
             if n_pos_right != 0:

### 2014-05-13 TestClassifiers.py

@@ -38,7 +38,7 @@ if __name__ == "__main__":
     rhos = [2**(-8), 2**(-7),2**(-6),2**(-5)]
     Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0]
     sigmas = [0.01, 0.02, 0.04,0.2, 1.0]
-    cs = [-0.25, -0.125, -0.0625, -0.03125, 0.0, 0.03125, 0.0625, 0.125]
+    cs = [-0.0625, -0.03125, 0.0, 0.03125, 0.0625]
     ds = [1, 2, 3, 4]
     
     #liss of classifiers and their names
@@ -54,6 +54,13 @@ if __name__ == "__main__":
     for name in names:
         classifier_p_labels[name] = range(len(classifier_names))
 
+    param_r_labels = dict()
+    for name in names:
+        param_r_labels[name] = range(len(classifier_names))
+    param_p_labels = dict()
+    for name in names:
+        param_p_labels[name] = range(len(classifier_names))
+
 
     #set up parameters and their names                                      
     parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas], [cs, ds]]
@@ -68,6 +75,7 @@ if __name__ == "__main__":
         for p in [1.0, 0.1, 'adaptive']:
             print "P value is: ", p
             #go through users
+            
             for k in range(len(names)):
                 #use k to determine plots
                 name = names[k]
@@ -118,15 +126,20 @@ if __name__ == "__main__":
                 best_r_params, max_recall, r_neg_updates = classifier_tester.ReportBestRecall()
 
                 best_p_params, max_precision, p_neg_updates = classifier_tester.ReportBestPrecision()
-
+                
+                
+                
+                
                 if p == 1.0:
                     pyplot.figure(2*k)
-                    if classifier_names[cln] == "Perceptron":
+                    if cln == 0:
                         pyplot.bar(cln,max_recall,label="p = 1.0",width=0.2, color="blue")
                     else:
                         pyplot.bar(cln,max_recall,width=0.2, color="blue")
                         
                     classifier_r_labels[name][cln] = classifier_names[cln] + "\n Neg updates: " + str(r_neg_updates)
+
+                    param_r_labels[name][cln] = "\n params: " + str(best_r_params)
 
                     pyplot.figure(2*k + 1)
                     if classifier_names[cln] == "Perceptron":
[…]

### 2014-05-13 OnlineSVM.py
Removed eta from the grid search in classifiers where it was irrelevant.

@@ -62,9 +62,11 @@ class OnlineSVMClassifier:
 
 #wrapper functions to set up classifiers for testing
 def MakeOnlineSVMClassifier(parameters):
-    """ parameters are just eta """
+    """ inputs:
+             parameters[0] - C, penalty in online SVM
+    """
     
-    classifier = OnlineSVMClassifier(parameters[0],parameters[1])
+    classifier = OnlineSVMClassifier(1.0,parameters[0])
     
     return classifier
 

### 2014-05-13 Perceptron.py

@@ -166,13 +166,12 @@ def MakeGaussianKernel(sigma):
 def MakeGaussianKernelPerceptronClassifier(parameters):
     """ wrapper to make Gaussian Kernel Perceptron from a list of 
     parameters:
-        parameters[0] = learning rate
-        parameters[1] = sigma, variance of kernel
+        parameters[0] = sigma, variance of kernel
     """
 
-    g_kernel = MakeGaussianKernel(parameters[1])
+    g_kernel = MakeGaussianKernel(parameters[0])
     
-    kclassifier = KernelPerceptronClassifier(parameters[0],g_kernel)
+    kclassifier = KernelPerceptronClassifier(1.0,g_kernel)
 
     return kclassifier
 
@@ -257,7 +256,7 @@ class MarginPerceptronClassifier():
 def MakeMarginPerceptronClassifier(parameters):
     """ parameters are learning rate and margin, rho """
 
-    margin_pclassifier = MarginPerceptronClassifier(parameters[0],parameters[1])
+    margin_pclassifier = MarginPerceptronClassifier(1.0, parameters[0])
 
     return margin_pclassifier
 

### 2014-05-13 TestClassifiers.py

@@ -63,9 +63,9 @@ if __name__ == "__main__":
 
 
     #set up parameters and their names                                      
-    parameters_list = [etas, [etas,rhos], [etas,Cs], [etas,sigmas], [cs, ds]]
-    parameter_names = [["eta"],["eta","rho"],["eta","C"],["eta","sigma"],["c","d"]]
-    nparams_list = [1, 2, 2, 2, 2]
+    parameters_list = [etas, rhos, Cs, sigmas, [cs, ds]]
+    parameter_names = [["eta"],["rho"],["C"],["sigma"],["c","d"]]
+    nparams_list = [1, 1, 1, 1, 2]
     
                       
 #go through all classifiers to test
@@ -197,17 +197,16 @@ if __name__ == "__main__":
             classifier_r_labels[names[k]][l] = classifier_r_labels[names[k]][l] + param_r_labels[names[k]][l]
         pyplot.xticks(range(len(classifier_names)),classifier_r_labels[names[k]],rotation=35,fontsize=8)
         pyplot.gcf().subplots_adjust(bottom=0.20)
-#        pyplot.gcf().tight_layout() # not working, maybe need a newer version
         pyplot.ylim([0,1])
         pyplot.legend(loc="best",prop={"size":10})
         pyplot.savefig("./" + names[k] + "Recall.pdf")
 
         pyplot.figure(2*k + 1)
         pyplot.title("Precision for " + names[k])
+        #append information about parameters to labels
         for l in range(len(classifier_names)):
             classifier_p_labels[names[k]][l] = classifier_p_labels[names[k]][l] + param_p_labels[names[k]][l]
         pyplot.xticks(range(len(classifier_names)),classifier_p_labels[names[k]], rotation = 35, fontsize=9)
-#       pyplot.gcf().tight_layout()
         pyplot.gcf().subplots_adjust(bottom=0.20)
         pyplot.ylim([0,1])
         pyplot.legend(loc="best",prop={"size":10})

### 2014-05-13 ClassifierTester.py
cleaned up bar plots a little.

@@ -170,8 +170,8 @@ class ClassifierTester:
                 print_str = ""
             print "-"*60
 
-                
-            return
+            
+        return self.recall_grid, self.precision_grid
 
 
     def ReportBestRecall(self):

### 2014-05-13 TestClassifiers.py

@@ -19,6 +19,39 @@ from ClassifierTester import ClassifierTester
 
 
 
+def AddBarToPlot(cln, max_recall, max_precision, k):
+    """' helper function to add a bar to barplot 2k and 2k+1 , 
+    inputs:
+            cln - classifier number, from test script
+            max_recall - best recall achieved by classifier
+            max_precision - best precision achieved by classifier
+            k - user name number.
+            """
+    
+    if p == 1.0:
+        offset = 0
+        plot_clr = "blue"
+    elif p == 0.1:
+        offset = 0.2
+        plot_clr = "red"
+    elif p == 'adaptive':
+        offset = 0.4
+        plot_clr = "green"
+
+    pyplot.figure(2*k)
+    if cln == 0:
+        pyplot.bar(cln + offset,max_recall,label = "p = " + str(p),width=0.2, color=plot_clr)
+    else:
+        pyplot.bar(cln + offset,max_recall,width=0.2, color=plot_clr)
+
+    pyplot.figure(2*k + 1)
+    if cln == 0:                    
+        pyplot.bar(cln + offset,max_precision,label="p = " + str(p), width=0.2, color=plot_clr)
+    else:
+        pyplot.bar(cln + offset,max_precision, width=0.2, color=plot_clr)
+
+
+
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
@@ -47,19 +80,24 @@ if __name__ == "__main__":
 
 
     #set up empty lists for labels on bar graphs
+    # add entry for "__everyone__" to aggregate
     classifier_r_labels = dict()
     for name in names:
         classifier_r_labels[name] = range(len(classifier_names))
+    classifier_r_labels["__everyone__"] = range(len(classifier_names))
     classifier_p_labels = dict()
     for name in names:
         classifier_p_labels[name] = range(len(classifier_names))
+    classifier_p_labels["__everyone__"] = range(len(classifier_names))
 
     param_r_labels = dict()
     for name in names:
         param_r_labels[name] = range(len(classifier_names))
+    param_r_labels["__everyone__"] = range(len(classifier_names))
     param_p_labels = dict()
     for name in names:
         param_p_labels[name] = range(len(classifier_names))
+    param_p_labels["__everyone__"] = range(len(classifier_names))
 
 
     #set up parameters and their names                                      
@@ -74,8 +112,8 @@ if __name__ == "__main__":
         #go through values for p
         for p in [1.0, 0.1, 'adaptive']:
             print "P value is: ", p
+
[…]

### 2014-05-13 ClassifierTester.py
Polished some of the testing scripts stuff.  Bar graphs look good now.

@@ -171,7 +171,7 @@ class ClassifierTester:
             print "-"*60
 
             
-        return self.recall_grid, self.precision_grid
+        return self.recall_grid, self.precision_grid, self.neg_update_grid
 
 
     def ReportBestRecall(self):

### 2014-05-13 TestClassifiers.py

@@ -19,7 +19,7 @@ from ClassifierTester import ClassifierTester
 
 
 
-def AddBarToPlot(cln, max_recall, max_precision, k):
+def AddBarToPlot(cln, max_recall, max_precision, r_neg_updates, p_neg_updates, k):
     """' helper function to add a bar to barplot 2k and 2k+1 , 
     inputs:
             cln - classifier number, from test script
@@ -39,17 +39,60 @@ def AddBarToPlot(cln, max_recall, max_precision, k):
         plot_clr = "green"
 
     pyplot.figure(2*k)
+    pyplot.subplot(211)
     if cln == 0:
         pyplot.bar(cln + offset,max_recall,label = "p = " + str(p),width=0.2, color=plot_clr)
     else:
         pyplot.bar(cln + offset,max_recall,width=0.2, color=plot_clr)
 
+    pyplot.subplot(212)
+    if cln == 0:
+        pyplot.bar(cln + offset,r_neg_updates,label = "p = " + str(p),width=0.2, color=plot_clr)
+    else:
+        pyplot.bar(cln + offset,r_neg_updates,width=0.2, color=plot_clr)
+
     pyplot.figure(2*k + 1)
+    pyplot.subplot(211)
     if cln == 0:                    
         pyplot.bar(cln + offset,max_precision,label="p = " + str(p), width=0.2, color=plot_clr)
     else:
         pyplot.bar(cln + offset,max_precision, width=0.2, color=plot_clr)
 
+    pyplot.subplot(212)
+    if cln == 0:
+        pyplot.bar(cln + offset,p_neg_updates,label = "p = " + str(p),width=0.2, color=plot_clr)
+    else:
+        pyplot.bar(cln + offset,p_neg_updates,width=0.2, color=plot_clr)
+
+    return
+
+
+def BestParams(grid, neg_updates):
+    """ find the best values of parameters from the recall on a grid of parameters.  Also report the number of
+    negative updates needed for those values of parameters
+    inputs:  
+            grid - dict of either recall or precision from a single classifier, 1 entry for each set of parameters tested
+            neg_updates - dict of negative updates required for each set of parameters.  The keys here match the keys of grid
+           
+    outputs:
+           best_param        - set of parameters that gave the maximum value in grid
+           best_value        - maximum value found in grid (recall or precision)
+           best_neg_udpdates - number of negative updates needed by 
+                               classifier using best_param for parameters
+"""
+    
+    best_value = 0.
+    best_param = None
[…]

### 2014-05-13 OnlineSVM.py
Fixed online SVM parameters

@@ -66,7 +66,7 @@ def MakeOnlineSVMClassifier(parameters):
              parameters[0] - C, penalty in online SVM
     """
     
-    classifier = OnlineSVMClassifier(1.0,parameters[0])
+    classifier = OnlineSVMClassifier(parameters[0],1.0)
     
     return classifier
 

### 2014-05-13 TestClassifiers.py

@@ -210,6 +210,9 @@ if __name__ == "__main__":
                     total_recall_grid = recall_grid
                     total_precision_grid = precision_grid
                     total_neg_update_grid = neg_updates
+                    total_product_grid = dict()
+                    for param in recall_grid:
+                        total_product_grid = 
                 else:
                     #add values to grids for aggregating
                     for param in recall_grid:

### 2014-05-13 Paper.tex
updating Paper.tex

@@
 
-\section{Some Theory: Bounding Updates}
+\section{Theory: Algorithm and Bounding Updates}
 
 The main engine behind the tool is a modified Perceptron algorithm which employs an accept-reject method among the papers it labels uninteresting.
-The following pseudocode details the algorithm, where $x_t$ denotes feature data, $y_t$ denotes labels, $\widehat{y}_t$ are predictions, $w_t$ are hypotheses, and $k_t$ are i.i.d.
+The following pseudocode details the algorithm, where $x_t$ denotes feature vectors, $y_t$ denotes labels, $\widehat{y}_t$ are predictions, $w_t$ are hypotheses, and $k_t$ are i.i.d.
 random variables used for the accept-reject method.
-$k_t = 1$ with probability $p$ and $k_t = 0$ with probability $1-p$.\\
+$k_t = 1$ with probability $p$ and $k_t = 0$ with probability $1-p$.
+As mentioned, if the algorithm only made updates when $\widehat{y}=1$ (i.e.
+interesting) then this would leave the number of mistakes made when $\widehat{y} = -1$ unchecked (hence, several lost interesting articles).
+As a compromise, we generate the i.i.d.
+variables $k_t$ for each observation when $\widehat{y} = -1$.
+Note that if $\widehat{y} = -1$ and $k=1$, the algorithm will ask for the correct label and make an update.
+Otherwise if $\widehat{y} = -1$ and $k=0$, the algorithm does not ask for the correct label and makes no update.\\
 
@@
 
-As mentioned, if the algorithm only made updates when $\widehat{y}=1$ (i.e.
-interesting) then this would leave the number of mistakes made when $\widehat{y} = -1$ unchecked (and, hence, several lost interesting articles).
-As a compromise, we generate the i.i.d.
-variables $k_i$ for each observation when $\widehat{y} = 0$.
-Note that if $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=0$, the algorithm does not ask for the correct label, and makes no update.
+We learned in the course how it can be shown that the number of updates occuring in the original Perceptron algorithm can be bounded in terms of the separating margin $\rho$ and the size $r$ of the ball containing the feature data.
+We wanted to find a similar bound in our case where the number of updates is limited by how often we ask for the correct label when $\widehat y = 0$.
+Naturally we should aim for a probabilistic bound as opposed to a concrete bound since we incorporate the extra random variables $k_t$.
 
 Let $I_1$ be the set of $t$ where a mistake was made and
-$\hat{y}=1$ (false positives).  Let $I_2$ be the set where a mistake was made and
-$\hat{y} = -1, k = 1$ (false negatives where the algorithm updates), and let $I_3$ be the set where a mistake was
-made, $\hat{y} = -1$ and $k = 0$ (false negatives where the algorithm does \bold{not} make an update). Finally, let $M_i = |I_i|$ for $i =
-1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
-$M$ in the usual perceptron case.  We assume that there exits a $\rho$
-and $R$ satisfying the assumptions of Theorem 7.8 from our text, and a separating hyperplane determined by the vector $v$. Let $M' = M_1 + M_2$, then
+$\widehat{y}=1$ (false positives).  Let $I_2$ be the set where a mistake was made with
+$\widehat{y} = -1$ and $k = 1$ (false negatives where the algorithm updates), and $I_3$ the set where a mistake was
+made with $\widehat{y} = -1$ and $k = 0$ (false negatives where the algorithm does {\it not} make an update). Finally, let $M_i = |I_i|$ for $i =
+1,2,3$.
+We bound $M_1 + M_2$ in the same way we bound $M$ in the original Perceptron algorithm.
+Assume there exists a $\rho$ and $R$ satisfying the assumptions of Theorem 7.8 from our text, and a separating hyperplane determined by the vector $v$.
+Let $M' = M_1 + M_2$, then
 \begin{align*}
-M' \rho =&\ \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2} y_t\V{x}_t \
- \leq   \left\|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t\right\| \\
-=& \ \left\|\sum_{t \in I_1 \cup I_2} (\V{w}_{t+1} - \V{w}_t) \right\| 
-= \ \|\V{w}_{T+1} \| \\
-=&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 - \|\V{w}_t\|^2 }\\
-= &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
-  \|\V{w}_t\|^2 }\\
-= &\ \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
-  \|\V{x}_t\|^2} \\
-\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
-\sqrt{M'r^2} \end{align*}
-This implies that $M' \leq \frac{r^2}{\rho^2}$.
-We then have that $M = M' + M_3$, so we would like a bound on $M_3$, the number of mistakes made that the algorithm does not update on.
-Here we revert to a weaker bound, considering the expectation of
+M' \rho =&\ \frac{v}{\|v\|}\sum_{I_1 \cup I_2} y_tx_t \
+ \leq   \Bigl\|\sum_{t \in I_1 \cup I_2} y_t x_t\Bigr\| \\
+=& \ \Bigl\|\sum_{t \in I_1 \cup I_2} (w_{t+1} - w_t) \Bigr\| 
+= \ \|w_{T+1} \| \\
+=&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  w_{t+1}\|^2 - \|w_t\|^2 }\\
+= &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  w_{t} + y_t x_t\|^2 - \|w_t\|^2 }\\
+= &\ \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t w_t\cdot x_t - \|x_t\|^2} \\
+\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|x_t\|^2}
+\leq \sqrt{M'r^2}.
+\end{align*}
+This implies that $M' \leq \frac{r^2}{\rho^2}$. Since $M = M' + M_3$, a bound on $M_3$ is needed. We revert to a weaker bound and consider the expectation of
 $M_3$. Since 
-\[M_3 = \sum_{i=1}^m 1_{\left\{\hat{y}_i = 0 \cap y_i = 1\right\}}1_{k_i = 0}, \]
+\[M_3 = \sum_{t=1}^T 1_{\left\{\widehat{y}_t = -1 \cap y_t = 1\right\}}1_{k_t = 0}, \]
 we get that
 \begin{align*}
-\E[M_3] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 0}] \\
- = &\ (1 - p)\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}],
+\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] \\
+ = &\ (1 - p)\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
 \end{align*}
-where the last equality used the fact that $k_i$ is independent of the data.  Now we want to control the sum of expectations in this expression, and to do this we consider the expectation of $M_2$.
+where the last equality uses the independence of $k_t$ from the data. To control the sum of expectations in this expression we consider the expectation of $M_2$. Since
+\[
+M_2 =  \sum_{t=1}^T 1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}1_{k_t = 1},
+\]
+then
 \begin{align*}
-M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}1_{k_i = 1} \\
-\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
-= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = -1 \cap y_i = 1\right\}}]\\
-\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
+\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \\
+=&\ p\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
 \end{align*}
-We may then apply the crude bound $\E[M_3] \leq  \frac{1-p}{p}
-M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
+Thus
+\[
+E[M_3] = \ \frac{1-p}{p}\ \E[M_2].
+\]
+We can apply the crude bound $\E[M_3] \leq \frac{1-p}{p}\ \E[M']$, since $M_2 \leq M'$. Thus the expected number of mistakes can be bounded by
 \begin{align*}
@@
 \leq & \ \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
-\leq  & \ \frac{1}{p}\frac{r^2}{\rho^2} \\
+\leq  & \ \frac{1}{p}\frac{r^2}{\rho^2}
 \end{align*}
@@
 
+\section{Implementation}
+
+The tool is made from components in multiple Python files, split up according to their function in the program.
+The metadata for each article is obtained using arXiv's Open Archives Initiative protocol which returns an XML file with a list of up to 1000 articles as nodes containing a variety of metadata, including abstracts, authors, submission dates, and fields and subfields, making the data quite accessible and fairly simple to sort.
+The file {\tt ArxivData.py} contains the functions and class definitions used to collect, organize and process data.
+Included are a class of objects representing papers and a class definition for feature vectors.
+%
+%DESCRIBE BAG OF WORDS APPROACH FOR FEATURE VECTORS SOMEWHERE
+%
+The primary function is {\tt GetPapersOAI()} and its wrapper which prompts the user for a particular subject, any of arXiv's listed subfields for that subject, and a range of dates from which to select the papers.
+Then it draws the XML file of data from arXiv's database, filters the articles using the XML entries according to the subfields, and prepares the stream of abstracts to present the user.
+The user is then asked to label each article as interesting or not, one at a time, with updates made according to the algorithm employed.
+
+%To use the program, run both scripts {\tt getTestData.py} to collect the papers to rate and then {\tt LabelData.py}
+
+The files {\tt Perceptron.py} and {\tt OnlineSVM.py} house the classes that compose the different classifying algorithms we use.
+The classes contain the methods that run the algorithm and the attributes such as weights and parameters that the algorithm uses and updates.
+Within {\tt Perceptron.py} is the modified Perceptron algorithm we presented earlier, a Margin Perceptron classifier, and a Kernel Perceptron classifier supplied with both a polynomial and Gaussian kernel.
+Similarly, the Online SVM algorithm is implemented in the file {\tt OnlineSVM.py}.
+Each algorithm takes a learning rate $\eta$ as a parameter.
+The modified Perceptron requires no extra parameters, while the Gaussian Kernel Perceptron classifier requires a $\sigma$ specifying the variance in the kernel.
+The Polynomial Kernel Perceptron takes two parameters $c$ and $d$ which are the constants used in constructing the polynomial kernel.
+The Margin Perceptron requires a parameter $\rho$ designating the separating margin of the feature vectors, and the Online SVM algorithm takes a parameter $C$ for the penalty applied to the update (i.e.
+$w_{t+1} = w_t -\eta(w_t- Cy_tx_t)$).
+Each algorithm class has an associated wrapper that instantiates a class, and we use each of these algorithms when testing the tool.
+
+There are some additional Python files included that we used primarily for testing.
+For instance, {\tt getTestData.py} and {\tt LabelData.py} are scripts that call the functions that collect arXiv data and present the abstracts to acquire labels, respectively, which we place in a single script for the user.
+Additionally {\tt ClassifierTester.py} defines a class for the classification algorithms we include allowing them to be used in a uniform manner despite taking different parameters.
+This enables us to run tests over each algorithm, with multiple data sets from a few different users, using a set of several values for each parameter in a fairly organized manner in the script {\tt TestClassifiers.py}.
+Plots are also constructed in that script as well.
+
+One of the most important aspects of this tool is the feature data itself, and what characteristics distinguish
+
 \end{document}
-
-%GIVE THE ALGORITHM THEN PRESENT THE BOUND
 

### 2014-05-13 ProjectNotes.tex
changed testdata stuff, set up testing, started fixing proof in ProjectNotes.tex
fixed ProjectNotes.tex
updating Paper.tex

@@
 We would like to modify the perceptron algorithm to only make updates when $\hat{y} = 1$ in order for the user to not have to see every article, but this will leave the number of mistakes made with $\hat{y} = 0$ unbounded.
-as a compromise, let us generate iid variables $k_i$ for each observation which are equal to 1 with probability $p$ and equal to $0$ with probability $1-p$.
-If $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=1$, the algorithm does not ask for the correct label, and makes no update.
-It seems that in this way, we should still be able to bound the number of mistakes, perhaps in expectation or probabilistically.\\
+As a compromise, let us generate iid variables $k_i$ for each observation which are equal to 1 with probability $p$ and equal to $0$ with probability $1-p$.
+If $\hat{y} = 0$ and $k=1$, the algorithm will ask for the correct label and make an update, otherwise if $\hat{y} = 0$ and $k=0$, the algorithm does not ask for the correct label, and makes no update.
+It seems that in this way, we should still be able to bound the number of mistake, perhaps in expectation or probabilistically.\\
 
-Let us let $I_1$ be the set of $t$ where a mistake was made and,
+Let $I_1$ be the set of $t$ where a mistake was made and
 $\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
@@
  \leq & \  \|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t \|\\
-= & \ \|\sum_{t \in I_1 \cup I_2} \V{w}_{t+1} - \V{w}_t) \| \\
+= & \ \|\sum_{t \in I_1 \cup I_2} (\V{w}_{t+1} - \V{w}_t) \| \\
 = & \ \|\V{w}_{T+1} \| \\
@@
 \begin{align*}
-M_3 = & \sum_{I_2} 1_{k = 0} \\
-\E[M_3] = & \sum_{I_2} \E[1_{k = 0}] = (1 - p) (M_3 + M_2) \\
-M_2 = & \sum_{I_2} 1_{k = 1} \\
-\E[M_2] = & p (M_3 + M_2) \\
+M_3 =& \sum_{i=1}^m 1_{\left\{\hat{y}_i = 0 \cap y_i = 1\right\}}1_{k_i = 0} \\
+\E[M_3] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 0}] \\
+ = & (1 - p)\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\\
+\end{align*}
+Where the last equality used the fact that $k_i$ is independent of the data.  Now we want to control the sum of expectations in this expression, and to do this we consider the expectation of $M_2$.
+\begin{align*}
+M_2 = & \sum_{i=1}^m 1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}1_{k_i = 1} \\
+\E[M_2] = & \sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\E[1_{k = 1}] \\
+= & p\sum_{i=1}^m \E[1_{\left\{\hat{y_i} = 0 \cap y_i = 1\right\}}]\\
 \Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
@@
 \leq &  \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
-\leq = \frac{1}{p}\frac{r^2}{\rho^2} \\
+\leq  & \frac{1}{p}\frac{r^2}{\rho^2} \\
 \end{align*}

### 2014-05-13 ClassifierTester.py
Added Weighted Majority Algorithm.

@@ -67,7 +67,7 @@ class ClassifierTester:
                             if len(data) - i < 100 :
                                 total_end_negative_checks += 1
 
-                elif y_hat == 1:
+                elif y_hat == 1 and y == -1:
                     #update on false positive, add one to n_wrong
                     n_precision_wrong += 1
                     classifier.Update(x,y_hat,y)

### 2014-05-13 TestClassifiers.py

@@ -15,6 +15,8 @@ from Perceptron import MakeMarginPerceptronClassifier
 from Perceptron import MakeGaussianKernelPerceptronClassifier
 from Perceptron import MakePolynomialKernelPerceptronClassifier
 from Perceptron import KernelPerceptronClassifier
+from WeightedMajority import WeightedMajorityClassifier
+from WeightedMajority import MakeWeightedMajorityClassifier
 from ClassifierTester import ClassifierTester
 
 
@@ -98,7 +100,7 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","sid","iantobasco","joey","manas","travis"]
+    names = ["steven","joey"]#,"sid","iantobasco","manas","travis"]
     custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
     custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
     
@@ -118,9 +120,8 @@ if __name__ == "__main__":
     ds = [1, 2, 3, 4]
     
     #liss of classifiers and their names
-    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier]
-    classifier_names = ["Perceptron","Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron"]
-
+    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier, MakeWeightedMajorityClassifier]
+    classifier_names = ["Perceptron","Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron", "Weighted Majority Classifier"]
 
     #set up empty lists for labels on bar graphs
     # add entry for "__everyone__" to aggregate
@@ -144,10 +145,9 @@ if __name__ == "__main__":
 
 
     #set up parameters and their names                                      
-    parameters_list = [etas, rhos, Cs, sigmas, [cs, ds]]
[…]

### 2014-05-13 WeightedMajority.py
Actually added weighted majority algorithm now.

@@ -1,0 +1,99 @@
+""" Implement a simple weighted majority algorithm to combine multiple online learning algorithms and hopefully get a performance boost.
+
+
+
+"""
+
+from Perceptron import PerceptronClassifier
+from Perceptron import KernelPerceptronClassifier
+from Perceptron import MarginPerceptronClassifier
+from Perceptron import MakeGaussianKernelPerceptronClassifier
+from Perceptron import MakePolynomialKernelPerceptronClassifier
+from OnlineSVM import OnlineSVMClassifier
+
+
+def sign(x):
+    """ compute sign of x, with convention that 0 is positive """
+    if x >= 0:
+        return 1
+    else:
+        return -1
+
+
+class WeightedMajorityClassifier:
+    
+    def __init__(self, classifier_list):
+        
+        self.name = "Weighted Majority Classifier"
+        self.classifier_list = classifier_list
+        self.weights = [1. for k in classifier_list]
+        
+
+        #TODO: Tune Beta
+        self.beta = 0.9
+        
+    def Predict(self,x):
+        """ Predict by doing a weighted vote """
+        
+        value = 0.
+        for k in range(len(self.classifier_list)):
+            value += self.weights[k]*self.classifier_list[k].Predict(x)
+        
+        return sign(value)
+
+    def Update(self,x,y_hat,y):
+        """ given that the weighted majority has guessed y_hat for data x, 
+        update it using the correct value y.
+
+        Note: This assumes y != y_hat
+
+        Note: must be used after prediction to obtain a correct accuracy estimate, 
+        Note: We may only update on some of the predictions where y_hat = -1 (undesireable paper).
+        """
+
+        #update weights for weighted majority
+        #update each classifier in classifier list if it's incorrect.
+        for k in range(len(self.classifier_list)):
+            if self.classifier_list[k].Predict(x) != y:
+                self.weights[k] = self.beta*self.weights[k]
+                self.classifier_list[k].Update(x,y_hat,y)
+            else:
+                #this subclassifier is correct:
+                self.weights[k] = self.weights[k]/self.beta
+            
+        return
+
+
+    
+    def __repr__(self):
+        
+        repstring = "Weighted Majority Classifier using list of classifiers: " 
+        for cl in self.classifier_list:
+            repstring += str(cl)
[…]

### 2014-05-13 ClassifierTester.py
Added threshold for accuracy report.

@@ -43,6 +43,7 @@ class ClassifierTester:
             n_recall_wrong = 0
             total_negative_checks = 0    #how many negative predictions the user must verify
             total_end_negative_checks = 0 #how many checks we do in the last 100 papers
+            threshold = 35 #hard code threshold = 35 for now
 
             #loop through data and run the algorithm
             for i in range(len(data)):
@@ -50,7 +51,8 @@ class ClassifierTester:
                 y_hat = classifier.Predict(x)
                 y = labels[i]
                 if y == 1 and y_hat == 1:
-                    n_pos_right += 1
+                    if i > threshold:
+                        n_pos_right += 1
                 elif y == -1 and y_hat == -1:
                     #update total_negative_checks count if we had to check, 
                     # and for adaptive p, update value of current_p
@@ -69,11 +71,13 @@ class ClassifierTester:
 
                 elif y_hat == 1 and y == -1:
                     #update on false positive, add one to n_wrong
-                    n_precision_wrong += 1
+                    if i > threshold:
+                        n_precision_wrong += 1
                     classifier.Update(x,y_hat,y)
                 else:
                     #maybe update on false negative, depends on p.
-                    n_recall_wrong += 1
+                    if i > threshold:
+                        n_recall_wrong += 1
                     if self.p == 'adaptive':
                         # got it wrong, move current_p toward 1.0
                         # to check more frequently

### 2014-05-13 TestClassifiers.py

@@ -100,7 +100,7 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","joey"]#,"sid","iantobasco","manas","travis"]
+    names = ["steven","joey","sid","iantobasco","manas","travis"]
     custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
     custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
     

### 2014-05-13 ClassifierTester.py
Added VotedPerceptronClassifier.

@@ -43,7 +43,7 @@ class ClassifierTester:
             n_recall_wrong = 0
             total_negative_checks = 0    #how many negative predictions the user must verify
             total_end_negative_checks = 0 #how many checks we do in the last 100 papers
-            threshold = 35 #hard code threshold = 35 for now
+            threshold = 50 #hard code threshold = 50 for now
 
             #loop through data and run the algorithm
             for i in range(len(data)):

### 2014-05-13 Perceptron.py

@@ -71,8 +71,6 @@ class PerceptronClassifier:
         print "10 Most Negative words:"
         for k in range(10):
             print sort_wandw[-k][1], sort_wandw[-k][0]
-            
-            
 
 
 #wrapper functions to set up classifiers for testing
@@ -80,6 +78,77 @@ def MakePerceptronClassifier(parameters):
     """ parameters are just eta """
     
     classifier = PerceptronClassifier(parameters[0])
+    
+    return classifier
+
+
+class VotedPerceptronClassifier:
+    """ Same as simple perceptron algorithm, but uses average of hypotheses
+        from all rounds """
+    
+    def __init__(self,eta):
+        """ Constructor for Perceptron. 
+
+           Arguments:
+                   eta - learning rate
+        """
+        self.eta = eta
+        self.weights = dict()
+        self.voted_weights = dict()
+        self.T = 1
+        self.name = "Voted Perceptron Classifier"
+        
+    def Update(self,x,y_hat,y):
+        """ given that the Perceptron has guessed y_hat for data x, update it 
+        using the correct value y.
+
+        Note: must be used after prediction to obtain a correct accuracy estimate, 
+        We will only update on some of the predictions where y_hat = -1 (undesireable paper).
+        """
+        if y_hat != y:
+            #update
+            x.UpdateWeights(self.weights,y,self.eta)
+            self.T = self.T + 1
+            for word in self.weights:
+                if word in self.voted_weights:
+                    self.voted_weights[word] = self.voted_weights[word]*(self.T - 1)/self.T + self.weights[word]/self.T
+                else:
+                    self.voted_weights[word] = self.weights[word]/self.T
+        return
+        
+    def Predict(self,x):
+        """ predict y by using sign of a dot product of x with weights """
+        
+        return sign(x.Dot(self.voted_weights))
+
+    def __repr__(self):
+        
+        repstring = 'Perceptron Classifier, eta = %1.3f' % self.eta
+        
+        return repstring
+    
+    __str__ = __repr__
+
+    def ReportHighestWeights(self):
+        #HACK: report the words with the largest absolute weights
+        
+        words_and_weights = [(self.weights[word],word) for word in self.weights]
+            
+        sort_wandw = sorted(words_and_weights, reverse=True)
+        print "10 Most Positive words:"
+        for k in range(10):
+            print sort_wandw[k][1], sort_wandw[k][0]
+        print "10 Most Negative words:"
[…]

### 2014-05-13 TestClassifiers.py

@@ -10,6 +10,7 @@ from OnlineSVM import OnlineSVMClassifier
 from OnlineSVM import MakeOnlineSVMClassifier
 from Perceptron import PerceptronClassifier
 from Perceptron import MakePerceptronClassifier
+from Perceptron import MakeVotedPerceptronClassifier
 from Perceptron import MarginPerceptronClassifier
 from Perceptron import MakeMarginPerceptronClassifier
 from Perceptron import MakeGaussianKernelPerceptronClassifier
@@ -100,7 +101,7 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","joey","sid","iantobasco","manas","travis"]
+    names = ["steven","joey","sid","iantobasco","manas"]#,"travis"]
     custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
     custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
     
@@ -120,8 +121,8 @@ if __name__ == "__main__":
     ds = [1, 2, 3, 4]
     
     #liss of classifiers and their names
-    classifier_list = [MakePerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier, MakeWeightedMajorityClassifier]
-    classifier_names = ["Perceptron","Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron", "Weighted Majority Classifier"]
+    classifier_list = [MakePerceptronClassifier, MakeVotedPerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier, MakeWeightedMajorityClassifier]
+    classifier_names = ["Perceptron","Voted Perceptron", "Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron", "Weighted Majority Classifier"]
 
     #set up empty lists for labels on bar graphs
[…]

### 2014-05-13 WeightedMajority.py

@@ -30,7 +30,7 @@ class WeightedMajorityClassifier:
         
 
         #TODO: Tune Beta
-        self.beta = 0.9
+        self.beta = 1.0
         
     def Predict(self,x):
         """ Predict by doing a weighted vote """

### 2014-05-13 Perceptron.py
Added VotedPerceptronClassifier.

@@ -34,9 +34,13 @@ class PerceptronClassifier:
         We will only update on some of the predictions where y_hat = -1 (undesireable paper).
         """
         if y_hat != y:
+            if y_hat == 1:
+                eta = self.eta*self.p
+            else:
+                eta = self.eta
             #update
             self.n_wrong += 1
-            x.UpdateWeights(self.weights,y,self.eta)
+            x.UpdateWeights(self.weights,y,eta)
         else:
             self.n_correct += 1
         
@@ -107,7 +111,11 @@ class VotedPerceptronClassifier:
         """
         if y_hat != y:
             #update
-            x.UpdateWeights(self.weights,y,self.eta)
+            if y_hat == 1:
+                eta = self.eta*self.p
+            else:
+                eta = self.eta
+            x.UpdateWeights(self.weights,y,eta)
             self.T = self.T + 1
             for word in self.weights:
                 if word in self.voted_weights:

### 2014-05-13 TestClassifiers.py

@@ -101,7 +101,7 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","joey","sid","iantobasco","manas"]#,"travis"]
+    names = ["steven","joey","sid","manas"]#,"iantobasco","travis"]
     custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
     custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
     

### 2014-05-13 Paper.tex
more paper updates

@@
 \begin{document}
-\title{Online Learning Your arXiv Preferences}
+\title{Online Classification of arXiv Papers Based on Your Preferences}
 \author{Steve Delong and Joey McDonald}
@@
 
-One of the most important aspects of this tool is the feature data itself, and what characteristics distinguish
+An important feature of any text classification device is the data used to construct feature vectors.
+There are several approaches to text classification, itself a large field of research.
+We take an elementary approach and use a bag-of-words model, that is, performing a word count for each distinct word in the abstract and converting that into a vector.
+Each distinct word corresponds to a different coordinate in the feature space. This ``vectorization" is defined in {\tt ArxivData.py} and called when
+
+%One of the most important aspects of this tool is what is used for feature data. There are several approaches to text categorization that
 

### 2014-05-14 Paper.tex
added results to paper.

@@
 \usepackage{amsmath,amsthm,amssymb}
+\usepackage{graphicx}
 \pagestyle{myheadings}
@@
 
-One of the important aspects of the algorithm is that it present some articles predicted to be uninteresting.
-Otherwise there is risk in mislabeling and potentially discarding many articles that are interesting to the user.
+One of the important aspects of the algorithm is that it present some articles to the user that it predicted to be uninteresting.
+Otherwise there is risk of mislabeling and potentially discarding many articles that are interesting to the user.
 Nevertheless the goal is to have an active filter on the articles lest the whole purpose of the program be defeated.
@@
 original perceptron bound by a factor of $\frac{1}{p}$, it is also only a
-bound in expectation.
+bound in expectation.\\
 
@@
 %One of the most important aspects of this tool is what is used for feature data. There are several approaches to text categorization that 
+\section{Results}
+
+We tested different online learning algorithms with sample data generated by graduate students at NYU.
+Several students were asked to use a python script to gather the abstracts from Arxiv in categories that they specified (see SECTION REFERENCE HERE).
+Then the students were asked to generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
+\\
+This data was used to test the following online learning algorithms: Perceptron, Margin Perceptron, Online SVM, Gaussian Kernel Perceptron, and Polynomial Kernel Perceptron.
+For each algorithm with tunable parameters, a grid search was performed to determine the best value of each parameter.
+For each combination of parameters, each classifier was separately trained on the data from each student, and the resulting performance was averaged over students.
+Parameters chosen with a grid search are given in table \ref{table:Parametertable}.
+\\
+
+\begin{table}[h]
+\centering
+\begin{tabular}{l | r}
+Algorithm & Parameters Tuned \\
+\hline
+Margin Perceptron &  Margin, $\rho$  \\
+Online SVM & Penalty, $C$ \\
+Gaussian Kernel Perceptron &  variance, $\sigma$, \\
+Polynomial Kernel Perceptron &  intercept, $c$, and degree, $d$ \\
+\hline
+\end{tabular}
+\label{table:Parametertable}
+\caption{Parameters tuned for each classifier used.}
+\end{table}
+
+For this particular classification problem, it turned out that overall accuracy was a poor indicator of performance.
+Students tended to only label a small subset of papers as ``interesting'', so an algorithm which always predicted a label of $\hat{y} = -1$ (the paper was not interesting to the user) could achieve very high values of accuracy.
+Instead, we looked at Recall and Precision.
+Recall, $R$, is the percentage of papers labeled $y=1$ by the user that were successfully categorized by the algorithm, $\hat{y} = 1$.
+Precision, $P$, is the percentage of papers labeled $\hat{y} = 1$ by the algorithm that were actually interesting to the user, $y = 1$.
+The mathematical definitions are as follows
+\begin{align*}
+R(h) = & \frac{\sum_{i=1}^m 1_{\left{h(x_i) = 1 \cap y_i =1\right}}{\sum_{i=1}^m 1_{\left{y_i = 1\right}} \\
+P(h) = & \frac{\sum_{i=1}^m 1_{\left{h(x_i) = 1 \cap y_i =1\right}}}{{\sum_{i=1}^m 1_{\left{h(x_i) = 1\right}}. \\
+\end{align*}
+For each classifier and combination of parameters, the algorithm was shown 50 papers to obtain reasonable weights, and then as it continued to run, the number of correct positive labels, incorrect positive labels, and incorrect negative labels were recorded and used to calculate $R$ and $P$.
+These values were then averaged over all students separately.
+The best average $R$ (over all parameters tested) and the best average $P$ are shown in figure \ref{fig:PrecisionandRecall}, along with the number of negative labels asked of the user.
+We can see that the scheme with adaptive $p$ is able to achieve performance close to the the original algorithms but requiring less than half as many negative updates.
+
+\begin{figure}
+\includegraphics[width=0.7\textwidth]{EveryoneRecallPaper.pdf}
+\includegraphics[width=0.7\textwidth]{EveryonePrecisionPaper.pdf}
+\label{fig:PrecisionandRecall}
+\caption{Performance of tested online classification algorithms using different values of $p$.
+The adaptive $p$ algorithm performs relatively well compared to the original algorithm ($p = 1$), and requires less than half as many negative updates.
+Majority vote classifier combines all others in this figure.}
+\end{figure}
 

### 2014-05-14 ClassifierTester.py

@@ -22,6 +22,7 @@ class ClassifierTester:
         self.recall_grid = dict()
         self.precision_grid = dict()
         self.neg_update_grid = dict()
+        self.last_neg_update_grid = dict()
 
         
     def Test(self,data,labels):
@@ -43,7 +44,7 @@ class ClassifierTester:
             n_recall_wrong = 0
             total_negative_checks = 0    #how many negative predictions the user must verify
             total_end_negative_checks = 0 #how many checks we do in the last 100 papers
-            threshold = 50 #hard code threshold = 50 for now
+            threshold = 150 #hard code threshold = 150 for now
 
             #loop through data and run the algorithm
             for i in range(len(data)):
@@ -58,15 +59,16 @@ class ClassifierTester:
                     # and for adaptive p, update value of current_p
                     if self.p == 'adaptive':
                         #got it correct, reduce p towards 0.01, our minimum
+#                        print "current p is", self.current_p
                         if np.random.binomial(1,self.current_p) == 1:
                             self.current_p = 0.9*self.current_p + 0.001
                             total_negative_checks += 1
-                            if len(data) - i < 100 :
+                            if i  > threshold :
                                 total_end_negative_checks += 1
                     else:
                         if np.random.binomial(1,self.p) == 1:
                             total_negative_checks += 1
-                            if len(data) - i < 100 :
+                            if i  > threshold :
                                 total_end_negative_checks += 1
 
                 elif y_hat == 1 and y == -1:
@@ -81,23 +83,25 @@ class ClassifierTester:
                     if self.p == 'adaptive':
                         # got it wrong, move current_p toward 1.0
                         # to check more frequently
+#                        print "current p is", self.current_p
                         k = np.random.binomial(1,self.current_p)
                         if k == 1:
                             total_negative_checks += 1
-                            if len(data) - i < 100 :
+                            if i  > threshold :
                                 total_end_negative_checks += 1
                             classifier.Update(x,y_hat,y)
-                            self.current_p = 0.4*self.current_p + 0.6
+                            self.current_p = 0.55*self.current_p + 0.4
                     else:
                         k = np.random.binomial(1,self.p)
                         if k == 1:
                             total_negative_checks += 1
-                            if len(data) - i < 100 :
+                            if i  > threshold :
[…]

### 2014-05-14 Perceptron.py

@@ -9,8 +9,6 @@ def sign(x):
     else:
         return -1
 
-
-
 class PerceptronClassifier:
     """ Simple perceptron algorithm for online learning. """
     
@@ -34,13 +32,9 @@ class PerceptronClassifier:
         We will only update on some of the predictions where y_hat = -1 (undesireable paper).
         """
         if y_hat != y:
-            if y_hat == 1:
-                eta = self.eta*self.p
-            else:
-                eta = self.eta
             #update
             self.n_wrong += 1
-            x.UpdateWeights(self.weights,y,eta)
+            x.UpdateWeights(self.weights,y,self.eta)
         else:
             self.n_correct += 1
         
@@ -111,11 +105,7 @@ class VotedPerceptronClassifier:
         """
         if y_hat != y:
             #update
-            if y_hat == 1:
-                eta = self.eta*self.p
-            else:
-                eta = self.eta
-            x.UpdateWeights(self.weights,y,eta)
+            x.UpdateWeights(self.weights,y,self.eta)
             self.T = self.T + 1
             for word in self.weights:
                 if word in self.voted_weights:

### 2014-05-14 TestClassifiers.py

@@ -101,7 +101,7 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","joey","sid","manas"]#,"iantobasco","travis"]
+    names = ["steven","joey"] #,"sid","manas","iantobasco","travis"]
     custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
     custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
     
@@ -122,7 +122,7 @@ if __name__ == "__main__":
     
     #liss of classifiers and their names
     classifier_list = [MakePerceptronClassifier, MakeVotedPerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier, MakeWeightedMajorityClassifier]
-    classifier_names = ["Perceptron","Voted Perceptron", "Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron", "Weighted Majority Classifier"]
+    classifier_names = ["Perceptron","Voted Perceptron", "Margin Perceptron","Online SVM","Gaussian Kernel Perceptron","Polynomial Kernel Perceptron", "Majority Vote Classifier"]
 
     #set up empty lists for labels on bar graphs
     # add entry for "__everyone__" to aggregate
@@ -155,13 +155,13 @@ if __name__ == "__main__":
 
         #go through values for p
         for p in [1.0, 0.1, 'adaptive']:
-            print "P value is: ", p
+#            print "P value is: ", p
 
             #go through users
             for k in range(len(names)):
                 #use k to determine plots
                 name = names[k]
-                print "User: ", name
+#                print "User: ", name
 
                 #create classifier tester
                 classifier_tester = ClassifierTester(classifier_list[cln],parameters_list[cln],nparams_list[cln],p,classifier_names[cln])
@@ -192,18 +192,15 @@ if __name__ == "__main__":
                     
             #shuffle custom and regular data together
                 packaged_data = [(current_data[i],current_labels[i]) for i in range(len(current_data))]
-                random.seed(1)
+                random.seed(3)
                 random.shuffle(packaged_data)
                     
[…]

### 2014-05-14 Paper.tex
added to paper.

@@
-\documentclass[12pt]{article}
+g\documentclass[12pt]{article}
 \usepackage{amsmath,amsthm,amssymb}
@@
 
+This algorithm can be also be used with other classifiers.
+The set of data on which the scheme updates on is no longer iid, but any bound on the number of mistakes that doesn't require iid data, like the bound for Perceptron algorithm, will still hold in expectation with a similar modification.
+We apply the same approach to the OnlineSVM, Margin Perceptron, and Kernel Perceptron algorithms.
+\\
+The general method outlined above corrects negative predictions slowly and at a constant rate.
+It seems natural that instead we might want to correct a lot of negative predictions when we feel the algorithm is not accurate, and be more lenient when the algorithm is doing well.
+In order to achieve this, we introduce an adaptive $p$ scheme.
+This scheme starts with some value of $p$, and each time it asks the user to label a data point that it predicted would have a negative label, it modifies $p$.
+If it was correct, then $p$ is reduced and it checks negative predictions less often.
+On the other hand, if it was incorrect it increses $p$.
+
+\noindent Adaptive $p$ Perceptron algorithm:
+\begin{quotation}
+%\noindent Modified Perceptron:\\
+\noindent $w_1=0$\\
+\noindent $p=1$\\
+{\tt for $t=1$ to $T$}:\\
+\indent receive($x_t$)\\
+\indent $\widehat{y}_t=\mbox{sign}(w_t\cdot x_t)$\\
+\indent {\tt if} $\widehat{y}_t =1$ : \\
+\indent\indent receive($y_t$)\\
+\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
+\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
+\indent\indent {\tt else $w_{t+1} = w_t$}\\
+\indent\{\tt else if ($\widehat{y}_t =-1$ {\tt and} $k_t = 1$):\\
+\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
+\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
+\indent\indent\indent $p=p + \gamma_1(1 - p)$\\
+\indent\indent {\tt else }
+\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
+\indent\indent\indent $p = p - \gamma_2(p - p_{\min})$}
+\indent {\tt else if $\widehat{y}_t = -1$ and $k_t=0$}:\\
+\indent\indent $w_{t+1} = w_t$\\
+{\tt return $w_{T+1}$}
+\end{quotation}
+Where $p_{\min}$, $\gamma_1$ and $\gamma_2$ are parameters that can be tuned by the user.
+It is easy to extend the bound above to this case.
+Let $I_i$, $M_i$, and $M'$ be defined as above.
+The bound $M'\leq r^2/\rho^2$ follows in exactly the same way.
+We then bound $M_3$ in expectation,
+\begin{align*}
+\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] \\
+ \leq &\ (1 - p_{\min})\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
+\end{align*}
+and bound $\E[M_2]$ from below
+\begin{align*}
+\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \\
+\geq &\ p\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
+\end{align*}
+Continuing as before, this gives the following bound on $\E[M]$,
+\begin{align}
+\E[M] = &\E[M'] + \E[M_3] \leq \frac{r^2}{\rho^2} + \frac{1-p_{\min}}{p_{\min}} \frac{r^2}{\rho^2}\\
+= & \frac{1}{p_{\min}}\frac{r^2}{\rho^2}\\
+\end{align*}
+Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sef:results} and see that it performs fairly well while requiring less input from the user.\\
+
 \section{Implementation}
-
 The tool is made from components in multiple Python files, split up according to their function in the program.
@@
 
+\section{Conclusion}
+
 \end{document}

### 2014-05-14 Paper.tex
some fixes to paper.tex

@@
-g\documentclass[12pt]{article}
+\documentclass[12pt]{article}
 \usepackage{amsmath,amsthm,amssymb}
@@
 If it was correct, then $p$ is reduced and it checks negative predictions less often.
-On the other hand, if it was incorrect it increses $p$.
+On the other hand, if it was incorrect it increases $p$.
+\\
 
@@
 \end{align*}
-Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sef:results} and see that it performs fairly well while requiring less input from the user.\\
+Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sec:results} and see that it performs fairly well while requiring less input from the user.\\
 
@@
 \section{Results}
+\label{sec:results}
 

### 2014-05-14 Paper.tex
commit little changes before bed.

@@
 \newcommand{\E}[0]{\mathbb{E}}
-
 \begin{document}
@@
 This algorithm can be also be used with other classifiers.
-The set of data on which the scheme updates on is no longer iid, but any bound on the number of mistakes that doesn't require iid data, like the bound for Perceptron algorithm, will still hold in expectation with a similar modification.
-We apply the same approach to the OnlineSVM, Margin Perceptron, and Kernel Perceptron algorithms.
+The set of data on which the scheme updates on is no longer iid, but any bound on the number of mistakes that does not require iid data, like the bound for Perceptron algorithm, could still hold in expectation with a similar modification.
+We implement this approach with the Online SVM, Margin Perceptron, and Kernel Perceptron algorithms.
 \\
@@
 On the other hand, if it was incorrect it increases $p$.
-\\
+Psuedocode is given below \\
 
@@
 \end{quotation}
-Where $p_{\min}$, $\gamma_1$ and $\gamma_2$ are parameters that can be tuned by the user.
-It is easy to extend the bound above to this case.
+Where $p_{\min}$, $\gamma_1$ and $\gamma_2$ are parameters that can be tuned.
+It is easy to extend the bound above from the modified Perceptron to the adaptive $p$ case.
 Let $I_i$, $M_i$, and $M'$ be defined as above.

### 2014-05-14 TestClassifiers.py

@@ -101,9 +101,9 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","joey"] #,"sid","manas","iantobasco","travis"]
-    custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', }
-    custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl'}
+    names = ["steven","joey", "aj"] #,"sid","manas","iantobasco","travis"]
+    custom_data_dict = {'steven' : 'stevenCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', 'aj' : 'ajCustomTestData.pkl'}
+    custom_label_dict = {'steven' : 'stevencustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl', 'aj' : 'ajcustomlabels.pkl'}
     
 #get data
     data_filename = "./OfficialTestData.pkl"
@@ -161,15 +161,16 @@ if __name__ == "__main__":
             for k in range(len(names)):
                 #use k to determine plots
                 name = names[k]
-#                print "User: ", name
+                print "User: ", name
 
                 #create classifier tester
                 classifier_tester = ClassifierTester(classifier_list[cln],parameters_list[cln],nparams_list[cln],p,classifier_names[cln])
 
                #get labels
                 label_filename = name + "labels.pkl"
-                label_file = open(label_filename,"rb")
-                labels = cPickle.load(label_file)
+                if name != 'aj':
+                    label_file = open(label_filename,"rb")
+                    labels = cPickle.load(label_file)
                 
             #get extra data and labels
                 if name in custom_data_dict:
@@ -181,23 +182,33 @@ if __name__ == "__main__":
                         custom_abstracts = GetAbstracts(custom_paper_list)
                         custom_abstract_vectors = FeaturizeAbstracts(custom_abstracts)
                         current_data = abstract_vectors + custom_abstract_vectors
+                        if name == "aj": #aukosh didn't do data 1
+                            current_data = custom_abstract_vectors
                         
                     with open(custom_label_file_name,"rb") as custom_label_file:
[…]

### 2014-05-14 Paper.tex
paper updates

--- 2014-05-14 Paper.tex
@@
 \usepackage{amsmath,amsthm,amssymb}
-\usepackage{graphicx}
 \pagestyle{myheadings}
@@
 
-One of the important aspects of the algorithm is that it present some articles to the user that it predicted to be uninteresting.
-Otherwise there is risk of mislabeling and potentially discarding many articles that are interesting to the user.
+One of the important aspects of the algorithm is that it present some articles predicted to be uninteresting.
+Otherwise there is risk in mislabeling and potentially discarding many articles that are interesting to the user.
 Nevertheless the goal is to have an active filter on the articles lest the whole purpose of the program be defeated.
@@
 original perceptron bound by a factor of $\frac{1}{p}$, it is also only a
-bound in expectation.\\
-
-This algorithm can be also be used with other classifiers.
-The set of data on which the scheme updates on is no longer iid, but any bound on the number of mistakes that doesn't require iid data, like the bound for Perceptron algorithm, will still hold in expectation with a similar modification.
-We apply the same approach to the OnlineSVM, Margin Perceptron, and Kernel Perceptron algorithms.
-\\
-The general method outlined above corrects negative predictions slowly and at a constant rate.
-It seems natural that instead we might want to correct a lot of negative predictions when we feel the algorithm is not accurate, and be more lenient when the algorithm is doing well.
-In order to achieve this, we introduce an adaptive $p$ scheme.
-This scheme starts with some value of $p$, and each time it asks the user to label a data point that it predicted would have a negative label, it modifies $p$.
-If it was correct, then $p$ is reduced and it checks negative predictions less often.
-On the other hand, if it was incorrect it increases $p$.
-\\
-
-\noindent Adaptive $p$ Perceptron algorithm:
-\begin{quotation}
-%\noindent Modified Perceptron:\\
-\noindent $w_1=0$\\
-\noindent $p=1$\\
-{\tt for $t=1$ to $T$}:\\
-\indent receive($x_t$)\\
-\indent $\widehat{y}_t=\mbox{sign}(w_t\cdot x_t)$\\
-\indent {\tt if} $\widehat{y}_t =1$ : \\
-\indent\indent receive($y_t$)\\
-\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
-\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
-\indent\indent {\tt else $w_{t+1} = w_t$}\\
-\indent\{\tt else if ($\widehat{y}_t =-1$ {\tt and} $k_t = 1$):\\
-\indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
-\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
-\indent\indent\indent $p=p + \gamma_1(1 - p)$\\
-\indent\indent {\tt else }
-\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
-\indent\indent\indent $p = p - \gamma_2(p - p_{\min})$}
-\indent {\tt else if $\widehat{y}_t = -1$ and $k_t=0$}:\\
-\indent\indent $w_{t+1} = w_t$\\
-{\tt return $w_{T+1}$}
-\end{quotation}
-Where $p_{\min}$, $\gamma_1$ and $\gamma_2$ are parameters that can be tuned by the user.
-It is easy to extend the bound above to this case.
-Let $I_i$, $M_i$, and $M'$ be defined as above.
-The bound $M'\leq r^2/\rho^2$ follows in exactly the same way.
-We then bound $M_3$ in expectation,
-\begin{align*}
-\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] \\
- \leq &\ (1 - p_{\min})\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
-\end{align*}
-and bound $\E[M_2]$ from below
-\begin{align*}
-\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \\
-\geq &\ p\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
-\end{align*}
-Continuing as before, this gives the following bound on $\E[M]$,
-\begin{align}
-\E[M] = &\E[M'] + \E[M_3] \leq \frac{r^2}{\rho^2} + \frac{1-p_{\min}}{p_{\min}} \frac{r^2}{\rho^2}\\
-= & \frac{1}{p_{\min}}\frac{r^2}{\rho^2}\\
-\end{align*}
-Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sec:results} and see that it performs fairly well while requiring less input from the user.\\
+bound in expectation.
 
 \section{Implementation}
+
 The tool is made from components in multiple Python files, split up according to their function in the program.
@@
 
-An important feature of any text classification device is the data used to construct feature vectors.
+An important aspect of any text classification device is the data used to construct feature vectors.
 There are several approaches to text classification, itself a large field of research.
-We take an elementary approach and use a bag-of-words model, that is, performing a word count for each distinct word in the abstract and converting that into a vector.
-Each distinct word corresponds to a different coordinate in the feature space. This ``vectorization" is defined in {\tt ArxivData.py} and called when
+We take an elementary approach and use a bag-of-words model; that is, performing a word count for each distinct word in the abstract and converting that into a vector.
+Each distinct word corresponds to a different coordinate in the feature space.
+This ``vectorization" is defined in a class {\tt TextFeatureVector} in {\tt ArxivData.py} and is called in the function {\tt FeaturizeAbstracts()}, which appears before running the algorithms, naturally.
+Word counts seems like a naive approach, yet the bag-of-words model is well used and often augmented with other methods.
+Moreover implementing such a model is not terribly complicated, which makes it a useful and attractive option.
 
 %One of the most important aspects of this tool is what is used for feature data. There are several approaches to text categorization that
-\section{Results}
-\label{sec:results}
-
-We tested different online learning algorithms with sample data generated by graduate students at NYU.
-Several students were asked to use a python script to gather the abstracts from Arxiv in categories that they specified (see SECTION REFERENCE HERE).
-Then the students were asked to generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
-\\
-This data was used to test the following online learning algorithms: Perceptron, Margin Perceptron, Online SVM, Gaussian Kernel Perceptron, and Polynomial Kernel Perceptron.
-For each algorithm with tunable parameters, a grid search was performed to determine the best value of each parameter.
-For each combination of parameters, each classifier was separately trained on the data from each student, and the resulting performance was averaged over students.
-Parameters chosen with a grid search are given in table \ref{table:Parametertable}.
-\\
-
-\begin{table}[h]
-\centering
-\begin{tabular}{l | r}
-Algorithm & Parameters Tuned \\
-\hline
-Margin Perceptron &  Margin, $\rho$  \\
-Online SVM & Penalty, $C$ \\
-Gaussian Kernel Perceptron &  variance, $\sigma$, \\
-Polynomial Kernel Perceptron &  intercept, $c$, and degree, $d$ \\
-\hline
-\end{tabular}
-\label{table:Parametertable}
-\caption{Parameters tuned for each classifier used.}
-\end{table}
-
-For this particular classification problem, it turned out that overall accuracy was a poor indicator of performance.
-Students tended to only label a small subset of papers as ``interesting'', so an algorithm which always predicted a label of $\hat{y} = -1$ (the paper was not interesting to the user) could achieve very high values of accuracy.
-Instead, we looked at Recall and Precision.
-Recall, $R$, is the percentage of papers labeled $y=1$ by the user that were successfully categorized by the algorithm, $\hat{y} = 1$.
-Precision, $P$, is the percentage of papers labeled $\hat{y} = 1$ by the algorithm that were actually interesting to the user, $y = 1$.
-The mathematical definitions are as follows
-\begin{align*}
-R(h) = & \frac{\sum_{i=1}^m 1_{\left{h(x_i) = 1 \cap y_i =1\right}}{\sum_{i=1}^m 1_{\left{y_i = 1\right}} \\
-P(h) = & \frac{\sum_{i=1}^m 1_{\left{h(x_i) = 1 \cap y_i =1\right}}}{{\sum_{i=1}^m 1_{\left{h(x_i) = 1\right}}. \\
-\end{align*}
-For each classifier and combination of parameters, the algorithm was shown 50 papers to obtain reasonable weights, and then as it continued to run, the number of correct positive labels, incorrect positive labels, and incorrect negative labels were recorded and used to calculate $R$ and $P$.
-These values were then averaged over all students separately.
-The best average $R$ (over all parameters tested) and the best average $P$ are shown in figure \ref{fig:PrecisionandRecall}, along with the number of negative labels asked of the user.
-We can see that the scheme with adaptive $p$ is able to achieve performance close to the the original algorithms but requiring less than half as many negative updates.
-
-\begin{figure}
-\includegraphics[width=0.7\textwidth]{EveryoneRecallPaper.pdf}
-\includegraphics[width=0.7\textwidth]{EveryonePrecisionPaper.pdf}
-\label{fig:PrecisionandRecall}
-\caption{Performance of tested online classification algorithms using different values of $p$.
-The adaptive $p$ algorithm performs relatively well compared to the original algorithm ($p = 1$), and requires less than half as many negative updates.
-Majority vote classifier combines all others in this figure.}
-\end{figure}
-
-\section{Conclusion}
 

### 2014-05-14 Paper.tex

--- 2014-05-14 Paper.tex
@@
 
-An important feature of any text classification device is the data used to construct feature vectors.
+An important aspect of any text classification device is the data used to construct feature vectors.
 There are several approaches to text classification, itself a large field of research.
-We take an elementary approach and use a bag-of-words model, that is, performing a word count for each distinct word in the abstract and converting that into a vector.
-Each distinct word corresponds to a different coordinate in the feature space. This ``vectorization" is defined in {\tt ArxivData.py} and called when
+We take an elementary approach and use a bag-of-words model; that is, performing a word count for each distinct word in the abstract and converting that into a vector.
+Each distinct word corresponds to a different coordinate in the feature space.
+This ``vectorization" is defined in a class {\tt TextFeatureVector} in {\tt ArxivData.py} and is called in the function {\tt FeaturizeAbstracts()}, which appears before running the algorithms, naturally.
+Word counts seems like a naive approach, yet the bag-of-words model is well used and often augmented with other methods.
+Moreover implementing such a model is not terribly complicated, which makes it a useful and attractive option.
 

### 2014-05-14 Paper.tex
paper updates

@@
 =& \ \Bigl\|\sum_{t \in I_1 \cup I_2} (w_{t+1} - w_t) \Bigr\| 
-= \ \|w_{T+1} \| \\
+=  \|w_{T+1} \| \\
 =&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  w_{t+1}\|^2 - \|w_t\|^2 }\\
@@
 original perceptron bound by a factor of $\frac{1}{p}$, it is also only a
-bound in expectation.\\
+bound in expectation.
 
 This algorithm can be also be used with other classifiers.
-The set of data on which the scheme updates on is no longer iid, but any bound on the number of mistakes that does not require iid data, like the bound for Perceptron algorithm, could still hold in expectation with a similar modification.
+The set of data the scheme uses to update itself is no longer i.i.d., but any bound on the number of mistakes that does not require i.i.d.
+data, like the bound for the Perceptron algorithm, could still hold in expectation with a similar modification.
 We implement this approach with the Online SVM, Margin Perceptron, and Kernel Perceptron algorithms.
-\\
-The general method outlined above corrects negative predictions slowly and at a constant rate.
-It seems natural that instead we might want to correct a lot of negative predictions when we feel the algorithm is not accurate, and be more lenient when the algorithm is doing well.
+
+The general method outlined above corrects false negative predictions slowly and with fixed probability.
+It seems natural that instead we might want to correct a lot of false negatives when we feel the algorithm is not accurate, and be more lenient when the algorithm is doing well.
 In order to achieve this, we introduce an adaptive $p$ scheme.
@@
 If it was correct, then $p$ is reduced and it checks negative predictions less often.
-On the other hand, if it was incorrect it increases $p$.
-Psuedocode is given below \\
+On the other hand, if it was incorrect it increases $p$: \\
 
@@
 \indent\indent {\tt else $w_{t+1} = w_t$}\\
-\indent\{\tt else if ($\widehat{y}_t =-1$ {\tt and} $k_t = 1$):\\
+\indent {\tt else if ($\widehat{y}_t =-1$ {\tt and} $k_t = 1$)}:\\
 \indent\indent {\tt if $y_t\neq\widehat{y}_t$}:\\
@@
 \indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
-\indent\indent\indent $p = p - \gamma_2(p - p_{\min})$}
+\indent\indent\indent $p = p - \gamma_2(p - p_{\min})$
 \indent {\tt else if $\widehat{y}_t = -1$ and $k_t=0$}:\\
@@
 \end{quotation}
-Where $p_{\min}$, $\gamma_1$ and $\gamma_2$ are parameters that can be tuned.
+Note that $p_{\min}$, $\gamma_1$ and $\gamma_2$ are parameters that can be tuned.
 It is easy to extend the bound above from the modified Perceptron to the adaptive $p$ case.
@@
 Continuing as before, this gives the following bound on $\E[M]$,
-\begin{align}
-\E[M] = &\E[M'] + \E[M_3] \leq \frac{r^2}{\rho^2} + \frac{1-p_{\min}}{p_{\min}} \frac{r^2}{\rho^2}\\
-= & \frac{1}{p_{\min}}\frac{r^2}{\rho^2}\\
+\begin{align*}
+\E[M] = &\ \E[M'] + \E[M_3] \leq \frac{r^2}{\rho^2} + \frac{1-p_{\min}}{p_{\min}} \frac{r^2}{\rho^2}\\
+= &\ \frac{1}{p_{\min}}\frac{r^2}{\rho^2}
 \end{align*}
-Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sec:results} and see that it performs fairly well while requiring less input from the user.\\
+Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sec:results} and see that it performs fairly well while requiring less input from the user.
 
@@
 
-We tested different online learning algorithms with sample data generated by graduate students at NYU.
-Several students were asked to use a python script to gather the abstracts from Arxiv in categories that they specified (see SECTION REFERENCE HERE).
-Then the students were asked to generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
-\\
+We tested the different online learning algorithms with sample data generated by graduate students at NYU.
+Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified (see SECTION REFERENCE HERE) and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
+
 This data was used to test the following online learning algorithms: Perceptron, Margin Perceptron, Online SVM, Gaussian Kernel Perceptron, and Polynomial Kernel Perceptron.
@@
 For each combination of parameters, each classifier was separately trained on the data from each student, and the resulting performance was averaged over students.
-Parameters chosen with a grid search are given in table \ref{table:Parametertable}.
+Parameters chosen with a grid search are given in Table \ref{table:Parametertable}.
 \\
@@
 \hline
-Margin Perceptron &  Margin, $\rho$  \\
-Online SVM & Penalty, $C$ \\
+Margin Perceptron &  margin, $\rho$  \\
+Online SVM & penalty, $C$ \\
 Gaussian Kernel Perceptron &  variance, $\sigma$, \\
@@
 Students tended to only label a small subset of papers as ``interesting'', so an algorithm which always predicted a label of $\hat{y} = -1$ (the paper was not interesting to the user) could achieve very high values of accuracy.
-Instead, we looked at Recall and Precision.
+Instead, we looked at the two quantities recall and precision.
 Recall, $R$, is the percentage of papers labeled $y=1$ by the user that were successfully categorized by the algorithm, $\hat{y} = 1$.
@@
 \begin{align*}
-R(h) = & \frac{\sum_{i=1}^m 1_{\left{h(x_i) = 1 \cap y_i =1\right}}{\sum_{i=1}^m 1_{\left{y_i = 1\right}} \\
-P(h) = & \frac{\sum_{i=1}^m 1_{\left{h(x_i) = 1 \cap y_i =1\right}}}{{\sum_{i=1}^m 1_{\left{h(x_i) = 1\right}}. \\
+R(h) = & \frac{\sum_{i=1}^m 1_{\left\{h(x_i) = 1 \cap y_i =1\right\}}}{\sum_{i=1}^m 1_{\left\{y_i = 1\right\}}} \\
+P(h) = & \frac{\sum_{i=1}^m 1_{\left\{h(x_i) = 1 \cap y_i =1\right\}}}{\sum_{i=1}^m 1_{\left\{h(x_i) = 1\right\}}}.
 \end{align*}
 For each classifier and combination of parameters, the algorithm was shown 50 papers to obtain reasonable weights, and then as it continued to run, the number of correct positive labels, incorrect positive labels, and incorrect negative labels were recorded and used to calculate $R$ and $P$.
-These values were then averaged over all students separately.
-The best average $R$ (over all parameters tested) and the best average $P$ are shown in figure \ref{fig:PrecisionandRecall}, along with the number of negative labels asked of the user.
-We can see that the scheme with adaptive $p$ is able to achieve performance close to the the original algorithms but requiring less than half as many negative updates.
+These values were averaged over all students separately.
+The best average $R$ (over all parameters tested) and the best average $P$ are shown in Figure \ref{fig:PrecisionandRecall}, along with the number of negative labels asked of the user.
+We can see that the scheme with adaptive $p$ is able to achieve performance close to the the original algorithms but requiring less than half as many updates.
 
-\begin{figure}
+\begin{figure}\centering
 \includegraphics[width=0.7\textwidth]{EveryoneRecallPaper.pdf}

### 2014-05-14 Paper.tex
paper edits.
fixed table reference.
added a brief conclusion.

@@
 \indent\indent\indent $p=p + \gamma_1(1 - p)$\\
-\indent\indent {\tt else }
-\indent\indent\indent $w_{t+1} = w_t + y_t x_t$\\
-\indent\indent\indent $p = p - \gamma_2(p - p_{\min})$
+\indent\indent {\tt else }\\
+\indent\indent\indent $w_{t+1} = w_t$\\
+\indent\indent\indent $p = p - \gamma_2(p - p_{\min})$\\
 \indent {\tt else if $\widehat{y}_t = -1$ and $k_t=0$}:\\
@@
 For each combination of parameters, each classifier was separately trained on the data from each student, and the resulting performance was averaged over students.
-Parameters chosen with a grid search are given in Table \ref{table:Parametertable}.
+Parameters chosen with a grid search are given in Table \ref{tab:parametertable}.
 \\
-
 \begin{table}[h]
@@
 \end{tabular} 
-\label{table:Parametertable}
 \caption{Parameters tuned for each classifier used.}
+\label{tab:parametertable}
 \end{table}
@@
 \section{Conclusion}
+We have developed a tool to present users with potentially interesting articles from the massive number of papers available on Arxiv.
+Online learning methods are used to learn the user's preferences over time, but in order for them to be useful, they cannot present the user with every single prediction.
+Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those it feels will not be interesting.
+We show that in this context, a bound on the expected number of mistakes can still be achieved under the some assumptions.
+Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.\\
+In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particulary to develop an improved bound on the adaptive $p$ algorithm.
+It is possible that such a bound would lead to a more informed decision on how to change $p$ in the algorithm to minimize mistakes.
+Finally, it would be worthwhile to explore other online learning algorithms and possible other features that might improve predictive performance.
 

### 2014-05-14 Arxiver.py
more in arxiver

@@ -1,6 +1,6 @@
 import ArxivSubjects as arxs
 from ArxivData import GetPapersOAI
-
+import Perceptron as perc
 
 class Arxiver:
     
@@ -9,7 +9,9 @@ class Arxiver:
         self.classifier = classifier
         self.subjects = None
         self.subcategories = None
-        
+        self.name = ''
+
+
     def SetUp(self):
         """ Ask for name, subjects and subcategories"""
         
@@ -72,14 +74,102 @@ class Arxiver:
     def CheckTodaysPapers(self):
         """ Use OAI to get today's papers and check them one at a time asking for user input."""
 
-        paper_list = getPapersOAI()
-        
-        
-        
-        
-    
-    
+        paper_list = GetPapersOAI()
 
-                    
+    def Prompt(self):
+        """ Present an abstract to the user 
+        """        
+        
+    def Run(self):
+        """ Run the algorithm by presenting abstracts, receiving labels and calling function to
+                update weights.
+        """
 
-                
+        #filename where data is stored
+        data_filename = "./" + user_name + "CustomTestData.pkl"
+
+        data_file = open(data_filename,"rb")
+
+
+        paper_list = cPickle.load(data_file)
+
+        print paper_list
+
+        #initialize list of labels
+        label_list = []
+
+
+        #Vectorize abstracts
+        classifier = perc.PerceptronClassifier(1.0)
+        for paper in paper_list:
+            print "-"*80
+            #Predict abstract, make y_hat
+            #If prediction is 1, present paper, make update
+            #Else if predition is -1, make k
+            #If k=1 present abstract, make update
+            #If k=0 don't
+            label = PromptUser(paper)
+            label_list.append(label)
+
+
+        out_file = open(str(user_name) + "customlabels.pkl","wb")
+        cPickle.dump(label_list,out_file)
+
+
+
+    def CheckAbstract(x, label)
+        """ Receive data and label for one abstract, make prediction 
+        """
+
+        #for i in range(len(data)):
+            x = data[i]
+            y_hat = classifier.Predict(x)
+            y = label
+            if y == 1 and y_hat == 1:
+                if i > threshold:
+                    n_pos_right += 1
+            elif y == -1 and y_hat == -1:
+                #update total_negative_checks count if we had to check, 
+                # and for adaptive p, update value of current_p
+                if self.p == 'adaptive':
+                    #got it correct, reduce p towards 0.01, our minimum
[…]

### 2014-05-15 Arxiver.py
little more to Arxiver

@@ -1,5 +1,7 @@
 import ArxivSubjects as arxs
 from ArxivData import GetPapersOAI
+from ArxivData import GetAbstracts
+
 import Perceptron as perc
 
 class Arxiver:
@@ -93,17 +95,36 @@ class Arxiver:
 
         paper_list = cPickle.load(data_file)
 
-        print paper_list
+        #print paper_list
 
         #initialize list of labels
         label_list = []
 
-
         #Vectorize abstracts
+        vectors = FeaturizeAbstracts(GetAbstracts(paper_list))
+
         classifier = perc.PerceptronClassifier(1.0)
-        for paper in paper_list:
-            print "-"*80
+        for i, x in enumerate(vectors):
             #Predict abstract, make y_hat
+            paper = paper_list[i]
+            y_hat = classifier.Predict(x)
+
+            if y_hat == 1:
+                #Present paper, make update if needed
+                y = PromptUser(paper)
+                if y == 1:
+
+
+            elif y_hat == -1:
+                #make k
+
+                if k == 1:
+                    y = PromptUser(paper)
+
+                else:
+                    
+
+            print "-"*80
             #If prediction is 1, present paper, make update
             #Else if predition is -1, make k
             #If k=1 present abstract, make update
@@ -117,14 +138,25 @@ class Arxiver:
 
 
 
-    def CheckAbstract(x, label)
-        """ Receive data and label for one abstract, make prediction 
-        """
+#    def CheckAbstract(x, label)
+#        """ Receive data and label for one abstract, make prediction 
+#        """
+
+
+
+
+
+
+
+
+
+
+
+
 
         #for i in range(len(data)):
             x = data[i]
             y_hat = classifier.Predict(x)
-            y = label
             if y == 1 and y_hat == 1:
                 if i > threshold:
                     n_pos_right += 1

### 2014-05-15 Arxiver.py
arxiver

@@ -94,8 +94,7 @@ class Arxiver:
 
 
         paper_list = cPickle.load(data_file)
-
-        #print paper_list
+        chosen_papers = []
 
         #initialize list of labels
         label_list = []
@@ -111,26 +110,45 @@ class Arxiver:
 
             if y_hat == 1:
                 #Present paper, make update if needed
+                print "-"*80
                 y = PromptUser(paper)
                 if y == 1:
-
-
-            elif y_hat == -1:
-                #make k
-
-                if k == 1:
-                    y = PromptUser(paper)
-
+                    n_pos_right += 1
+                    chosen_papers.append(paper)
                 else:
+                    classifier.Update(x,y_hat,y)
                     
+            elif y_hat == -1:
+                #make k #update total_negative_checks count if we had to check, 
+                # and for adaptive p, update value of current_p
+                if self.p == 'adaptive':
+                    #got it correct, reduce p towards 0.01, our minimum
+                    if np.random.binomial(1,self.current_p) == 1:
+                        print "-"*80
+                        y = PromptUser(paper)
+                        #check if correct, if so reduce p towards .01
+                        if y == 1:
+                            self.current_p = 0.9*self.current_p + 0.001
+                            total_negative_checks += 1
+                            chosen_papers.append(paper)
+                            if i  > threshold :
+                                total_end_negative_checks += 1
+                else:
+                    if np.random.binomial(1,self.p) == 1:
+                        y = PromptUser(paper)
+                        total_negative_checks += 1
+                        if i  > threshold :
+                            total_end_negative_checks += 1
 
-            print "-"*80
+
+
+        for paper in chosen_papers:
+            print paper.id
+
             #If prediction is 1, present paper, make update
             #Else if predition is -1, make k
             #If k=1 present abstract, make update
             #If k=0 don't
-            label = PromptUser(paper)
-            label_list.append(label)
 
 
         out_file = open(str(user_name) + "customlabels.pkl","wb")
@@ -141,15 +159,6 @@ class Arxiver:
 #    def CheckAbstract(x, label)
 #        """ Receive data and label for one abstract, make prediction 
 #        """
-
-
-
-
-
-
-
-
-
 
 
 

### 2014-05-16 Arxiver.py
some changes to tests.  Added more labeled data for Steven.

@@ -92,7 +92,6 @@ class Arxiver:
 
         data_file = open(data_filename,"rb")
 
-
         paper_list = cPickle.load(data_file)
         chosen_papers = []
 
@@ -128,19 +127,20 @@ class Arxiver:
                         y = PromptUser(paper)
                         #check if correct, if so reduce p towards .01
                         if y == 1:
-                            self.current_p = 0.9*self.current_p + 0.001
+                            self.current_p = 0.9*self.current_p + 0.001 #TODO: This was a wrong negative, increase p
                             total_negative_checks += 1
                             chosen_papers.append(paper)
                             if i  > threshold :
                                 total_end_negative_checks += 1
+                        elif y == -1:
+                            #correct negative prediction, leave classifier alone and decrease p
+                            self.current_p = 0.9*self.current_p + 0.001
                 else:
                     if np.random.binomial(1,self.p) == 1:
                         y = PromptUser(paper)
                         total_negative_checks += 1
                         if i  > threshold :
                             total_end_negative_checks += 1
-
-
 
         for paper in chosen_papers:
             print paper.id

### 2014-05-16 ClassifierTester.py

@@ -44,7 +44,8 @@ class ClassifierTester:
             n_recall_wrong = 0
             total_negative_checks = 0    #how many negative predictions the user must verify
             total_end_negative_checks = 0 #how many checks we do in the last 100 papers
-            threshold = 150 #hard code threshold = 150 for now
+            threshold = 50 #hard code threshold = 50 for now
+            neg_threshold = 100
 
             #loop through data and run the algorithm
             for i in range(len(data)):
@@ -61,14 +62,14 @@ class ClassifierTester:
                         #got it correct, reduce p towards 0.01, our minimum
 #                        print "current p is", self.current_p
                         if np.random.binomial(1,self.current_p) == 1:
-                            self.current_p = 0.9*self.current_p + 0.001
+                            self.current_p = 0.85*self.current_p + 0.0015
                             total_negative_checks += 1
-                            if i  > threshold :
+                            if len(data) - i  < neg_threshold :
                                 total_end_negative_checks += 1
                     else:
                         if np.random.binomial(1,self.p) == 1:
                             total_negative_checks += 1
-                            if i  > threshold :
+                            if len(data) - i  < neg_threshold :
                                 total_end_negative_checks += 1
 
                 elif y_hat == 1 and y == -1:
@@ -87,15 +88,15 @@ class ClassifierTester:
                         k = np.random.binomial(1,self.current_p)
                         if k == 1:
                             total_negative_checks += 1
-                            if i  > threshold :
+                            if len(data) - i  < neg_threshold :
                                 total_end_negative_checks += 1
                             classifier.Update(x,y_hat,y)
-                            self.current_p = 0.55*self.current_p + 0.4
+                            self.current_p = 0.55*self.current_p + 0.45
                     else:
                         k = np.random.binomial(1,self.p)
                         if k == 1:
                             total_negative_checks += 1
-                            if i  > threshold :
+                            if len(data) - i  < neg_threshold:
                                 total_end_negative_checks += 1
                             classifier.Update(x,y_hat,y)
 
@@ -206,6 +207,7 @@ class ClassifierTester:
         max_recall = 0.
         best_param = None
         best_neg_updates = 0
+        best_last_neg_updates = 0
         #go through all parameters tested by this object, and return
         # the parameters that gave the best recall
         for param in parameters_list:
[…]

### 2014-05-16 Paper.tex
some changes to tests.  Added more labeled data for Steven.
changes to paper

@@
 
+To run the tool as a user, we've included a script {\tt Arxiver.py}, which first asks for filters to draw articles including subject, subfields, and dates.
+Then it presents a subset of those it pulled from arXiv, filtering out some of those it predicts are uninteresting according to the Perceptron algorithm we've described.
+When finished {\tt Arxiver} prints out the arXiv ID's for those articles the user labels as interesting.
+
 An important aspect of any text classification device is the data used to construct feature vectors.
@@
 
+What we can see from the data is that across the different algorithms the Polynomial Kernel Perceptron and Majority Vote Classifier fared better than the others, and the Gaussian Kernel Perceptron was generally the worst performing classifier in all cases.
+The classifiers generally had better results for precision than they did for recall, which makes a lot of sense since we might find quite a few papers interesting that share no overlap with the previous papers we have liked.
+Consequently the algorithm won't select this as interesting so recall is hurt.
+However if the algorithm has selected a paper as interesting it is probably because there is overlap with some previous papers, suggesting that it will be in a similar category.
+
+It was interesting to see how varying $p$ the probability of presenting the paper had an impact on the results, some which might not have been entirely expected.
+For instance I would expect that asking for the most labels from the user (i.e.
+$p = 1$) would translate to considerably higher gains in both precision and recall all around.
+Yet for the best performing algorithms there wasn't a huge difference in recall between the adaptive version and $p = 1$, and for precision both adaptive $p$ and $p = 0.1$ outperformed $p = 1$.
+In fact this was generally true for all algorithms.
+
 \begin{figure}\centering
@@
 
-\section{Conclusion}
-We have developed a tool to present users with potentially interesting articles from the massive number of papers available on Arxiv.
+\section{Conclusions}
+To summarize our work, we're pleased to have a developed a tool that we believe can be of use for many people across several fields and to have employed a number of machine learning features in its construction, from the text categorization model to the classification algorithms.
+Beyond constructing these features we created some of our own features.
+For instance the adaptive probability $p$ turned out to perform fairly well in comparison to the tool that didn't filter results based on preferences.
+It was also interesting to see the bound that we got adapted from the original Perceptron model.
+One point to mention about future work in this area is that it seems likely that some of the other bounds from the Perceptron algorithm can probably be applied to get similar bounds for this problem as well.
+
 Online learning methods are used to learn the user's preferences over time, but in order for them to be useful, they cannot present the user with every single prediction.
@@
 We show that in this context, a bound on the expected number of mistakes can still be achieved under the some assumptions.
-Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.\\
-In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particulary to develop an improved bound on the adaptive $p$ algorithm.
+Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
+
+In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particularly to develop an improved bound on the adaptive $p$ algorithm.
 It is possible that such a bound would lead to a more informed decision on how to change $p$ in the algorithm to minimize mistakes.
+Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes updates, though this guess is comes from our experience with the AdaBoost algorithm and its modifications.
+
 Finally, it would be worthwhile to explore other online learning algorithms and possible other features that might improve predictive performance.
+Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models.
+Nevertheless that is a huge body of work in and of itself.
 

### 2014-05-16 Arxiver.py

@@ -108,37 +108,49 @@ class Arxiver:
             paper = paper_list[i]
             y_hat = classifier.Predict(x)
 
+
             if y_hat == 1:
                 #Present paper, make update if needed
                 print "-"*80
                 y = PromptUser(paper)
                 if y == 1:
-                    n_pos_right += 1
                     chosen_papers.append(paper)
+                    if i > threshold:
+                        n_pos_right += 1
                 else:
+                #update on false positive, add one to n_wrong
                     classifier.Update(x,y_hat,y)
-                    
-            elif y_hat == -1:
-                #make k #update total_negative_checks count if we had to check, 
-                # and for adaptive p, update value of current_p
+                    if i > threshold:
+                        n_precision_wrong += 1
+
+            #y_hat == -1:        
+            else: 
+#                #update total_negative_checks count if we had to check, 
+#                # and for adaptive p, update value of current_p
                 if self.p == 'adaptive':
                     #got it correct, reduce p towards 0.01, our minimum
                     if np.random.binomial(1,self.current_p) == 1:
                         print "-"*80
                         y = PromptUser(paper)
                         #check if correct, if so reduce p towards .01
-                        if y == 1:
+                        if y == -1:
                             self.current_p = 0.9*self.current_p + 0.001
                             total_negative_checks += 1
-                            chosen_papers.append(paper)
                             if i  > threshold :
                                 total_end_negative_checks += 1
+#                            self.current_p = 0.9*self.current_p + 0.001
+#                            total_negative_checks += 1
+#                            chosen_papers.append(paper)
+#                            classifier.Update(x,y_hat,y)
+#                            self.current_p = 0.55*self.current_p + 0.4
+#                            if i  > threshold :
+#                                total_end_negative_checks += 1
                 else:
                     if np.random.binomial(1,self.p) == 1:
-                        y = PromptUser(paper)
-                        total_negative_checks += 1
-                        if i  > threshold :
-                            total_end_negative_checks += 1
+#                        y = PromptUser(paper)
+#                        total_negative_checks += 1
+#                        if i  > threshold :
+#                            total_end_negative_checks += 1
 
 
 
@@ -164,33 +176,33 @@ class Arxiver:
 
 
         #for i in range(len(data)):
-            x = data[i]
-            y_hat = classifier.Predict(x)
-            if y == 1 and y_hat == 1:
-                if i > threshold:
-                    n_pos_right += 1
[…]

### 2014-05-16 Arxiver.py
added to arxiver.py.

@@ -1,22 +1,29 @@
 import ArxivSubjects as arxs
 from ArxivData import GetPapersOAI
 from ArxivData import GetAbstracts
+import urllib
 
 import Perceptron as perc
 
 class Arxiver:
     
-    def __init__(self,classifier):
+    def __init__(self,classifier,p):
 
         self.classifier = classifier
         self.subjects = None
         self.subcategories = None
         self.name = ''
-
+        self.p = p
+        self.current_p = 1.0 #only used if p = 'adaptive'
+        self.gamma_1 = 0.55
+        self.gamma_2 = 0.1
+        
 
     def SetUp(self):
         """ Ask for name, subjects and subcategories"""
         
+        print "Please enter a name for this Arxiver."
+        self.name = raw_input()
         #initialize subjects and subcategories
         self.subjects = []
         self.subcategories = dict()
@@ -73,14 +80,103 @@ class Arxiver:
 
         return
     
-    def CheckTodaysPapers(self):
+    def CheckDaysPapers(self,date):
         """ Use OAI to get today's papers and check them one at a time asking for user input."""
 
-        paper_list = GetPapersOAI()
+        mkdir("./" + self.name + "/" + date)
+        paper_list = []
+        for subject in self.subjects:
+            print "Gathering ", subject, " papers."
+            paper_list += GetPapersOAI(day=date,subject=subject, subcategories=self.subcategories[subject])
+            time.sleep(20)
 
-    def Prompt(self):
-        """ Present an abstract to the user 
+        abstract_vectors = FeaturizeAbstracts(GetAbstracts(paper_list))
+
+        #shuffle data so there is no pattern from getting one subject at a time.
+        
+        random.shuffle(abstract_data)
+
+        for i, x in enumerate(abstract_vectors):
+            y_hat = self.classifier.Predict(x)
+            
+            if y_hat == 1:
+                #Present paper, make update if needed
+                print "-"*60
+                y = self.Prompt(paper,y_hat)
+                if y == 1:
+                    self.SavePaper(paper_list[i],date)
+                else:
+                    self.classifier.Update(x,y_hat,y)
+            elif y_hat == -1:
+                #make k #update total_negative_checks count if we had to check, 
+                # and for adaptive p, update value of current_p
+                if self.p == 'adaptive':
+                    if np.random.binomial(1,self.current_p) == 1:
+                        print "-"*60
+                        y = self.Prompt(paper,y_hat)
+                        #check if correct, if so reduce p towards .01
+                        if y == 1: #incorrect
[…]

### 2014-05-16 Paper.tex

@@
 
-Finally, it would be worthwhile to explore other online learning algorithms and possible other features that might improve predictive performance.
+Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.
 Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models.
 Nevertheless that is a huge body of work in and of itself.
+\end{document}
+
+\section{Conclusion}
+We have developed a tool to present users with potentially interesting articles from the massive number of papers available on Arxiv.
+Online learning methods are used to learn the user's preferences over time, but in order for them to be useful, they cannot present the user with every single prediction.
+Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those it feels will not be interesting.
+We show that in this context, a bound on the expected number of mistakes can still be achieved under the some assumptions.
+Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.\\
 

### 2014-05-16 Paper.tex
edited paper.

@@
 \usepackage{graphicx}
+\usepackage{natbib}
 \pagestyle{myheadings}
@@
 In Section 3, we describe the main components of the program in the python modules we created, and give a description on how to use the tool.
-We present our results in Section 4, followed by other observations and concluding remarks.
+We present our results in Section 4, followed by other observations and concluding remarks in seciont 5.
 
@@
 We bound $M_1 + M_2$ in the same way we bound $M$ in the original Perceptron algorithm.
-Assume there exists a $\rho$ and $R$ satisfying the assumptions of Theorem 7.8 from our text, and a separating hyperplane determined by the vector $v$.
+Assume there exists a $\rho$ and $R$ satisfying the assumptions of Theorem 7.8 from \cite{FML}, and a separating hyperplane determined by the vector $v$.
 Let $M' = M_1 + M_2$, then
@@
 \E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \\
-\geq &\ p\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
+\geq &\ p_{\min}\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
 \end{align*}
@@
 The classes contain the methods that run the algorithm and the attributes such as weights and parameters that the algorithm uses and updates.
-Within {\tt Perceptron.py} is the modified Perceptron algorithm we presented earlier, a Margin Perceptron classifier, and a Kernel Perceptron classifier supplied with both a polynomial and Gaussian kernel.
+Within {\tt Perceptron.py} is the original Perceptron algorithm, a Margin Perceptron classifier, and a Kernel Perceptron classifier supplied with both a polynomial and Gaussian kernel.
 Similarly, the Online SVM algorithm is implemented in the file {\tt OnlineSVM.py}.
@@
 We tested the different online learning algorithms with sample data generated by graduate students at NYU.
-Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified (see SECTION REFERENCE HERE) and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
+Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.\\
 
@@
 $p = 1$) would translate to considerably higher gains in both precision and recall all around.
-Yet for the best performing algorithms there wasn't a huge difference in recall between the adaptive version and $p = 1$, and for precision both adaptive $p$ and $p = 0.1$ outperformed $p = 1$.
-In fact this was generally true for all algorithms.
+Yet for the best performing algorithms there wasn't a huge difference in recall between the adaptive version and $p = 1$.
+For precision, the lower $p$ algorithms actually performed comparably to the original schemes.
 
@@
 The adaptive $p$ algorithm performs relatively well compared to the original algorithm ($p = 1$), and requires less than half as many negative updates.
-Majority vote classifier combines all others in this figure.}
+The $p = 0.1$ case tends to perform poorly, but requires far fewer updates.
+The majority vote classifier combines all others in this figure.}
 \end{figure}
@@
 \section{Conclusions}
-To summarize our work, we're pleased to have a developed a tool that we believe can be of use for many people across several fields and to have employed a number of machine learning features in its construction, from the text categorization model to the classification algorithms.
-Beyond constructing these features we created some of our own features.
-For instance the adaptive probability $p$ turned out to perform fairly well in comparison to the tool that didn't filter results based on preferences.
-It was also interesting to see the bound that we got adapted from the original Perceptron model.
-One point to mention about future work in this area is that it seems likely that some of the other bounds from the Perceptron algorithm can probably be applied to get similar bounds for this problem as well.
+To summarize our work, we're pleased to have a developed a tool that we believe can be of use for many people across several fields.
+We use online learning algorithms to incrementally learn the user's preferences and suggest interesting articles daily.\\
 
-Online learning methods are used to learn the user's preferences over time, but in order for them to be useful, they cannot present the user with every single prediction.
-Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those it feels will not be interesting.
-We show that in this context, a bound on the expected number of mistakes can still be achieved under the some assumptions.
+In order for this approach to be useful, it cannot present the user with every single prediction.
+Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those that it predicts will not be interesting.
+We show that in this context, a bound on the expected number of mistakes can still be achieved under the same assumptions as Theorem 7.8 from \cite{FML}.
 Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
-
+\\
 In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particularly to develop an improved bound on the adaptive $p$ algorithm.
 It is possible that such a bound would lead to a more informed decision on how to change $p$ in the algorithm to minimize mistakes.
-Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes updates, though this guess is comes from our experience with the AdaBoost algorithm and its modifications.
-
+Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes the number of labels required from the user.\\
 Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.
 Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models.
-Nevertheless that is a huge body of work in and of itself.
+\bibliography{paper}
 \end{document}
@@
 
+%To summarize our work, we're pleased to have a developed a tool that we believe can be of use for many people across several fields and to have employed a number of machine learning features in its construction, from the text categorization model to the classification algorithms.
+Beyond constructing these features we created some of our own features.
+For instance the adaptive probability $p$ turned out to perform fairly well in comparison to the tool that didn't filter results based on preferences.
+It was also interesting to see the bound that we got adapted from the original Perceptron model.
+One point to mention about future work in this area is that it seems likely that some of the other bounds from the Perceptron algorithm can probably be applied to get similar bounds for this problem as well.
+
+%Online learning methods are used to learn the user's preferences over time, but in order for them to be useful, they cannot present the user with every single prediction.
+Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those it feels will not be interesting.
+We show that in this context, a bound on the expected number of mistakes can still be achieved under the some assumptions.
+Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
+
+%In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particularly to develop an improved bound on the adaptive $p$ algorithm.
+It is possible that such a bound would lead to a more informed decision on how to change $p$ in the algorithm to minimize mistakes.
+Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes updates, though this guess is comes from our experience with the AdaBoost algorithm and its modifications.
+
+%Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.
+Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models.
+Nevertheless that is a huge body of work in and of itself.
+%
+%
+%
+%
+%
+%
+%
+%
+%
+
 \end{document}
@@
 % We envisioned that eventually after receiving enough data the tool can tailor the articles it presents to the preferences of the user and offer mostly articles that are ``interesting." The tool would sometimes offer articles it predicts that are uninteresting in order to get a full
-
-\end{document}

### 2014-05-16 Paper.tex
some edits to paper.

@@
 In Section 3, we describe the main components of the program in the python modules we created, and give a description on how to use the tool.
-We present our results in Section 4, followed by other observations and concluding remarks in seciont 5.
+We present our results in Section 4, followed by other observations and concluding remarks in Section 5.
 
@@
 \section{Theory: Algorithm and Bounding Updates}
-
+\label{sec:theory}
 The main engine behind the tool is a modified Perceptron algorithm which employs an accept-reject method among the papers it labels uninteresting.
-The following pseudocode details the algorithm, where $x_t$ denotes feature vectors, $y_t$ denotes labels, $\widehat{y}_t$ are predictions, $w_t$ are hypotheses, and $k_t$ are i.i.d.
+The following pseudocode details the algorithm, where $x_t$ denotes feature vectors, $y_t$ denotes labels, $\widehat{y}_t$ are predictions, $w_t$ are weights, and $k_t$ are i.i.d.
 random variables used for the accept-reject method.
@@
 variables $k_t$ for each observation when $\widehat{y} = -1$.
-Note that if $\widehat{y} = -1$ and $k=1$, the algorithm will ask for the correct label and make an update.
+If $\widehat{y} = -1$ and $k=1$, the algorithm will ask for the correct label and make an update.
 Otherwise if $\widehat{y} = -1$ and $k=0$, the algorithm does not ask for the correct label and makes no update.\\
@@
 1,2,3$.
-We bound $M_1 + M_2$ in the same way we bound $M$ in the original Perceptron algorithm.
+We bound $M_1 + M_2$ in the same way we bound $M$ in the original Perceptron algorithm, because these are all the mistakes after which an update is made..
 Assume there exists a $\rho$ and $R$ satisfying the assumptions of Theorem 7.8 from \cite{FML}, and a separating hyperplane determined by the vector $v$.
@@
 \end{align*}
-where the last equality uses the independence of $k_t$ from the data. To control the sum of expectations in this expression we consider the expectation of $M_2$. Since
+where the last equality uses the independence of $k_t$ from the data, and the expecation is taken over the realizations of $k_t$.
+To control the sum of expectations in this expression we consider the expectation of $M_2$.
+Since
 \[
@@
 For instance, {\tt getTestData.py} and {\tt LabelData.py} are scripts that call the functions that collect arXiv data and present the abstracts to acquire labels, respectively, which we place in a single script for the user.
-Additionally {\tt ClassifierTester.py} defines a class for the classification algorithms we include allowing them to be used in a uniform manner despite taking different parameters.
+Additionally {\tt ClassifierTester.py} takes a single classifier and tests it on a grid of possible parameters to find the best values.
 This enables us to run tests over each algorithm, with multiple data sets from a few different users, using a set of several values for each parameter in a fairly organized manner in the script {\tt TestClassifiers.py}.
-Plots are also constructed in that script as well.
+Plots are also constructed in that script as well.\\
 
-To run the tool as a user, we've included a script {\tt Arxiver.py}, which first asks for filters to draw articles including subject, subfields, and dates.
-Then it presents a subset of those it pulled from arXiv, filtering out some of those it predicts are uninteresting according to the Perceptron algorithm we've described.
-When finished {\tt Arxiver} prints out the arXiv ID's for those articles the user labels as interesting.
+To run the tool as a user, we've included a script {\tt Arxiver.py}, which first asks for filters to draw articles including subjects and subcategories.
+Then it presents abstracts from a subset of those it pulled from arXiv.
+As described in Section \ref{sec:theory}, it only asks for some of labels from papers that it predicts are uninteresting.
+As it runs, {\tt Arxiver} automatically saves the articles that the user labels as interesting.\\
 
@@
 We take an elementary approach and use a bag-of-words model; that is, performing a word count for each distinct word in the abstract and converting that into a vector.
+We normalize this vector by the total length of the abstract,
 Each distinct word corresponds to a different coordinate in the feature space.
-This ``vectorization" is defined in a class {\tt TextFeatureVector} in {\tt ArxivData.py} and is called in the function {\tt FeaturizeAbstracts()}, which appears before running the algorithms, naturally.
+This ``vectorization" is defined in a class {\tt TextFeatureVector} in {\tt ArxivData.py} and TextFeatureVector objects are created from abstracts using {\tt FeaturizeAbstracts()}.
 Word counts seems like a naive approach, yet the bag-of-words model is well used and often augmented with other methods.
 Moreover implementing such a model is not terribly complicated, which makes it a useful and attractive option.
+\\
+All of the software used for this tool project is available at ``github.com/skwaap/fml-arxiv'' including scripts for testing.\\
 
@@
 
-It was interesting to see how varying $p$ the probability of presenting the paper had an impact on the results, some which might not have been entirely expected.
-For instance I would expect that asking for the most labels from the user (i.e.
-$p = 1$) would translate to considerably higher gains in both precision and recall all around.
-Yet for the best performing algorithms there wasn't a huge difference in recall between the adaptive version and $p = 1$.
+It was interesting to see how varying $p$ the probability of presenting the paper had an impact on the results.
+For the best performing algorithms there wasn't a huge difference in recall between the adaptive version and $p = 1$.
 For precision, the lower $p$ algorithms actually performed comparably to the original schemes.
+This is not entirely unexpected, since precision measures the number of false positives, and the algorithms outlined here update on all false positives independent of $p$.
+\\
 
-\begin{figure}\centering
-\includegraphics[width=0.7\textwidth]{EveryoneRecallPaper.pdf}
-\includegraphics[width=0.7\textwidth]{EveryonePrecisionPaper.pdf}
+\begin{figure}[h]\centering
+\includegraphics[width=0.65\textwidth]{EveryoneRecallPaper.pdf}
+\includegraphics[width=0.65\textwidth]{EveryonePrecisionPaper.pdf}
 \label{fig:PrecisionandRecall}
@@
 The adaptive $p$ algorithm performs relatively well compared to the original algorithm ($p = 1$), and requires less than half as many negative updates.
-The $p = 0.1$ case tends to perform poorly, but requires far fewer updates.
+The $p = 0.1$ approach has ver poor recall, but requires far fewer updates.
 The majority vote classifier combines all others in this figure.}
@@
 It is possible that such a bound would lead to a more informed decision on how to change $p$ in the algorithm to minimize mistakes.
-Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes the number of labels required from the user.\\
+Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes the number of labels required from the user, and potentially give a clear improvement over the fixed $p$ case.\\
 Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.

### 2014-05-16 Paper.tex
Fixed some typos and set up bibliography.

@@
 \usepackage{graphicx}
-\usepackage{natbib}
+\usepackage{cite}
 \pagestyle{myheadings}
-\markright{Joseph McDonald}
+\markright{Steven Delong and Joseph McDonald}
 
@@
 We bound $M_1 + M_2$ in the same way we bound $M$ in the original Perceptron algorithm, because these are all the mistakes after which an update is made..
-Assume there exists a $\rho$ and $R$ satisfying the assumptions of Theorem 7.8 from \cite{FML}, and a separating hyperplane determined by the vector $v$.
+Assume there exists a $\rho$ and $R$ satisfying the assumptions of Theorem 7.8 from ~\cite{FML}, and a separating hyperplane determined by the vector $v$.
 Let $M' = M_1 + M_2$, then
@@
 
-\begin{figure}[h]\centering
+\begin{figure}[h!]\centering
 \includegraphics[width=0.65\textwidth]{EveryoneRecallPaper.pdf}
@@
 The adaptive $p$ algorithm performs relatively well compared to the original algorithm ($p = 1$), and requires less than half as many negative updates.
-The $p = 0.1$ approach has ver poor recall, but requires far fewer updates.
+The $p = 0.1$ approach has very poor recall, but requires far fewer updates.
 The majority vote classifier combines all others in this figure.}
@@
 We use online learning algorithms to incrementally learn the user's preferences and suggest interesting articles daily.\\
-
 In order for this approach to be useful, it cannot present the user with every single prediction.
 Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those that it predicts will not be interesting.
-We show that in this context, a bound on the expected number of mistakes can still be achieved under the same assumptions as Theorem 7.8 from \cite{FML}.
+We show that in this context, a bound on the expected number of mistakes can still be achieved under the same assumptions as Theorem 7.8 from ~\cite{FML}.
 Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
@@
 Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.
-Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models.
-\bibliography{paper}
+Considering a wider variety of text classification models would probably produce better results.
+\bibliography{paper}{}
+\bibliographystyle{plain}
+\bibstyle{plain}
 \end{document}

### 2014-05-16 Paper.tex
update paper

--- 2014-05-16 Paper.tex
@@
 \pagestyle{myheadings}
-\markright{Joseph McDonald}
+\markright{Joey McDonald, Steve Delong}
 
@@
 We use online learning algorithms to incrementally learn the user's preferences and suggest interesting articles daily.\\
-
 In order for this approach to be useful, it cannot present the user with every single prediction.
@@
 We show that in this context, a bound on the expected number of mistakes can still be achieved under the same assumptions as Theorem 7.8 from \cite{FML}.
-Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
+We also test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
 \\

### 2014-05-16 Paper.tex
small formatting edits in paper.

--- 2014-05-16 Paper.tex
@@
 \begin{align*}
-M' \rho =&\ \frac{v}{\|v\|}\sum_{I_1 \cup I_2} y_tx_t \
- \leq   \Bigl\|\sum_{t \in I_1 \cup I_2} y_t x_t\Bigr\| \\
-=& \ \Bigl\|\sum_{t \in I_1 \cup I_2} (w_{t+1} - w_t) \Bigr\| 
-=  \|w_{T+1} \| \\
+M' \rho =&\ \frac{v}{\|v\|}\sum_{I_1 \cup I_2} y_tx_t  \leq \Bigl\|\sum_{t \in I_1 \cup I_2} y_t x_t\Bigr\| \\
+=& \ \Bigl\|\sum_{t \in I_1 \cup I_2} (w_{t+1} - w_t) \Bigr\| =  \|w_{T+1} \| \\
 =&\ \sqrt{\sum_{t \in I_1 \cup I_2} \|  w_{t+1}\|^2 - \|w_t\|^2 }\\
@@
 = &\ \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t w_t\cdot x_t - \|x_t\|^2} \\
-\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|x_t\|^2}
-\leq \sqrt{M'r^2}.
+\leq &\ \sqrt{\sum_{t \in I_1 \cup I_2} \|x_t\|^2} \leq \sqrt{M'r^2}.
 \end{align*}
@@
 \begin{align*}
-\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] \\
- = &\ (1 - p)\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
+\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] = (1 - p)\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
 \end{align*}
@@
 \begin{align*}
-\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \\
-=&\ p\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
+\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] = p\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
 \end{align*}
@@
 \begin{align*}
-\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] \\
- \leq &\ (1 - p_{\min})\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
+\E[M_3] = & \sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 0}] \leq \  (1 - p_{\min})\sum_{t=1}^T \E[1_{\left\{\widehat{y_t} = -1 \cap y_t = 1\right\}}],
 \end{align*}
@@
 \begin{align*}
-\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \\
-\geq &\ p_{\min}\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
+\E[M_2] =&\ \sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}]\E[1_{k_t = 1}] \geq \ p_{\min}\sum_{t=1}^T \E[1_{\left\{\hat{y_t} = -1 \cap y_t = 1\right\}}].
 \end{align*}
@@
 \end{align*}
-Unfortunately, we do not have a stonger theoretical bound for this adaptive $p$ approach, but we test this scheme in section \ref{sec:results} and see that it performs fairly well while requiring less input from the user.
+Unfortunately, we do not have a stronger theoretical bound for this adaptive $p$ approach that takes into account the fact that $p$ will become smaller as the algorithm learns.
+However, we test this scheme in section \ref{sec:results} and see that it performs fairly well while requiring less input from the user.
 
@@
 \label{fig:PrecisionandRecall}
-\caption{Performance of tested online classification algorithms using different values of $p$.
+\caption{ \small Performance of tested online classification algorithms using different values of $p$.
 The adaptive $p$ algorithm performs relatively well compared to the original algorithm ($p = 1$), and requires less than half as many negative updates.

### 2014-05-16 Paper.tex

--- 2014-05-16 Paper.tex
@@
 \title{Online Classification of arXiv Papers Based on Your Preferences}
-\author{Steve Delong and Joey McDonald}
+\author{Steve Delong and Joseph McDonald}
 \maketitle
@@
 We use online learning algorithms to incrementally learn the user's preferences and suggest interesting articles daily.\\
-In order for this approach to be useful, it cannot present the user with every single prediction.
+\indent In order for this approach to be useful, it cannot present the user with every single prediction.
 Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those that it predicts will not be interesting.
-We show that in this context, a bound on the expected number of mistakes can still be achieved under the same assumptions as Theorem 7.8 from ~\cite{FML}.
-Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
+We show that in this context, a bound on the expected number of mistakes can still be achieved under the same assumptions as Theorem 7.8 from \cite{FML}.
+We also test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.
 \\
-In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particularly to develop an improved bound on the adaptive $p$ algorithm.
+\indent In the future, it would be nice to develop tighter theoretical bounds on our modified learning algorithm, and particularly to develop an improved bound on the adaptive $p$ algorithm.
 It is possible that such a bound would lead to a more informed decision on how to change $p$ in the algorithm to minimize mistakes.
 Perhaps giving a different functional form to the way $p$ is changed can produce an algorithm that minimizes the number of labels required from the user, and potentially give a clear improvement over the fixed $p$ case.\\
-Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.
+\indent Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance.
 Considering a wider variety of text classification models would probably produce better results.

### 2014-05-18 ArxivData.py
Added a lot more to arxiver

@@ -8,6 +8,7 @@ from xml.etree import ElementTree as ET
 from datetime import datetime
 import cPickle
 import ArxivSubjects as arxs
+import StopWords
 import time
 
 class TextFeatureVector:
@@ -173,6 +174,7 @@ class Paper:
 
             self.published = entry.find('.//{http://purl.org/dc/elements/1.1/}date').text #, namespaces=ns).text
             self.id = entry.find('.//{http://www.openarchives.org/OAI/2.0/}identifier').text #, namespaces=ns).text
+            self.id = self.id[14:]
         else:
             print "Error: xml_type must be one of: query, rss, OAI"
             raise NotImplementedError
@@ -391,7 +393,7 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
             This function returns a list of Paper objects, populated from Arxiv papers updated on given
             range of days within given subject set
     """
-    
+    until_string = ''
     if arxs.subject_dict[subject]:   
         subcategory_list = [arxs.subject_name[subject]+' - '+subcategory for subcategory in subcategories]
     else:
@@ -437,7 +439,6 @@ def GetPapersOAI(day='', until='', subject='', subcategories=None):
     start = time.clock()
     for entry in root.findall('.//{http://www.openarchives.org/OAI/2.0/}record'): #, namespaces=ns):
         this_paper = Paper(entry, 'OAI')
-
         if IsPaperInSubcategories(entry, subcategory_list, ns):
             # check that the paper was published today, not just updated.
             if day and until:
@@ -539,7 +540,7 @@ def FeaturizeAbstracts(abstracts):
         abstract_vectors  -  list of TextFeatureVectors, one for each abstract.
 
     """
-    stop_words = ["is","it","that","the","a","an","of","in","this","and","if","by","are","when","not","with","at","on","also","to"]
+    stop_words = StopWords.stop_words
 
     feature_list = []
     #initialize feature vector
@@ -547,10 +548,7 @@ def FeaturizeAbstracts(abstracts):
         text_features = TextFeatureVector()
         abstract_cleaned = re.sub(r'\$\$[^$]*\$\$','',abstract)
         abstract_cleaned = re.sub(r'\$[^$]*\$','',abstract_cleaned)
-        
-#        abstract_cleaned = re.sub(r'\\begin{align[^\(\end\)]*\\end{align\*?}','',abstract_cleaned)
[…]

### 2014-05-18 Arxiver.py

@@ -1,9 +1,55 @@
 import ArxivSubjects as arxs
+from Perceptron import PerceptronClassifier, MarginPerceptronClassifier, VotedPerceptronClassifier
+from Perceptron import KernelPerceptronClassifier
+from OnlineSVM import OnlineSVMClassifier
+from WeightedMajority import WeightedMajorityClassifier
 from ArxivData import GetPapersOAI
 from ArxivData import GetAbstracts
-import urllib
-
+from ArxivData import FeaturizeAbstracts
+from datetime import datetime
+import errno, urllib, os, cPickle, time
+import numpy as np
 import Perceptron as perc
+
+
+def mkdir_p(path):
+    #helper function for making directories
+    try:
+        os.makedirs(path)
+    except OSError as exc: # Python >2.5
+        if exc.errno == errno.EEXIST and os.path.isdir(path):
+            pass
+        else: raise
+
+
+#define kernel functions locally so we can pickle them
+def GaussianKernel(x,y):
+
+    return np.exp(x.Distance2(y)/(2.))
+
+def PolynomialKernel(x,y):
+        
+    return (x*y)**3
+
+def MakeWeightedMajorityClassifier():
+    """ wrapper to make weighted majority classifier from
+    Perceptron, Margin perceptron, SVM, Gaussian kernel Perceptron Classifier, Polynomial Kernel Perceptron Classifier 
+    For use directly with Arxiver, all parameters hard coded for now"""
+
+
+    pclassifier = PerceptronClassifier(1.0)
+    v_pclassifier = VotedPerceptronClassifier(1.0)
+    margin_pclassifier = MarginPerceptronClassifier(1.0, 0.03125)
+    svmclassifier = OnlineSVMClassifier(0.25, 1.0)
+    gk_pclassifier = KernelPerceptronClassifier(1.0,GaussianKernel)
+    pk_pclassifier = KernelPerceptronClassifier(1.0,PolynomialKernel)    
+
+    classifier_list = [pclassifier, v_pclassifier, margin_pclassifier, svmclassifier, gk_pclassifier, pk_pclassifier]
+    
+    wm_classifier = WeightedMajorityClassifier(classifier_list)
+    
+    return wm_classifier
+    
 
 class Arxiver:
     
@@ -15,6 +61,7 @@ class Arxiver:
         self.name = ''
         self.p = p
         self.current_p = 1.0 #only used if p = 'adaptive'
+        self.p_min = 0.01
         self.gamma_1 = 0.55
[…]

### 2014-05-18 Perceptron.py

@@ -425,12 +425,4 @@ if __name__ == "__main__":
     
     
     print "Completed some basic tests"
-
-
-
-
-        
-
-        
-           
         

### 2014-05-18 TestClassifiers.py

@@ -115,11 +115,11 @@ if __name__ == "__main__":
     
     #set up lists of parameters and classifiers for grid searches
     etas = [1.0]
-    rhos = [2**(-8), 2**(-7),2**(-6),2**(-5)]
-    Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0]
+    rhos = [2**(-8), 2**(-7),2**(-6),2**(-5), 2**(-4)]
+    Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0, 4.0]
     sigmas = [0.01, 0.02, 0.04,0.2, 1.0]
-    cs = [0.0, 0.03125, 0.0625]
-    ds = [1, 2, 3, 4]
+    cs = [0.0, 0.03125, 0.0625, 0.125]
+    ds = [1, 2, 3, 4, 5]
     
     #liss of classifiers and their names
     classifier_list = [MakePerceptronClassifier, MakeVotedPerceptronClassifier, MakeMarginPerceptronClassifier,MakeOnlineSVMClassifier,MakeGaussianKernelPerceptronClassifier, MakePolynomialKernelPerceptronClassifier, MakeWeightedMajorityClassifier]
@@ -156,7 +156,7 @@ if __name__ == "__main__":
 
         #go through values for p
         for p in [1.0, 0.15, 'adaptive']:
-#            print "P value is: ", p
+            print "P value is: ", p
 
             #go through users
             for k in range(len(names)):
@@ -212,7 +212,7 @@ if __name__ == "__main__":
                 
 
                 classifier_tester.Test(current_data,current_labels)
-                recall_grid, precision_grid, neg_updates, last_neg_updates = classifier_tester.ReportGrid(0)
+                recall_grid, precision_grid, neg_updates, last_neg_updates = classifier_tester.ReportGrid(1)
                 
                 #set up grid from gridsearch that aggregates over all names:
                 #if it's the first name, make the grid
@@ -334,11 +334,3 @@ pyplot.subplot(212)
 pyplot.title("Number of Negative Updates")
 pyplot.xticks(range(len(classifier_names)),classifier_names, rotation = 35, fontsize=9)
 pyplot.savefig("./EveryonePrecision.pdf")
-
-
-    
-    
-
-
-    
-                    

### 2014-05-18 Arxiver.py
small fixes.

@@ -172,7 +172,7 @@ class Arxiver:
                             self.classifier.Update(x,y_hat,y)
                         elif y == -1:
                             #correct negative prediction, leave classifier alone and decrease p
-                            self.current_p = self.current_p - self.gamma_2(self.current_p - self.p_min)
+                            self.current_p = self.current_p - self.gamma_2*(self.current_p - self.p_min)
                 else:
                     #check with fixed probability p
                     if np.random.binomial(1,self.p) == 1:

### 2014-05-18 Arxiver.py
Added more to Arxiver.py

@@ -375,10 +375,21 @@ class Arxiver:
 #                            total_end_negative_checks += 1
 #                        classifier.Update(x,y_hat,y)
     def SavePaper(self,paper,date):
-        """ Save paper to folder"""
+        """ Clean the title and Save paper to folder"""
 
+        cleaned_title = ''
+        for i in range(len(paper.title)):
+            if paper.title[i] != "/" and paper.title[i:(i+1)] != "\n":
+                cleaned_title += paper.title[i]
+                if paper.title[i:(i+1)] != "\n":
+                    cleaned_title += " "
+                    i = i + 1
+                    
+            elif paper.title[i] == "/":
+                cleaned_title += " "
+                
         urllib.urlretrieve("https://www.arxiv.org/pdf/" + paper.id + ".pdf","./"+ self.name + "/" + date + "/" + paper.title + ".pdf")
-        
+
         return
         
 

### 2014-05-19 Presentation.tex
Added presentation, small changes to test script.:

\documentclass{beamer}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}

\title{Online cassification of ArXiv papers based on your preferences }

\author{Steven Delong and Joseph McDonald}

\begin{document}
\maketitle

\begin{frame}
  \frametitle{Goals}
  Wanted to create a tool to learn an individual's preferences for ArXiv articles.
\begin{itemize}
\item New articles added every day, we want to predict whether they are interesting and learn from them.
\item Natural setting for online learning.
\item Traditional online learning algorithms would ask for a label for every paper rendering them useless. Can we get away with asking for less of the articles that are uninteresting.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Method}
\begin{itemize}
\item Start: simple perceptron and bag-of-words model.
\item Update always when  $\hat{y} = 1$, and with probability $p$ if $\hat{y} = -1$.
\item Can show that this achieves a bound on mistakes in expectation similar to normal perceptron $E[M] \leq \frac{1}{p}\frac{r^2}{\rho^2}$.
\item Much weaker bound, but requires less ``work'' from the user.
\item Intuitively, maybe we should look at more of the $\hat{y} = -1$ observations when we're less sure of the algorithm.
\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Idea: Variable $p$}

\begin{itemize}
\item Start with $p = 1$, increase $p$ on false negatives, decrease $p$ on correct negative predictions.
\item Never reduce $p$ below some value $p_\min$. 
\item Set $p = p + \gamma_1(1 - p)$ when we're wrong, and $p = p - \gamma_2(p - p_\min)$ when correct.
\item Can show the same bound holds as in the constant $p$ case, using $p = p_\min$.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Results}
We each labeled several articles, shuffled their order, and then tested several online learning algorithms on them.  We measured recall and number of negative labels required in the last 120 papers.
\includegraphics[width=0.6\textwidth]{EveryoneRecallPaper.pdf}
\end{frame}

\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
\item The modified algorithms perform reasonably well while requiring less labels.
\item We obtained bounds on  $\mathbb{E}[M]$ for the modified perceptron algorithms.
\item In the future: Better bounds on adaptive $p$, tune adaptive $p$, explore other features and algorithms.
\item Code available at www.github.com/skwaap/fml-arxiv.
\end{itemize}
\end{frame}

\end{document}

### 2014-05-19 ClassifierTester.py

@@ -44,8 +44,8 @@ class ClassifierTester:
             n_recall_wrong = 0
             total_negative_checks = 0    #how many negative predictions the user must verify
             total_end_negative_checks = 0 #how many checks we do in the last 100 papers
-            threshold = 50 #hard code threshold = 50 for now
-            neg_threshold = 100
+            threshold = 100 #hard code threshold = 50 for now
+            neg_threshold = 120
 
             #loop through data and run the algorithm
             for i in range(len(data)):

### 2014-05-19 TestClassifiers.py

@@ -102,7 +102,7 @@ def BestParams(grid, neg_updates):
 #Begin Script here:
 if __name__ == "__main__":
 #names of people who contributed labels
-    names = ["steven","joey", "aj"] #,"sid","manas","iantobasco","travis"]
+    names = ["steven","joey"] #,"sid","manas","iantobasco","travis"]
     custom_data_dict = {'steven' : 'stevenallCustomTestData.pkl', 'joey' : 'joeynewCustomTestData.pkl','travis' : 'travisCustomTestData.pkl', 'aj' : 'ajCustomTestData.pkl'}
     custom_label_dict = {'steven' : 'stevenallcustomlabels.pkl', 'joey' : 'joeynewcustomlabels.pkl', 'travis' : 'traviscustomlabels.pkl', 'aj' : 'ajcustomlabels.pkl'}
     
@@ -115,10 +115,10 @@ if __name__ == "__main__":
     
     #set up lists of parameters and classifiers for grid searches
     etas = [1.0]
-    rhos = [2**(-8), 2**(-7),2**(-6),2**(-5), 2**(-4)]
-    Cs = [2**(-6),2**(-5),2**(-4),2**(-3),2**(-2), 2**(-1), 1.0, 2.0, 4.0]
-    sigmas = [0.01, 0.02, 0.04,0.2, 1.0]
-    cs = [0.0, 0.03125, 0.0625, 0.125]
+    rhos = [2**(-9), 2**(-5), 2**(-1), 2.]
+    Cs = [2**(-8),2**(-5),2**(-1),2,2**(3)]
+    sigmas = [1.0]
+    cs = [0.0, 0.03125, 0.0625, 0.125, 0.25, 0.5]
     ds = [1, 2, 3, 4, 5]
     
     #liss of classifiers and their names
@@ -155,7 +155,7 @@ if __name__ == "__main__":
     for cln in range(len(classifier_list)):
 
         #go through values for p
-        for p in [1.0, 0.15, 'adaptive']:
+        for p in [1.0, 0.1, 'adaptive']:
             print "P value is: ", p
 
             #go through users
@@ -276,7 +276,7 @@ if __name__ == "__main__":
 #        pyplot.xticks(range(len(classifier_names)),classifier_r_labels[names[k]],rotation=35,fontsize=8)
         pyplot.xticks([],[])
         pyplot.gcf().subplots_adjust(bottom=0.20)
-        pyplot.ylim([0,0.6])
+        pyplot.ylim([0,0.75])
[…]

### 2014-05-19 Presentation.tex
Modified presentation and added Readme.

@@
 \item Update always when  $\hat{y} = 1$, and with probability $p$ if $\hat{y} = -1$.
-\item Can show that this achieves a bound on mistakes in expectation similar to normal perceptron $E[M] \leq \frac{1}{p}\frac{r^2}{\rho^2}$.
+\item Can show that this achieves a bound on mistakes in expectation similar to normal perceptron $\mathbb{E}[M] \leq \frac{1}{p}\frac{r^2}{\rho^2}$.
 \item Much weaker bound, but requires less ``work'' from the user.
@@
 \item Set $p = p + \gamma_1(1 - p)$ when we're wrong, and $p = p - \gamma_2(p - p_\min)$ when correct.
-\item Can show the same bound holds as in the constant $p$ case, using $p = p_\min$.
+\item Can show the same bound holds as in the constant $p$ case, using
+  $p = p_\min$. $\mathbb{E}[M] \leq \frac{1}{p_{\min}}\frac{r^2}{\rho^2}$.
 \end{itemize}
@@
 \frametitle{Results}
-We each labeled several articles, shuffled their order, and then tested several online learning algorithms on them.  We measured recall and number of negative labels required in the last 120 papers.
-\includegraphics[width=0.6\textwidth]{EveryoneRecallPaper.pdf}
+We each labeled several articles, shuffled their order, and then
+tested several online learning algorithms on them.  We measured recall
+and number of labels used by the algorithm when $\hat{y} = -1$.
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{EveryoneRecallPaper.pdf}
+\end{figure}
 \end{frame}

### 2014-05-20 Paper.tex
Added stopwords, set arxiver date to today.

--- 2014-05-16 Paper.tex
@@
 This enables us to run tests over each algorithm, with multiple data sets from a few different users, using a set of several values for each parameter in a fairly organized manner in the script {\tt TestClassifiers.py}.
-Plots are also constructed in that script as well.\\
+Plots are also constructed in that script as well.
 
@@
 As described in Section \ref{sec:theory}, it only asks for some of labels from papers that it predicts are uninteresting.
-As it runs, {\tt Arxiver} automatically saves the articles that the user labels as interesting.\\
+As it runs, {\tt Arxiver} automatically saves the articles that the user labels as interesting.
 
@@
 Moreover implementing such a model is not terribly complicated, which makes it a useful and attractive option.
-\\
+
 All of the software used for this tool project is available at ``github.com/skwaap/fml-arxiv'' including scripts for testing.\\
@@
 We tested the different online learning algorithms with sample data generated by graduate students at NYU.
-Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.\\
+Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
 

### 2014-05-20 ArxivData.py

@@ -8,7 +8,7 @@ from xml.etree import ElementTree as ET
 from datetime import datetime
 import cPickle
 import ArxivSubjects as arxs
-import StopWords
+#import StopWords
 import time
 
 class TextFeatureVector:
@@ -540,7 +540,9 @@ def FeaturizeAbstracts(abstracts):
         abstract_vectors  -  list of TextFeatureVectors, one for each abstract.
 
     """
-    stop_words = StopWords.stop_words
+#    stop_words = StopWords.stop_words
+
+    stop_words = ['is','this','and']
 
     feature_list = []
     #initialize feature vector

### 2014-05-20 Arxiver.py

@@ -6,7 +6,7 @@ from WeightedMajority import WeightedMajorityClassifier
 from ArxivData import GetPapersOAI
 from ArxivData import GetAbstracts
 from ArxivData import FeaturizeAbstracts
-from datetime import datetime
+from datetime import date
 import errno, urllib, os, cPickle, time
 import numpy as np
 import Perceptron as perc
@@ -229,151 +229,7 @@ class Arxiver:
                     ans = raw_input('Invalid response. Yes/No? Use "quit" to leave.')
             
         return y
-        
-#    def Run(self):
-#       """ Run the algorithm by presenting abstracts, receiving labels and calling function to
-#                update weights.
-#        """
-#        pass
-        #filename where data is stored
-#        data_filename = "./" + user_name + "CustomTestData.pkl"
-#
-#        data_file = open(data_filename,"rb")
-#
-#        paper_list = cPickle.load(data_file)
-#        chosen_papers = []
-#
-#        #initialize list of labels
-#        label_list = []
-#
-#        #Vectorize abstracts
-#        vectors = FeaturizeAbstracts(GetAbstracts(paper_list))
-#
-#        classifier = perc.PerceptronClassifier(1.0)
-#        for i, x in enumerate(vectors):
-#            #Predict abstract, make y_hat
-#            paper = paper_list[i]
-#            y_hat = classifier.Predict(x)
-#
-#
-#            if y_hat == 1:
-#                #Present paper, make update if needed
-#                print "-"*80
-#                y = PromptUser(paper)
-#                if y == 1:
-#                    chosen_papers.append(paper)
-#                    if i > threshold:
-#                        n_pos_right += 1
-#                else:
-#                #update on false positive, add one to n_wrong
-#                    classifier.Update(x,y_hat,y)
-#                    if i > threshold:
-#                        n_precision_wrong += 1
-#
-#            #y_hat == -1:        
-#            else: 
-#                #update total_negative_checks count if we had to check, 
-#                # and for adaptive p, update value of current_p
-#                if self.p == 'adaptive':
-#                    #got it correct, reduce p towards 0.01, our minimum
-#                    if np.random.binomial(1,self.current_p) == 1:
-#                        print "-"*80
-#                        y = PromptUser(paper)
-#                        #check if correct, if so reduce p towards .01
-#                        if y == 1:
-#                            self.current_p = 0.9*self.current_p + 0.001 #TODO: This was a wrong negative, increase p
-#                            total_negative_checks += 1
-#                            if i  > threshold :
[…]

### 2014-05-20 StopWords.py

@@ -1,0 +1,3 @@
+# List of stop words for english from rank.nl
+
+stop_words = ["a","about","above","after","again","against","all","am","an","and","any","are","aren't","as","at","be","because","been","before","being","below","between","both","but","by","can't","cannot","could","couldn't","did","didn't","do","does","doesn't","doing","don't","down","during","each","few","for","from","further","had","hadn't","has","hasn't","have","haven't","having","he","he'd","he'll","he's","her","here","here's","hers","herself","him","himself","his","how","how's","i","i'd","i'll","i'm","i've","if","in","into","is","isn't","it","it's","its","itself","let's","me","more","most","mustn't","my","myself","no","nor","not","of","off","on","once","only","or","other","ought","our","ours	ourselves","out","over","own","same","shan't","she","she'd","she'll","she's","should","shouldn't","so","some","such","than","that","that's","the","their","theirs","them","themselves","then","there","there's","these","they","they'd","they'll","they're","they've","this","those","through","to","too","under","until","up","very","was","wasn't","we","we'd","we'll","we're","we've","were","weren't","what","what's","when","when's","where","where's","which","while","who","who's","whom","why","why's","with","won't","would","wouldn't","you","you'd","you'll","you're","you've","your","yours","yourself","yourselves"]

### 2014-05-20 ArxivData.py
using stopwords from rank.nl now.

@@ -540,9 +540,8 @@ def FeaturizeAbstracts(abstracts):
         abstract_vectors  -  list of TextFeatureVectors, one for each abstract.
 
     """
-#    stop_words = StopWords.stop_words
+    stop_words = StopWords.stop_words
 
-    stop_words = ['is','this','and']
 
     feature_list = []
     #initialize feature vector
